\chapter{Dread}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		"'Emergencies' have always been the pretext on which the safeguards of individual liberty have eroded."
		\begin{flushright}- Friedrich Hayek\end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}


Kraerion eventually stopped running; once his emotions cooled off, he felt embarrassed for how he had acted. 

"Well, good riddance---", he thought, "at least I can't go back now. One day is truly today."

The chipmunk returned to his burrow one last time, to fetch his screw nuts and say his goodbyes. He had stood there for a very long time; not knowing how to say farewell, and he somehow felt that the moment required a solemn pause. When he made an attempt to leave, his legs refused; he felt an annoyance for his own nostalgia. Life underground was all he had known; nothing would ever be the same.

When he exited the networks of runs through the exit known as the Northwestern Arteriole, a large woodpecker were already waiting for him. His name was Redrill, and he had an especially pronounced red crest. Woodpeckers made excellent woodworkers, but most of them worked in small teams and only took on larger construction projects. But not Redrill, he was a loner and preferred to work alone and had hence accepted Kraerion's rather unorthodox request. The seven screw-nuts he had fetched were awkwardly wrapped around his front legs, and caught the sunlight and glimmered harmoniously. 

"You're really sure about this?", Redrill asked.

"Yes!", Kraerion answered, maybe a bit too quickly, as if he was caught with his paw down a honey pot, "I---I mean, I've never been more sure."

"Don't worry,", Redrill chuckled amused, "I won't argue with the hand that feeds me. I see you've brought payment."

"Well, only one is for you though. Better get going."

The woodpecker smiled, nodded, and unfolded his wings and set off north with Kraerion---with all his might---trying to keep up the pace through the thick undergrowth.\\

The Wadborough villagers---in a time before environmental concerns---dumped much of their \textit{undesirables} in the forest. Everyone denied it---of course---yet batteries, plastics, electronics, and everything else one can imagine found itself in every nook and cranny of the forest floor. Even a run down car or two occasionally joined the detritus. Most animals---after a good whiff---would not bother with these alien contraptions. But, in a magpie a curiosity grew; soon, he conjectured: these objects of Men may teach a thing or two! The magpie began to take them apart; study their intricate design and their innate structures. He felt an unnatural compulsion towards to the weird family of human fasteners: the screw nuts. Death may be the mother of all beauty, yet these imperishable hexagons of cast steel were of different kind. Sun rays bouncing off their plain silver surfaces caught the magpie in awe; the beauty consumed him, and he eventually took to hoarding. The desire for these little things spread like wildfire; first amongst the magpies and the other birds in the crow family, but soon all animals had taken a fancy to them---a treasured commodity was born. But it wasn't like any other commodity: it endured where blueberries rot, it was portable where trees stood firm, but most significant was its limited supply---a thing of Man. It couldn't be produced like the spines of a hedgehog's back, nor grown like the acorns of an oak tree. Naturally, the young economy was tired of barter and sought a system to keep better score: an informational instrument to keep track of favours; a fair system of time allocation. And thus, for the first time in the kingdom of animal, go beyond reciprocal altruism---transcend death---and let a money be born.  

But to Kraerion, the screw nuts were but a means to an end: to purse life anew. \\

The day was a beautiful one; the sun shone bright on a blue canvas sky with only a few dots of white. His seven screw-nuts around his legs made it difficult to run, and he soon lost sight of Redrill. He did not worry though, the woodpecker would not drop his client for a lousy tempo. His anxious feelings from earlier that morning eased somewhat by the fine weather, like the potent antidote weather so often can be. 

"What a great day!", he said out loud to no one in particular, "What a shame it would be to have it spent underground."

The sun's rays told of high noon, yet the forest was uncharacteristically quiet. Noon was a time of activity, when the animals left their nests, burrows, lairs, and vocational duties to seek out trade. To buy or sell feed; to offer or acquire service. Anything imaginable were up for sale: a blackbird could be hired to sing, a joyride could be enjoyed from the back of a magpie, fresh blueberries---or stolen cabbage from the neighbouring fields---could be bought. Therefor, on any other day, a distant voice in his ears would not have sparked his curiousness. When he reached a clearing in the trees, he leaned back on his hind legs and saw---past the overgrowth---a hedgehog and a robin arguing intensely. He recognized the hedgehog as a acquaintance of his fathers, he knew him as Spinestack, and closed the distance to them.

 "Are you mad?", the robin asked flustered, "Have you completely lost your mind? You know I need more than two measly spines."
 
 "Spines are not weeds you simply pluck from a field of your choosing; they take effort and care to grow.", Spinestack answered calmly, "And these recent---although tragic---events have created a wonderful demand, as you surely understand."
 
 "But... But that's more than trice as expensive than just a couple weeks ago. This is war profiteering! I'm down to my last screw nut; you must understand."

"I mustn't anything.", Spinestack reassured calmly as he saw Kraerion approaching and waved, "I could ask any of your neighbours, who, I'm sure, would find the price both fair and appropriate."

"Wait, hold on,", Kraerion interrupted as he took notice of the small heap of spines, sharp and keen, laying between the two animals, "What do you mean war? And what on earth would you need spines for?"

"Oh haven't you heard!?", the robin squeaked, "It's terrible---\textit{Terr-i-ble} I say: just this morning a nightingale in the same tree as me got her screw nuts stolen. And it's not an isolated incident either, it has happened all over the forest in the last few days. I refuse to sit idle by; we must take up arms and defend ourselves---just like in the tales of the time of Man!"

"Hrmf", Redrill uttered from a twig above the group, seemingly appearing from nowhere, "I heard a few rats have similar complaints earlier this morning, apparently a few of their burrows had been raided. And they are \textit{rats} after all, who dares mess with them?"

"Yes, very sad indeed. Now could you take your discourse elsewhere?", Spinestack said glaring at the two newcomers, "We are conducting serious business here, go waste someone else's time---preferably someone whose time is of less value than mine."

Redrill gave Spinestack a sharp look of disgust, "You've always been more heap than stack, don't you think?", he jested, untucked his wings, and took off. Kraerion had not much choice but to follow.\\

When they reached the silver birch---which was to become Kraerion's home---a fluffy pigeon greeted them with a coo. 

"Welcome Kraerion, to our humble and peaceful corner of the Forest.", the pigeon said. His name was Greyhead; this pigeon landlord owned a score of birches and had agree to sell part of one to Kraerion. It was very unusual for one animal to only own part of a tree; most animals paid rent. Kraerion had first been offered to rent, but refused---he was ready for a life free from the burden of economic dependence and thus the need of a steady wage.

"The meter directly above the first twig is yours. I've etched in some markings, you may, of course, measure it yourself."

Kraerion nodded and handed over three of the screw nuts to Greyhead. The pigeon thanked, and having errands elsewhere---excused himself and flew away.

Redrill had received instructions many days ago, and wasted no time consulting Kraerion on what to do. He flew up and landed on the south facing side of the birch and began drilling. The woodpecker's head jerked back and forth, transforming his appearance into a red smear. Kraerion felt very silly when the origins of Redrill's name suddenly dawned on him, he could not believe how he hadn't realized it sooner.

Woodpeckers were not made to carve homes in the trunks of trees. Their strong chisel-like bill and shock-resistant head had slowly been selected by Nature for its ever increasing ability to prey on termites, beetles, and various other larvae dwelling behind bark and wood. But---like most animals---with the rise of a market, their abilities found a vastly greater commercial value elsewhere. And, the woodpeckers found it in carpentry.

Kraerion didn't know how to act whilst Redrill worked. He felt that he would only be in the way if he tried to help, and there was nothing else there he could occupy himself with. He had not stood there long before he was saved by a loud screech from a neighbouring birch.

"Wait here.", Redrill yelled urgingly from up above; he dashed---without hesitation---towards the sound. Kraerion paid no heed; instead, he lunged to the tree and rushed up its trunk. The trunk divided evenly into three large limbs; between them lay a pigeon's nest. He continued up one of the limbs as to look down and see it. Redrill was perched on a branch opposite of Kraerion---they were the first on site. And as pigeons came flying from all directions, they looked down and saw a terrified mother and her three newborn squabs, naked save for their scrawny, near undeveloped down.

"They're gone;", she said despondently, "They're all gone. Oh dear, how will we survive?"

"Won't nest insurance cover it?", a pigeon asked after a long moment of silence.

"No,", another pigeon answered, "theft has not been an issue since the time of Man. Why would anyone even think of including it in coverage?"

"It may yet be rectified, as far as I'm aware, nest insurance has always been implied to cover these kinds of things. I'm sure there's some broad clauses in there that might be stretched to cover this situation.", Greyhead broke in, sighed, "Otherwise, we'll come together and cover it ourselves; solidarity is not yet lost on us. Regardless, the best we can do for now is to give her some room and time to breath, especially by those not yet part of our community."

The insinuation was not lost on either Redrill or Kraerion. Nevertheless, it was a reasonably request, and the two animals vacated the tree.

"We're not particularly popular today.", Redrill muttered jokingly. \\

The moon had long since appeared when Redrill finished his work. The woodpecker sailed down to Kraerion at the foot of the birch.

"I guess I'm done!", he proclaimed, "Are you sure it's deep enough? It's barely more than an entrance."

"Well, you know I can't afford more of your time.", Kraerion answered. "Besides, me teeth should be strong enough to carve out the rest. Take the screw nut before I regret it."

As he handed over one of his screw nuts to the bird, Greyhead appeared again.

"Good evening, excuse my rude remark earlier," the pigeon began, "these are strange times; I hope you don't take it as a reflection of your person."

"No offense taken.", Redrill said whilst Kraerion simply nodded.

"I have some news that might not have reached the two of you yet.", Greyhead continued, "The crows have called for a state of emergency, there's going to be a meeting in the Glade, tomorrow at noon. Thought you'd like to know."

"Okay, thanks.", Redrill said tiredly, yawned, and turned to Kraerion, "It's getting late, are you sleeping here?" 

"Not like I have a choice, the new tenants have most likely already moved in to my old burrow."

"Well then,", the woodpecker said and untucked his wings, prompting Greyhead to do the same. The two birds took off and disappeared into the blissful summer night. Kraerion was left alone with his hollow, his new life, and his ever intruding thoughts. Still unsure if he had made the right decision, he climbed up the tree to his entrance.

"One day was today.", he concluded solemnly. The hollow's floor was still rough and unyielding, but it wasn't the brown soil of a burrow---that was all that mattered. With time, he would widen the hollow, grind the walls and floor sleek, carry up moss and lichen to make a bed, and slowly be able to call it home. That night, he slept uneasy; his body and limbs were heavy and exhausted, yet his mind was unbridled and completely awake. When sleep finally came, it was with an unusual satisfaction that only major life decisions produces---it scared him to know that he'd almost gone a whole life without it.


