\chapter{Dilution}

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “The long run is a misleading guide to current affairs. In the long run we are all dead.”
        \begin{flushright}- John Maynard Keynes \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}

Deep winter had sealed the world, locking the promise of spring in a distant, unreachable future. The frost was not merely on the ground and in the trees; it was in the marrow. And while the turning of the earth guaranteed that spring must eventually conquer winter, to a starving animal, the 'eventual' is a rather poor substitute for the 'now'.

Yet, against the odds, the animals had endured---even done great given the circumstance. The tragedy of Veritas's death had served as a grim wake-up call. The chipmunks had heavily rationed their food stores, and that of the Winter Fund. Through influential animals loyal to them---like rabbits, and the hares---the message of low feed stores had been spread throughout the forest. It had been done subtly, very carefully, so as not to incite panic, and been effective enough to stop any real catastrophe in its tracks.

In the end, the animals were going to survive the winter, but it would still be the worst winter in living memory. And, as with any setback, there's plenty of blame to go around---whether the blame is justified is seldom of concern when seeking scapegoats.\\

``Eveything set?", Br'r Rabbit whispered to his right-paw rabbit Thlayli as the first light of dawn broke through into the glade. The two rabbits were hutched within a thick bush---invisible to any animal in the glade.

``Yes, Br'r", Thlayli replied softly, ``the beavers, the moles, the rats, the hares, the mice, the squirrels, the hedgehogs, and songbirds of various feathers, all have some form of representation in the area. Your message will not go unnoticed."

``How about the chipmunks, and the deer?", Br'r rabbit asked, as he licked his paw and anxiously dragged it over his long ears. ``Is Aequitus here?"

``No, Br'r.", Thlayli replied hesitantly, ``He's..---He's been hard to reach these days. But Pietus will be here. And, the two biggest deer-bucks have promised you their protection if fighting breaks out. I can't get a visual though, they are too big to hide here. They should be within earshot."

``Good enough.", Br'r Rabbit sighed, ``and the stoats?"

``Far away, Br'r.", Thlayli assured and a big grin spread across his face, ``They swallowed the bait of the Aesop sighting in the east meadows. Every stoat is off searching for him save for Eaglewings personal stoat. It was genius of you to spread the rumors through the moles---the crows are too arrogant to think blind animals in a strange tongue could contain any cunning."

``I still got one last trick in me.", Br'r Rabbit chuckled amused. ``Now let's get to work.".\\

Br'r Rabbit had always been full of tricks, using his cunning and wit to get his way. But he was not young anymore, and his brain growing slower for each day. He had been angry, very angry---both with himself and with the crows---for the introducing the stoats into the forest, and his own failure to act against it. His last trick, would be to release the bottled tension of the winter's suffering directly at the crows---tension that would erupt on Br'r rabbits terms.

Snow was still covering the ground, when Br'r Rabbit made his way to the edge of the Glade---the very spot where he had failed to act against the introduction of the stoats.\\

``This is not money!", he loudly proclaimed, his voice raw. ``This is a lie!"

He dug a small hole in the snow in front of the Old Oak, and into that hole, he deposited a large pile of leaves.

``We trusted your scheme, Eaglewing!", he cried, as animals gathered from all sides around him as planned, and a few sleepy crows came out of the Old Oak to see what the commotion was about. ``We followed everything you asked of the forest, yet we had to ration and starve just to get through the winter---is that what \textit{progress} is to you?"

Before he let any crow respond, he turned around, and with his short round white tail high in the air, he defecated on the pile of leaves.

``To all the animals present in this Glade:", Br'r Rabbit continued, ``Let it be known that henceforth, the rabbits will no longer accept leaves as a form payment for our goods or services. We will accept blueberries---and only blueberries---until the crows sees it fit to return our screw-nuts!"

Eaglewing appeared from a hollow in the Old Oak, his black feathers ruffled by the cold air. The crow glared down at Br'r Rabbit.

``What treachery be th...", he began, his voice sharp, but he was immediately interrupted by the thunder of a great buck stepping forward.

``\textbf{No leaves, no leaves, no leaves!}", the buck bellowed, and the chant was quickly taken up by the rest of the animals, until the entire glade was roaring in unison.

Eaglewing stiffened. He opened his beak to retort, to weave a spell of words as he had done so often, but his voice was drowned in the feverish chant. He saw the anger in their eyes---a hunger that mere rhetoric could not feed. A rebuke at this moment would only ignite their frenzy.

With a sharp snap of his wings, the crow turned his back on the mob, feigning indifference, and retreated into the Old Oak.

Br'r Rabbit did not stay to watch the fire he had lit. He slipped into the dense undergrowth where Thlayli was waiting.

``Our work here is done.", he whispered, a youthful mischievous glint in his old eyes, ``Let's get out of here before it turns ugly."

As soon as Eaglewing was out of sight from the Glade, he abandoned all pretense of composure. He let his fury be known with a violent thrash of his wings, knocking over a heap of nuts that scattered across the hollow floor.

``Dispatch a magpie for the stoats!", he commanded the nearest crow, his eyes narrowing. ``And summon Hroðulf hither immediately. The Rabbit fancies himself cunning; let us see how his parlor tricks fare against the full weight of Law."\\

The following days the temperature rose sharply. The thaw came with a vengeance, the meltwater saluting the coming of spring by transforming the trails into muddy brooklets
.
Initially, the animals had rejoiced, believing Br'r Rabbit's plan had liberated them. But a terrible realization soon dawned on the Forest: blueberries were a poor substitute for a currency. Blueberries were seasonal, ripening only in the heat of late summer. Worse, they all had their wealth tied up in the leaves that effectively became worthless overnight---reducing everyone's savings to zero. The playing field had, for the moment, been reset.

``How could I be so foolish?", Br'r Rabbit muttered, seeing a rat and beaver struggling to barter as neither had any blueberries to their name. He hopped through a muddy trail, his ears drooped low. ``Why did I pick blueberries...? My plan was flawed from the start---I'm truly too old for this."

As the rabbit came into a clearing, he was intercepted by a large magpie.

``Br'r Rabbit.", the magpie squawked, ``I come bearing a message from Eaglewing."

Br'r rabbit's ears perked up, ``Let hear it.", he said shortly.

``Eaglewing demands a meeting with you, Snowball, and Pietus, at a time and place of your choosing. The crow wishes to discuss a possible amicable resolution to this... predicament. He has promised to not bring any stoats to the meeting. And I quote: '..Let him bring those testy bucks of his, or any other animals he fancies for protection.' Would you like me to return a message?"

The rabbit didn't answer at once; instead, he sat down for a moment, mulling over the offer. Finally, he simply nodded an agreement. ``Tell him I'll meet him three days from now, when the sun is at its peak, at the grove next to Rabbit Hill."

The magpie took flight, setting off to search for Snowball and Pietus, before returning to the crows.\\

Three days later, just as the sun passed its zenith, Eaglewing and Hroðulf made their way into the grove. Br'r Rabbit, Snowball, and Pietus were already waiting. Behind them, the two bucks stood in the shadows, swaying their heavy antlers back and forth in a silent threat.

``Ah what a delightful mess thou hast made, Br'r Rabbit", Eaglewing began, his tone dripping of false sympathy.

``Blue---berr---ies", Hroðulf added, struggling to quench his laughter. ``Out of everything you could have picked... you picked \textit{blueberries}."

``You're right.", Br'r Rabbit admitted calmly, ``Blueberries were perhaps a poor choice. But you're attacking a straw-animal. You know full well that was a desperate measure; our real intention is---and always has been---to return to the screw-nunts."

``We're sorry...", Eaglewing said, exchanging a glance with Hroðulf, who was still fighting a smirk, ``We know you're just trying to act in the best interest of the forest. It's just that... well, you don't seem to afford us the same courtesy. Spreading your misdirected gospel in the Public... thou could simply have come to us."

``Not even!", Hroðulf interjected, ``You may think whatever you want about the efficacy of our actions. Eaglewing saw an issue, and he acted in good faith to solve it, going through all the proper slow bureaucratic channels. And yet, you plan a coup in secret---undermining our Representative Glade, and stoop so low as to defecate on our way of governance. Shame!

``That's a convenient way to retell the events.", Br'r Rabbit retorted, ``But let's stick to the facts. \textit{You} introduced the leaves. The economy slowed as a direct consequence of the shift, and now \textit{we} have to deal with the fallout. Forget the blueberries---let us just go back to the screw-nuts and be done with it."

``Fair enough,", Hroðulf said, composing himself, ``Let's stick to the matter of hand. However, your premise is flawed. The economy didn't slow becase of the leaves; it slowed because the animals were too afraid to trade with a theif loose in the forest."

He waved a wing dismissively before anyone could interrupt, ``It's a moot point now, isn't it? The economy \textit{has} slowed. It needs a fresh start. So tell me: how does going back to screw-nuts fix that?"

"Because...", Br'r Rabbit hesitated, searching for the right words, "Well, the screw-nuts are \textit{real}. They've stood the test of time---they simply work. The leaves were an untested experiment, and it failed. We need to go back to what we know."

``Interesting.", Hroðulf mused, ``That did not answer my question, though. Let me rephrase it through a metaphor: Is water water?"

``What is this non-sense?", Snowball interrupted.

``What are you playing at Crow!?", Pietus muttererd frustrated, ``is this what you call an explanation?"

``Well, yes!", Hroðulf exclaimed, ``Metaphors are these precious little things---tender and digestible with reality abstracted, to afford even the dullest of minds---like yours---some amount of comprehension. So please, indulge me: is water water?"

``Fine... Yes Hroðulf.", Br'r Rabbit said at length, ``If you must. Water is water."

``Thank you, Br'r Rabbit.", Hroðulf said, his tone softening. ``Now, ask the salmon, who dares his life on his heroic journey upstream---does he swim to live in water instead of water?\\

Ask the beaver, who spends his days damning the brook to create a pond---does he labour to live in water instead of water?\\

Ask the doe, whose fawn drank from a stale puddle born with disease instead of the running brook as she was taught...\\
Ask her if water is just water?"\\

The crow paused, letting the question hang in the air, before answering his own question.
``No, water is not water if life is not death. Water is only a canvas, a medium that can be altered, shaped, and most importantly: controlled."

Hroðulf took another longer pause, looked each of them in the eye before continuing.

``And right now our economy is like that stale puddle. There's no activity in it, there's no life. How would we solve that problem, how would we make the water move?"

The grove was quiet for a long time, until finally Br'r Rabbit spoke.

``Rain.", he said slowly, ``You want to flood the market with leaves?"

``Exactly, Br'r Rabbit.", Hroðulf said, ``flood is a perfect word.
You see, Economics are not bound by fixed axiomatic truths like physics. It's entirely the product of our creation; it's made by us, for us. If we crave for two plus two to equal five, then we could simply change the axioms to make it so. Or two plus two can be whatsoever the Crax we want it to be! To let it rain for forty days and forty nights, our stale puddle of an economy, flushed clean, into a wide maelstrom of activity."

``Do you see yourself a God?", Snowball uttered, ``cause

``I think you're forgetting your place here Crow", Br'r Rabbit said sternly, ``You are but a servant of the forest, not its master. We're not in the Glade of Representatives, and you will never find quorum on this. We have no obligation to follow your insanity."

``The chipmunks will stand with the majority", Pietus added.

``Great!", Eaglewing exclaimed, ``That's all we ask. Then let's settle it with a forest wide vote---let's see what the animals think of this proposal and decide in let's say... four weeks?"

``Wait", Br'r Rabbit said as he was thinking it over, ``four weeks are too long---let's half it to two weeks. Either we agree to bring back the screw-nuts, or we start to use the leaves again."

``Agreed.", Eaglewing nodded, ``We'll meet in two weeks time in the Glade of Representatives and each vote-bearing animal may cast their vote."














