\chapter{Dilution}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“The long run is a misleading guide to current affairs. In the long run we are all dead.” 
		\begin{flushright}- John Maynard Keynes \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

"Is water water?", Vlahir crowed, peering out over the crowed that once again had gathered beneth the Old Oak. "Ask the doe, whose fawn drank from a puddle grown stale and infectious, and not from the healty brook as was taught. Ask the salmon, who dared his life swimming upstream only to get from one body of water to another. Water is not water - if life is not death. It's naught but a plain canvas; a medium to be altered, shaped, and most importantly: controlled." 

"Our forest is water — and currently, it's that still infectious puddle.  "

"Our forest is but a puddle; still and unproductive", Vlahir began, "It's known that puddles and otherwise still water carries disease. We shan't drink it.
We shall however drink from the brooks, where the current has brought life and fortune. Our forest is but a puddle; if it remains a puddle - we all be dead come winter."\\


Let the rain — like the King of Uruk foresaw, and the God of Man requried — let the rain drown the Forest for forty days and forty nights.

Vlahir looked around the glade, his curious eyes wandering. Vlahir truly loved an audience in dispense.\\

"Each of us are the droplets that makes the puddle. Our actions, its current. There is natural ebbs and flows of course, but sometimes it gets stuck still in ebb. Low demand for goods leads to fewer trades and subsequently fewer jobs. Fewer jobs in turn leads to fewer leaves to spend, further damaging demand. A maelstrom of disease if you will."\\

The glade was in complete silence now, only a few could grasp the true meaning of his words. Even fewer had any wits to contest it. \\

"Riddles are these precious little things, tender and digestible with reality abstracted, to afford even the dullest of minds some amount of comprehension. Solve this riddle and our economy is saved."

"It's the current that is the answer. A great stimulus. A greate spending to ignite, to create demand and need jobs. We will give you that." said Vlahir as he ended his speech. He left the branch and made room for Eaglewing.\\

Eaglewing stepped forward again. "Craax", he cried, "Through diligent consideration, we've decided to implement a set of policies to stimulate our economy. To increase demand and subsequently create jobs."


%"We need a current in our forest. If no-one demand anything, no-one works. If no-one works, we have no food. As puddles carries disease - a market gets stuck. It needs spending, jobs and stimulus. Otherwise it will carry disease  "  
