\chapter{Duty}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		%"Civilization is a hopeless race to discover remedies for the evils it produces."
		%\begin{flushright}- Jean-Jacques Rousseau\end{flushright}
        “Until they become conscious they will never rebel, and until after they have rebelled they cannot become conscious.”
		\begin{flushright}- George Orwell \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

The blackbird's proud song echoed unkindly against the dirt walls of the Aorta. There was something sinister about a bird in this unlikely habitat.

\input{blackbird.tex}

"I don't like this.", Cinnamon whispered to Kraerion so only he could hear, "I don't like this at all.", he answered with a nod lest he disturb the blackbird in its song or the other mourners.

Three days had past since the death of Veritas. Usually animals feel in their bones when their time is due, and they disappear to find a quiet place to die. But, Veritas died in her own burrow, and they were left without protocol. Aequitas had refused to leave Veritas side, and when they found him the next morning, he'd gone mute - finally showing his age by ageing a decade in three days. Hence, the daily operations was left to Pietas and Kraerion, which neither of them wanted. They'd decided to honour Veritas with a small ceremony in the Great Hall, in part with hopes that Aequitas recovery once she's properly made to rest. And a singer for hire blackbird was booked, which Kraerion now — when he learned how eeiry blackbird song was underground — deeply regretted.

The song eventually ebbed to naught; the chipmunks - unsure of what they'd just experienced - trickled out in pairs or groups of three. Cinnamon made a gesture to move, but when Kraerion remained still, she said: "I'll see you back at the burrow". Cinnamon's burrow which he'd spent the last three days; the damp place of dirt whence he'd promised never to return.

When but a few chipmunks remained, and Kraerion nigh alone with his thoughts, his uncle's voice broke through.

"Kraerion...", Pietas said gently, then louder when it didn't warrant a response, "Kraerion!"

"Uncle."


%The death of Aequitas left the chipmunks in disarray. With neither food nor leader the situation looked more dire the more the days passed. Pietas had earged Kraerion to fill his fathers place, and Kraerion, for the first time in his life, actually considered to do so. He did so, not because he particularly heeded Pietas advice, but because he didn't see any other way. He had grown up recieving the same education as his brother. He had learned every trick in the industry from his father, he knew he was the only chipmunk whom could hope to contain the disaster.

"Kraerion, I'm afrain my brother is lost to sorrow. Your father might never speak again."


"He could, and also did, help anyone", Kraerion murmured quietly, "save for his only daughter; he didn't help the one that mattered."
%"I figured as much. He could, and did, help everyone, save for his only daugther..."

"I know you don't like me to say this, but I must: I'm no Aequitas.
I'll always be the first to rise, and the last to call it day.
I'll always be a friend of toil, honest labour, and mess in need of launder.
But, I'll never have an aptitude for Aequitas Office - And you, you do. And, that's been plain since the day you were delivered."

%"I'm no Aequtias. I'll be the first to rise and the last to call a day; I'll always be a friend of toil and honest labour. But, I'll never be apt to hold the Office Aequitas held. But you, you are - and that's been plain since the day you were born."

"No matter how many times you, nor father, nor anyone else tells me - it's not for me.", he said showing anger, "It's not about aptitude; it's about want."

"Ah, this Senseless Search of Self again; this Pursuit of Happiness is but the priviledged damnation of your generation. These unpropable dreams: the endless struggle to fill an unfulfillable dream, which pursuit will produce but a hollow soul.
	
	You know, your father and I too had dreams: when we starved through winter, we dreamt of feed; when we laboured through summer, we dreamt of sleep. But our true dream was that our kittens would grow up without our pain: the insufferable hunger and the unbearable toil.

It's a simple dream, a concrete dream, a dream we all shared one way or another; and whatever the version of that dream you held, it will eventually be reduced to this: to do good work with, and for, the animals you live with, and care for. A dream we could, and did, fulfill - til today...

Your dream is an illusion, and I fear that when it's your time, you'll do so alone in a hollow birch still so desperatly clasping for that dream ever so just within reach.

You'll not find yourself in that tree; you'll find but droppings of pidgeons."

%"We don't chose our dreams, we are  our dreams - they consitute what makes us us
"We don't chose dreams; dreams chose us—they tell us who we are. Whether a dream is a curse or a blessing is of no substance - to refuse them would be to refuse yourself. And I'm bitten, my dream is already dreamt; it's something I'll have to pursue, or I'll become someone I'm not: someone else. And, if that ain't horror, what is?"

%"Whether a dream is a curse or a blessing, it's a part of us - not ours to choose. D

%What I crave to pursue is who I'am; I'm bitten. I can't change that, nor do I want to. And no words will make you understand.

%the pursuit of happiness is the priviledged whim of your generation. this lousy search of self, you'll never find it alone in a tree like a damned pidgeon

They'd reached an inpass, and whilst Pietas was harsh, Kraerion could see no malice in his eyes. They disagreed, as they most often did, yet it did not translate to disrespect. As each generation %carry 
hold their own set of common sense, the most productive thing is to realize that some logic ain't possible to follow.

"I will not move home; I will not take the reins", Kraerion said at length, "But I will stay this winter, til this mess is sorted out."

"I understand.", Pietas said, "I understand that I will never understand. But it's your life after all; it gives us time for the long run - I shall find a way to be content with it." 

Pietas was about to say something more when he paused, suddenly realizing how inappropriate this conversation was at a wake. And that it was the brother of the deceased he was addressing. 

"I— I'm sorry, I know this is not the time nor place for any of this — this mess...", he said preemptively,  "But Winter does not weep for lost kin, and time will be but more scarce on the morrow. I'm afraid there's more that needs to addressing..."

"She was your niece too", Kraerion answered rather annoyed, "But I understand, do go on."

"We must decide on what we should do with all the early claimants."

%"You mean if we should pay or not? I assumed we'd pay, as the agreement says..."

"I did not hear you suggest that!", Kraerion cried, "We've not failed a single payment since the Fund's inception; besides, it's an obligation: not a choice for us to make. " 

"Well, we're obligated to do the impossible: to give food we don't have. The Winter Fund was never designed for failures this early, before we've even reached the winter solstice. An animal that runs out now must be feed for the rest of the winter, effectively worth 10 animals that does the same with one week left of winter. And we will – at this rate – run out. How is it fair to feed the most ill-prepared, only to run out and doom the animals on the verge of making it til spring? If we're to prioritice later claimants, we could assure the survival of the many instead of this gamble on the few. It's, in fact, our duty to make this choice - to think of the greater good - and to us remains but one sensible and mathematically sound option: to let them starve."

% wouldn't it be more fair then if we prioriticed later claimants who we can assure will survive instead of this gamble on the worst prepared? "

"No, I will not have it. There must be another way."

"You know there isn't one."

"But what about the other clause, that we should prioritze premium-paying claimants?"

"That's the thing, almost all claimants have been from the paying cohort. And, the few that's not, have only done so because they're carrying young."

"Why would that be?"

"Your guess is as good as mine, pride cuts deep - they'd rather starve than to seek help?"

%"And why would you continue to pay your premiums if you were short of food?"

%"Wouldn't you? The last thing one does when times get tough, is to stop paying for insurance..."

"There must be a way...", Kraerion repeated, "..we can't let kittens starve, policyholder or no. There must be a way!", he turned quiet-staring at nothing and everything-searching his mind for a solution, "What if we raise debt?"

 %"Well, wasn't it intended to prioritize animals that actually paid into the Fund?"

%"That's the queer thing, almost all claimants have paid their premiums." % WITH YOUNG HERE?

%"But why? Wouldn't you stop paying the premiums if you were running out of funds?"

%"The last thing one does when times get tough, is to stop paying for insurance..."

"I suppose we could, but what food can money buy when there's no food for sale?"

"We would have to make it for sale; the rabbits have always had large safety and Zefrafa has always been a friend of us, surely they could be convinced to sell us their surplus. And, there must be others: wealthy individuals all around the forest with extra reserves. The crows could possibly help us too: get the word out, and make it all happen!"

"I guess that's possible; but what about the cost! Zefrafa could probably give us a fair price, but the crows and the others — not likely — they'd likely fleece us and call themselves heros."

"Sure, but no one would starve; how do you put a price on that?"

%// Winter Fund being in well standing and respected institution it carried the highest possible rating of credit, and possibility to draw debt from their line of credit
%But what food can money buy when there is no food for sale

The Winter Fund — being a respected instituion in good standing, carring the highest Crow's rating, and all its lines of credit still undrawn — had no difficulty raising debt. But, as they predicted, finding food to buy proved difficult. The surplus was so fragmented across individuals; each requiring to be found, convince, bargain, only to find that most of them had only a couple of days extra supply. Pietas and Kraerion worked through day and night, and with much help from the crows, they mostly pulled through. And they did get fleeced, but as a direct result of their sacrifice: that year did not go down in history as a year of famine.


%However, what food can money buy when there's no food for sale? 

%// And so the Winter Fund was reduced to debt, a soul sold, and which to repay in full would be like if Sisyphus managed to push his boulder over the crest. Ever tied to others interests

And so it came to be that the Winter Fund—the animals' last resort against winter—was reduced to indebtedness. A part of the its soul owed to others' interests. And would that interest— like Hades's interest in Sisyphus reaching the crest— ever be in favor of it being paid back in full, when interest - like the boulder - could be paid for evermore?

But whatever the cost to posterity may be, who could blame the hand that feeds the starved kittens and destitue pups — the moral agent left but one rightous road to travel? Whereas the hand that can't be seen, can very well be blamed: with a cry of Nature's cruelty. 

%Who could blame current relief when only some unknown posterity are to pay?


%Three days after Aequitas death, the chipmunks held a ceremony for their fallen industrious leader. They gathered in the Aeortha, made some remarks about his life and listened to a nightingale's song whom they hired for the occasion. The song echoed unfortunate in the narrow tunnles and sounded as out of place as the nightingale himself looked underground. 


%Value is subjective, but in a flock but a few seek value of their own. Value is also a means

%Value is subjective, but like a lemming flying off the edge off a cliff - only a few seek a valuation of their own. Value is but a means to an end, food on the table or a bed for the night. A small minority finds beauty in something scarce, dense and fungible; expanded by the majority by the function of value into something truly vast. The illusion of value becomes tangible and true - the function of value providing prosperity to all. Illusion is close to delusion, when the original beauty disappears the minority moves on, but not the lemming. The lemming sees but the folly of others, blind to the inevitable implosion. The vast wave of delusion ends in one giant crash against the cliff of lemming and the cycle begins anew.    

%Value is subjective, but value itself fulfill a remarkable function in trade. For most value is but 

%Value is subjective, yet the function value - the means of trade - is not. To most, value is but the means to an end: to put food on the table; a bed for the night. What may originate from beauty, or scarcity, or whatever attribute , expands and becomes arbitrary by pragmatic function. It does not matter what the arbitrary form is, it is value; its illusion proven, tangible, and true. Nevertheless, illusion and delusion are kin. And, eventually the beauty dissapears, value flickers, yet the function remains the same. Delusion feeds itself, larger and larger it grows, and when the rug is pulled, it all comes crashing down, and the cycle may begin anew.   

