\chapter{Diligence}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“I have never made but one prayer to God, a very short one: Oh Lord, make my enemies ridiculous. And God granted it."
		\begin{flushright}- Voltaire \end{flushright}
	\end{quote}
\end{localsize}
\vspace{1cm}

"Today is one day", Kraerion wispered to himself as his eyes opened. The chipmunk had woke, like he did all mornings, to a loud noise down the run outside the comforts of his burrow. The sound signaled a new day for the chipmunks and that they ought to be in the great hall presently. The frowst air this deep underground usually made him rise as soon as he woke - to get fresh air, but today he lingered in thought.
"Today is one day", he repreated, as he knew that tomorrow and never were but the same day. He had longed for this day as long as he could remember, so he didn't know why he needed to convince himself.

Chipmunks may be poised for a life underground, but not Kraerion. Even as a little kitten, he had disliked the damp and dark runs and burrows. Instead, he had taken to the sun, wind, and all the elements above earth. He yearned to run the branches of trees and not the runs dug in the forest soil. His father even japed that he was born more squrriel than chipmunk. When he said that he was going to live in the trees one day, he'd been laught at and told that silly dreams perish with the years. His dream had persisted though, and now he had means to pursue it. 
  The chipmunk eventually rose from his bed made of moss. He went over to the corner of his burrow and began scratching away dirt from the ground.
"Good, still here", he confirmed anxiously, as he looked down on the three gleeming screw-nuts laying before him. Kraerion covered them up again and left his burrow into the run, he followed its twists, took the right turns and soon the run widened into a great hall — The Great Hall. It was dug under a great willow with its massiv network of roots, intertwined with walls and ceiling, bearing the weight of the hollow space.

Since the time of Man, the forest had steadily increased its economic efficiency. And with it, the increased speciallization of its inhabitants. Whilst many an animal gather their feed, none is as great a carrier than the chipmunk. In their elastic cheecks they are able to carry feed, and other goods for that matter, efficiently around the forest. When other animals began to hire them for their service, their networks of runs and tunnels were redrawn to connect all important hubs of the forest. Soon chipmunks were the only specie transporting goods around the forest. And therefor, every morning, the chipmunks gathered in the Great Hall to share news and plan the day ahead.
  Most chipmunks were already present when Kraerion entered the hall. He placed himself in the back, instead of his usual place in the front.
"This is my last day", he whisperd to himself, as to be reassured its truth, "If I stand in the front, it would be as if nothing changed."

The murmur of conversation dissappeard in an instance when a chipmunk entered the hall. His grey spots of fur spoke of his age, yet his features were easy on the eye and he bore them proudly.
 Aequitas was the name he bore and he had done much and more for the welfare of the chipmunks. When he was but a boy, he'd renegotiated all major contracts in their favor and, without hesitation, passed them on to the chipmunks with their weekly pay. Together with the rabbit Zefrafa and a few crows, he had started the winter fund. A collective fund that functions similar to that of an insurance: its members contributes food during the spring, summer, and autumn as a fee, which then pays the members short of food during winter. Aequitas, being a founder, had secured the contract to manage the logistics of the fund: to collect the food, store it safely underground where the was grainy and air arid to prevent pest and rot, investigate claims, and fairly adjust payouts. Since the beginning all chipmunks had been covered, their fee being deducted from their pay. The fund was a great success, the winter deaths had decreased almost from the start; the chipmunks got a steady stream of work and means for a better life.
For all contributions Aequtias had made, none could match the feeling he instilled in every chipmunk: a intangible sense of value. The status he'd brought them in the forest, and the care he had for his own — treating them all as equals.

When he got to the front of the hall, he turned around, faceing the crowd.
"I bring both good and bad tidings.", he began. "And, as you may not be able to appreciate good in anticipation of the bad, I'll begin with the bad."
  "The eastbound tunnel collapsed late last evening; a pheasant went chasing a maggot above it, and well..."

"A pheasant", Pietas, who stood to the right of Aequitas, repeated, "Again, really? Did they not promise that the last time would be the last?"  

"They did indeed. The issue may be brought to the Concil, but what, other than petty, would be gained?", Aequtias paused for a moment, "I want you, Pietas, to go to the moles and ask them to dig the eastbound tunnel deeper this time. That atleast we can affect. You'll have the funds required."
----
Hēo seċġaþ þone ealda sprǣċe
----
"What about our current operations in the east?", Vertias asked with a squeaky voice. "The rabbit shipment is due today." 

"I'll deal with the rabbits personally, they're usually understanding with these matters.", Aequitas answered, "The personnel will be divided amongst our other projects until the eastbound tunnel is operational again."

"As to the good news", he continued, "The rumors are true: we'll follow the crows advice and institute a 2\% tax on all our shipments. All of which will go directly to the Winter Fund."

"How is that good news?", Veritas asked, the squeak in her voice gone.

"We're using our services for free, we'll effecively be exempt from this tax."

"No, that's not how this works", She said angrily, "This will only hurt our margins; to only tax our industry — It's.. It's unfair."

"Enough.", Aequtias grumbled, "That's enough, we may discuss that later. Vertias, I need you to oversee our storage facilities and expand them to consider this tax. Bring as many chipmunks you see fit for the task." 

Veritas did not answer, yet all knew she'd comply.

Aequitas gave out a few more routinely commands before he dismissed his workforce; however, his eyes were fixed on Kraerion — the dismissal did not apply to him. When the last chipmunk left the hall, he began to speak.

"Kraerion.", he said.

"Father." Kraerion answered dutifully.

"It's true then, you're really leaving what we've worked so hard to create?"

"What you created, you mean? You all pretend that this is news; I've always been different, even you said that I was born more squirrel than chipmunk. There's no secret of my extra shifts these last months either. If you didn't see, you refused to look."

"We all dream dreams, but that's where it ends. They are exercieses in growing up: things to smother to learn responsibility. What about your sister? You expect Pietas and I to go on forever?"

"Veritas is smarter than us three combined, she could take over tomorrow if you let her."

"And what about Cinnamon?"

"Don't", he said flustered, "I've already bought the birch, Redrill will make it ready today. It's done, it's already done."

Before he knew it, he was running. Running from the hall. Running, running, running.

He turned around and ran.
He ran, and he ran, and he kept on running until the pain in his lungs numbed the thoughts that so rudly had occupied his mind.


%Supram had procured a piece of a great Silver Birch overlooking a clearing central in the forest. It was pigeon territory, but they had been easy to persuade with the many screw-nuts he'd brought. He had made an appointment with a woodpecker known as Redrill, who was to excavate a home high in the birch. They had agreed to meed when the sunshine stood in line with a tall spruce at the entrance E3 to the tunnel network. The sun had far still to travel to that point and Supram felt at unease as one does with the prospect of the inevitable life changing event ticking closer. "I might as well get my things ready" he thought and left the hall in direction for his burrow.\\

%Chipmunks are usually gatherers and known to eat seeds, nuts, berries and even grass, shoots and other plant material. With the event man leaving the forest, a sort of calmness had arose letting the animals cooperate and specialize to a greater extent. Many animals are great gatherers, but no specie is as great at carrying feed as the chipmunks. In their stretchable cheeks they may carry large quantities of feed without slowing down their speed and while other animals gathered feed, the chipmunks transported it almost like the freight industry of man. In the winter they stored food for the whole forest deep underground and rationed it to last the winter. \\
