\chapter{Diversion}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“The struggle of man against power is the struggle of memory against forgetting.”
		\begin{flushright}- Milan Kundera \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

%one could argue something similar could be said of those who paid into the winter fund, but they could hide under the name of soldiarity

It may be easy — in places of kind latitudes, or in times of modern comforts — to forget the implications of seasons. The beautiful autumn fires had raged for weeks in the forest's canopy; but now the leaves were falling, a red and orange carpet to invite the forth and final season. 
%Indent
When Man first left the forest generations ago, the animals come together, in the glade of representatives, with a singular purpose in mind: to survive winter. It was an idealistic time, and a crow had uttered the phrase: "No flake of snow shall fall, til every Animal seeth a path to spring.", to a roaring glade - drunk of hope and future prospects, and thenceforth it became known as the crow's law. But, more importantly, it became legend - the story every mother told their kitten, pup, or bunny - and the backbone of moral.
%Indent
No matter how beautiful the law appeared to the first animals, reality seldom bends to beauty; and it had some very real practical limitations.
There were simply too many an animal to listen to them all; but even so, the fraction animals that did speak, had a tendency to refrain from sharing the truth. It requires little difficulty to imagine why an animal would not stand up, in front of the whole forest, and all potential mates, and declare himself incompetent - to advertise his inability to survive the winter without aid. 


%There had long been a custom for the animals to hold an annual meeting the day after the first frost. A moment to finalize the winter preparations, before activity contracted to survival speeds. The autumn colours of fire had fallen from the trees and only rotten leaves remained, like ash, to tell of its tales. The nights grew longer and colder; eventually frost was inevitable. The forest had prospered since the time of men, but winter was still winter - the unprepared would not live to see the spring. 
 
"Craax, hares!", Eaglewing cried tiredly, without his usual tact, as the fifth hour in the glade began, "Thou art next Snowball."

%"Hrm", Snowball uttered as he took a step forward. He looked anything like a snowball, still wearing his brown coat. His beauty was concealed and dormant, but in the next few weeks his fur would transform into a magnificent white coat, the sort of white whom even the snow were jealous of. "Our burrows are filled to the brim with hay. But you all know us, we'll manage to scavenge for food even in the thickest of snow. Our warren will be safe this winter."

"Okey", the hare, who looked nothing like a snowboll, said; but over the coming weeks he would, as would the forest, gain a beautiful coat of white. "Well — yes, we hares are very well prepared. We've estimated that we collectively have 10\% more produce than the year before. And, like the years before, most of us have paid into the Winter Fund as well."

"And dost thou speak for all the hares?", Eaglewing asked, as this was feasible way to comply with the Crow's law.

"Inasmuch as I'm aware."

"If any hare doth not feel spoken for - speaketh now!"

"...so the hare seeth a path to spring." Eaglewing continued when no one spoke and they moved on to the next speaker. And so it went on for many an hour. 

The species in the forest varied greatly in their independence; whilst the hares, rabbits, and chipmunks only required one speaker each, there were just as many on the other side of the spectrum. For instance, all the magpies and roebucks represented themselves, each outbragging the next until it bordered on the ridicoulus. The moles, who did speak their own peculiar language and did seldom partake in forest functions, also lined up the share their story individually; although, they all said a variation of the same sentence: "Ic hæbbe fōda nôg.", and thus went rather quickly.


%The moles, who did speak in their own language and did usually not partake in functions, all lined up to share their status; although, they all said a variation of "Ic hæbbe fōda nôg." and thus went rather quickly. The magpies, and the roebucks, did also all speak, but it did not go as quickly; they seemed to treat it like a bragging con
%Eaglewing seemed content with his answered and continued by calling up the next speaker. 

%Unlike the emergency meeting regarding theft the meeting of the first frost followed a dull routine. 

%Ultimately the animals were individuals against the winter, but their sovereignty ranged over a broad spectrum. On one extreme stood the rabbits who slept in the same hill, pooled digging labor and grazed in large numbers. So only Zefrafal was called upon to speak on the warrens behalf. On the other end were the roebucks who would almost beat each other to death if met during the wrong during the wrong season. Every single buck were thus called upon to speak. A task both time consuming and pointless as bucks were more concerned with boasting their zeal than reveal any concern about any shortages. The rest of species fell in between the two.

%The sun was about to set when only one speaker remained, save for the crows themselves of course. Most animals had stopped listening long ago. The remaining and last to speak was Aequitas of the chipmunks, as was custom since no one knew better than him how much had been transported and stored underground.

The sun was setting by the time all had been spoken for, save for the crows who never spoke. Now only an update of the winter fund remained before the animals could return to their burrows and nests.

"Before I leave the word to Aequitas and the Winter Fund, let me leave this final remark", Eaglewing said, as he regained his tact,

"Every year we gather here, and nigh every year we are better off than the one before. Incrementally quality of life improveth, each year invisible to the eye; nonetheless the generations, in aggegate, since our humble beginnings are visible: the destitute of the savage Animal be now extinct!

Oughtn't we to be content with our progression? Oughtn't we stand in awe - admire our accomplishments? No, we ought to always strive for more - for better; and we have by no means inherited a perfect system. We're at the whims of our market, it ebbs and it flows, but it is never stable - and we suffer for it, when value be erased, jobs be lost, and progress must reset. And even worse: unfairness be innate to markets, its abudance is distributed according to power law — to wit, as the words of Man's God saith: whoever hath, more shall be given; whoever hath not, even that shall be taken away.

No, we oughtn't be content with our progression! And the first step have already been taken, to stabilize market demand and at the same time aid our poorest percentiles. Namely, as ye already know, we imposed a small levy on transportation this last spring, with the funds going directly to the Winter Fund. This year everyone be covered, independent of means: whoever hath not, will hath. But I must assure ye, but a temporary clause in this time of transition - those who hath paid their premiums will hath a priority in payout in the unlikely event of the Fund running dearth of feed."

The crow with the brown wing looked around for a while, gauged the response from the animals. He looked pleased, and he continued:

"Thou hast waited patiently, Aequtias; conclude this a-gathering with thy Winter Fund update - have we naugth to fear these a-coming winter months?"

"Thank you, Eaglewing," Aequitas said as he took a few steps forward; and with that action it became apparent to certain animals, including Kraerion, what he wasn't: in the company of Vertias. "As you were saying, with the proceeds from this new taxation we've recorded record levels of stored feed. Even further, the level of churn of existing customers now when everyone is technically covered anyway-albeit with a lower priority-have not materialized."

"So thou sayest-to be explicit-we have naught to fear this winter?"

"Yes, indeed - that is what I am saying."

"I thank thee! If no one else hath something to contribute, i'd regard winter as welcome and this —"

"Oh, hold it Crow, I do believe you're forgetting something!", Aesop cried assertively from somewhere out of sight. The animals around him moved away hastily as if to show no doubt of any association.
%"Craax", Eaglewing concluded, "Another prosperous yield. Before we part ways I would like to make a final remark regarding the --"

"Oh dost thou?", he answered glibly, "What have I forgotten, please elighten us!"
%"I think you're forgetting something", Aseop cried as he slowly moved from the outskirts of the glade to its very center. His smell of rot and death made the stomachs of those whom he passed turn. 

%"Oh no, I don't think I do.", Eaglewing said giving of a sly smile, "Please enlighten us."\\

"Quit the theater Eagleshit; you've not become senile and you — and everyone else in this damned glade — know to what I'm referring to."\\

%"Oh, I do?!", Eaglewing said amused. He owned the air and he knew it, so he let tension build before he answer, "I'm sorry to disappoint you, but you'll have to be more specific."\\

"Oh, I do?", he chuckled amused, "well then, could thou be a lamb and remindst the rest of us of what we already know?"

%"So it's theater then, huh, I'll give theater if that's what you want.", Aesop cried loudly. He crawled up on large rock next to the oak as to be in height with Eaglewing, but instead of facing Eaglewing he turned and faced Zefrafal. "I hold Zefrafal to be an honest and trusted animal, if you agree say aye."\\

"Theater it's then, let the records show that theater was never my intent", Aesop said calmly and moved towards a rock near the center of the glade; he climbed it and became at a height with Eaglewing, but instead of addressing the crow he turned to the rabbit Zefrafa.

"Is it not true that Zefrafa is as trustworthy and credible as any other Animal present in this Glade?"

%A low murmur of ayes filled the glade, it appeared to be unanimous.\\

Some of the animals nodded, others muttereda a 'yes' or an 'aye', and a lone 'hear, hear'. They were in agreement: Zefrafa was trustworthy.

"I though as much", Aesop said, "Zefrafa, could you answer me this: the leaves we did exchange for our screw-nuts this last summer, weren't they but a temporary mean to stop theft?"

"Yes, that's true", Zefrafa said puzzled, cleary not aware of whatever Aesop had planned.

"And, haven't crime been absent for quite a while now — not even once since the exchange was made?"

"Yes, that's indeed also true."

"Would it then not be in order, to return to the screw-nuts as it was decided, or was it never intented to be temporary?"

%"Thank you", Aesop continued, "Zefrafal, is it not true that the leaves given to us in exchange for our screw-nuts were only a temporary measure to combat crime?"\\

%"Yes", Zefrafal said puzzled, "I mean no... It is as you say."\\

%"And is it not also true that there has been no crime in since our last meting?"\\

%"That is indeed also true."\\

%"Is it not then in order for us to once retrieve our screw-nuts that was to us promised? Should we not be expected to demand what is rightfully ours?"\\

%"Seize him!", Eaglewing cried and before Aesop had a moment to blink he was surrounded by stoats. The stoats were still only mere adolescents, but their specie's fierce reputation made them appear taller than they actually were. 

"Seize him!", Eaglewing screamed, and within seconds Aesop were surrounded by stoats. The stoats were still mere younglings, yet their ferocity were without question; their weight naught but tooth and claw. "Dost thou take us for fool? The theft has stopped \textit{because} of the leaves marking; and if we'd return to the screw-nuts, thou couldst just begin a-stealing again. Anyway, dear Animals, the evidence is plain enough - Aesop were the theif all along — why else would he care so deeply of the reinstatement of screw-nuts?"


%"So this is your little trick, Aesop?", Eaglewing continued, "I must say I'm very disappointed. You expect us to just return back to the screw-nuts, so you continue stealing without repercussions. This, my fellow animals, is all evidence I need. Aesop is the thief we've been searching for. why else would he so deeply care for the reinstation of the screw-nuts?"\\

% You expect us to return to screw-nuts so you continue stealing.\\

%"Because, I DO NOT TRUST CROWS, that's why!", Aesop cried whilst spinning around in a circle, flashing his claws, as to not let any stoat close to his back.

"Because!", Aesop cried whilst spinning around in a cricle — claws flashing — not exposing his back to the same stoat for more than a second at a time, "I DO NOT TRUST THE SCHEMES OF CROWS!"

%Aesop saw his chance, he bolted for the opening the attacking stoat had left

%Then everything happened very quickly. One of the stoats leaped forward, reaching with his left paw for Aesop's head. The blow caught him clean in his right chin, the extended claws cut him deep and blood flew. Aesop did not flinch, instead he leaned in towards the blow swirling his head around, catching the young stoat by the neck with his teeth. A loud snap filled the glade as the neck gave way. Before the stoat had fallen to the ground, the others were on him from all angles. Aesop kicked them off as best he could and ran in full throttle away from the glade, the stoats in full pursuit leaving their dead brother behind.\\ Like the tail of a kite

Then things happened very quickly. The stoat behind Aesop leaped forward, claws reaching for the badger's back. Aesop spun, but not quick enought, and the blow caught in his right cheek, just below the eye. Blood flowed, yet Aesop did not flinch; instead, he turned his face towards the blow and—before the stoat had a chance to get away—caught the stoat by the neck with his teeth. The neck snapped and the brave youth were no more. The injured badger saw his chance: he bolted for the opening the attacking stoat had left behind but the other stoats were on him. He ran for his life, away and out of the glade; the stoats in full pursuit like that of a tail chasing its kite.% that of the tail of a kite.
  The dead stoat remained in the center of the glade, the grass drinking itself red. Dead silence filled the glade, yet it screamed like never before.% The glade appropriatly in dead silence, yet it screamed louder than ever before.

"Craax."

Eaglewing's crow broke the silence like so many a time before. But instead of speaking, he calmly put his beak under this deformed brown wing—cleaning it without haste. Strained silence were to him but crowfood. "Let this be a lesson ye learn as it's nonce taught. ""
Aesop is guilty of the thefts this spring - as evident by what this Glade hath witnessed here today. He be sentenced to be beyond law - an Enemy of the Forest - and free to be killed by whomsoever feeleth need. Yet screw-nuts are like oxygen to Aesop and those similarly inclined; he may lurk in the shadows for monhts without trace or risk of capture. Therefor I must decree that henceforth: 

	All forms of private hoarding of screw-nuts, including those used as ornamentation, sentimental piece, or otherwiste tertiary usage, shall be forbidden. All Animals are hereby required to deliver on or before the first snowfall, to this Glade of Representatives or to me or any crow in my service, all screw-nuts now owned by them or a-coming in to their ownership. Upon delivery the screw-nuts shall be redeemed by equal worth in leaves. Omission to comply with this Order will, if deemed done unknowingly be subject to a fine not exceeding five leaves; however, if deemed willful the subject shall be sentenced to death by stoat.

%"Craax", Eaglewing crowed and calmly snatched a feather on his brown wing with his beak, "Let this be a lesson to you all. This is what happens to criminals."

%"Further, this situation calls for immediate action, I have no other choice. All trade in screw-nuts shall be illegal and all private hoarding of screw-nuts, including those used for decoration, shall be forbidden. All screw-nuts must be delivered to this oak tree on or before tomorrow at midnight. Any violation shall be regarded an accomplice and an enemy of the forest."