\chapter{Duplicity} % 10

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “What you do speaks so loudly that I cannot hear what you say.”
        \begin{flushright}- Ralph Waldo Emerson \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}


The Old Oak stood eerily grey in the otherwise lush Glade of Representative. Its stiff leafless branches swayed naked in warm late spring breeze. The massive trunk, now hollowed out and riddled with newly excavated apartments, had sustained too much damage to pump nutrients to the canopy. Rot had began to toke hold, and larvae of all kinds feasted blindly on its dying roots.

But to Eaglewing, perched high on a barren branch, rot was simply the price of progress.
He looked down upon the Glade with a profound swelling pride. \textit{``We've done it!"}, he thought to himself. The vote had passed just over a month ago, and his many plans to better the Forest was in full motion. He peeked up to the sky, \textit{``Look father, look have far we've come."}

Below him, the quite glade was broken by the heavy, rhythmic panting of three sturdy roebucks. They were dragging a massive, rectangular slab of limestone across the grass.

``Where do you want this?" the largest roebuck grunted, catching his breath as the trio stopped to rest.

``At the opposite end of the Glade," Eaglewing answered, his voice commanding, channeling authority. ``And raise it on its short side, so it stands tall."

``And, how do you expect us to do that? the roebuck responded irritably. Eaglewing gave him a stern look, and the roebuck quickly added, ``Nevermind, we'll figure it out." The bucks lower their heads, and continued to haul the stone.

Eaglewing watched them go with an amused, sly grin. \textit{``Try to forget me now"}, he thought as his mind drifted to his childhood, and everything he had endured. \\

Eaglewing had not always been known as Eaglewing. He had been born Óttarr, named after his father's great-grandfather. Even as a hatchling, his left wing---a dull, patchy colour of brown---stuck out like a sore thumb. A group of older, cruel fledglings had swiftly dubbed him ``Mudwing".

The nickname stuck, as ill-intentioned names tend to do. By his third winter, Óttarr had had enough. He went to his father, Ongenþeow, then the Twig, and wept over the cruelty of his peers.

His father had not comforted him. Instead, he offered cold, hard truth.

``Nicknames, especially those dispensed with malice, are like quicksand---the more you squirm, the deeper they sink." Ongenþeow had said, without even looking at his son. ``The solution, I reckon, is no different than to any other problem. It is solely an affair of shaping public oppinion. You must never directly oppose your peers; float along like a log in the river and wait for an opportunity. And, when opportunity arise, steer it in the direction of your chosing. When you learn how to control rivers, there is no lanscape you cannot mold, and no opposition you cannot erode."

Eager to gain his father's approval and to change his name, the young crow began to hatch a plan.\\

The first week he simply stopped taking offense when called Mudwing. The second week, he pretended to enjoy it. By the third week, he was loudly preaching to anyone who would listen about the magnificent maroon hues of mud, acting deliberately pretentious and high on himself. He was setting bait, giving the bullies a reason to knock him down a notch. He was moving the needle at a speed below perception.

He enlisted the help of his only friend, Brightbeak, keeping him in the dark about the true nature of the scheme. When the day finally came, Ottarr and Brightbeak were walking along the very fledglings who had tormented him.

``Eagles are the rats of heaven," Ottarr declared, unprovoked.

``No, they are not," snapped Thorn, the largest of the bullies. ``They are majestic. I've even seen one myself."

``I doubt that," Ottarr scoffed. ``I you had, you would know how incredibly ugly they are, with their dull, brown wings."

``But Mudwing," Brightbeak chimed in innocently, right on cue. ``Your wing is brown."

``No, my wing is a brilliant maroon!" Ottarr cried, feigning deep offense.

``No it isn't. It's the exact same color as the eagle I saw," Thorn sneered slyly, falling for the bait. ``You have an eagle's wing."

``How dare you compare me with one of those flying rats!" Ottarr shrieked, acting devastated.

``I think we know what this calls for," another bully laughted. Thorn caught on, grinning maliciously. ``Surely we do. Don't we, \textit{Eaglewing}?"

Ottar let out a wail of despair. He tucked his head under his wing and fled. Behind him, the bullies roared with laughter. They had found---or so they thought---his new weakness.

For weeks, they relentlessly called him Eaglewing. The yelled it across the glades to ridicule him; they whispered it when he walked past. Ottarr played hurt every time, scurrying away in shame.

But though the bullies were spreading the name with malice, the rest of the murder didn't understand the nature of the joke. When they heard \textit{Eaglewing}, they heard strength. When the younger females heard it, they heard valor. The name began to circulate through the branches outside of the group of bullies, completely stripped of its cruel context.

By the time the bullies realized that their name had backfired---it was too late. The public had adopted the name, and not even the bullies could change it now. When the bullies later went to confront Ottarr about his deceit, Ottarr simply thank them for their service, and flew away.

Ottarr won, and he would never have to be Mudwing ever again.\\

A heavy thud echoed throughout the glade, pulling Eaglewing abruptly from his memories. The roebucks had finally managed to heave the massive limestone block upright.

``It is done," the largest roebuck panted, his legs trembling from the effort. ``How do you intend to pay?"

``Excellent, my assistant shall see to it." Eaglewing replied. Turning his beak towards a trunk of the Old Oak. ``Thorn!"

A large crow appeared on the branch from within a hollow in the Old Oak. ``Yes, Eaglewing?"

``Thorn, canst thou see to it that these gentle-bucks get paid?", Eaglewing asked,  ``And also, canst thou fetch the best woodpecker for me, I pray thee?"

``Right away, Twig!" Thorn announced, gliding down to the forest floor to count the leaves.

Eaglewing watched as the exchange took place. Thorn was a lousy assistant at best, but having him around reminded him to never forget his past, and his first, sweet victory.\\

When Mudwing had successfully orchestrated his own rebirth as Eaglewing, Ongenþeow had taken a sudden interest in his sun. Realizing, that his runt of a deformed son, possessed a sharp and capable mind. He took Eaglewing under his wing, and began to groom him for office. They went on long flights far beyond the border of Wadborough Forest, past the meadows and farms, to places that could teach him of leadership.

On the very first flight, Ongenþeow took him to a city much larger than the Wadborough village. They had perched on the top of a chimney next to the city square. Below them, humans in pristine, dull-coloured suits hurried across the paved paths, carrying naught but thin leather briefcases.

``Notice how these humans do not plow the fields." Ongenþeow pointed out. ``They do not harvest grain, nor carry heavy loads, yet their squiggly lines on paper makes them prosper more than any farmer."

Eaglewing tilted his head, watching a man in a splendid navy suit run by. ``Why would the farmers agree to such an arrangement?"

``I don't know," Ongenþeow answered honestly, ``But, never forget this: hard work does not always guarantee success."

Before leaving the city, they flew down to a stone statue surrounded by pigeon droppings. The Plaque read: \texttt{Admiral Lord Nelson, 1758-1805}.

``Who is this?" Eaglewing asked, hopping around the statue.

``He is some kind of army sailor..." Ongenþeow gestured with his wing, ``But, look at the numbers 1758-1805. They tell us that he died a long time ago---many generations ago.
That's a difference between them and us birds, we only remember one generation back.
All our thoughts, all our accomplishments die with our fledglings---we do not get to leave a legacy.\\

Every Sunday for a year, Ongenþeow would take him to the church in Wadborough village.
He showed Eaglewing of a hole in the rafter, where they could climb in, and listen to the sermons.

``Humans believe that there is one God in heaven, that is almighty and all-knowing." his father told him, ``It's similar to how the moles believes that one day the whole world will be swallowed by dirt.
And, how the rabbits pray to the moon.
The humans have everything written down in a book, a collection of tales of God's will."

The priest in the church began to speak, and Ongenþeow lowered his voice. ``The tales are powerful in and of themselves---teaching the humans how to behave. But they also give the cloaked men power, as they are the ones to study and channel these tales. Apparently, a long time ago, the book was written in another language entirely, only the cloaked men could read it. That gave them complete monopoly of the words of God, as no other villager could parse His teachings without the cloaked men's help."

Eaglewing became obsessed with these tales of Man, and looked forward to every sunday.
He enjoyed the rhythmic cadence of the priest, how the tales affected the villagers. How they inspired them to lead better lives.

But, Eaglewing also noticed something his father missed. When the priest wanted to put extra weight on a certain point, he would bring out an older version of the text: \textit{The King James Bible}. It was the same book, but the words were slightly off.
The language gave a certain grandeur to its message, and it put the villagers into a form of trance.

Eaglewing was fascinated. Over the years, he began to practice the odd language---practicing the \textit{thees}, the \textit{thous}, and the rolling cadence of the ancient tales. When he later tried it on animals in the forest, the effect was instantaneous. The archaic grammar gave his speech a shine of truth; the animals heard tradition---they heard \textit{authority}. Eaglewing decided then and here to try to master it.\\

When Eaglewing was almost fully grown, Ongenþeow took him on the longest trip yet.
They flew for many days and nights, all the way to a massive city named London.

It was like nothing Eaglewing had seen before.
Millions of humans going about their day in a complex web of streets and buildings.
It reminded him of an enormous anthill, scaled to fit the size of humans.
He wanted to stay at a place with the name of \texttt{Trafalgar Square}.
Stay there and just \textit{watch} the swarms of human beings moving about.
But, his father had other plans.

Ongenþeow took him to the \texttt{The British Museum}, and in the cover of night, they broke in.
They flew through the long echoing corridors and halls, until they found what his father wanted to show.

``See here, Ottarr," his father whispered, standing outside a glass display case.
``Look at this incredible clay tablet."\\

\input{testcuneiform.tex}

``What do those weird crow-feet mean?" Eaglewing asked, his eyes twitching in anticipation.

``I do not know," his father answered patiently. ``It is a law that was written by a king very long ago, in a land very far away, in a language no one alive can speak. But the name of the king we still remember: it's Hammurabi."

``So, you can't read the law, father?" Eaglewing asked again, his disappointment showing."

``No,", Ongenþeow replied, his black eyes gleaming, lowering his voice to a hush. ``But \textit{what} is says is not important. The fact that it \textit{is}, is important.
This man, Hammurabi---he cheated death.
His thoughts are still here intact, in the most profound place in the most profound city in the world.
His words have survived through time, and will remain here intact as long as there are human beings."\\

Back in the glade, Eaglewing smiled at the memory of that clay tablet, and at the image of Admiral Lord Nelson.
A woodpecker---Eaglewing remembered him as Redrill---came flying into the glade, landing swiftly on the Old Oak's bark.

``You asked for me?" Redrill asked shortly, his eyes suspicious.

``Ah, Redrill!" Eaglewing exclaimed, ``Seest thou this limestone block, I want thee to chisel it with thy beak."

``Chisel stone?", Redrill asked surprised, ``But, that would take months..."

``Well," Eaglewing croaked, "Then thou hadst best begin!"

Eaglewing was going to do great things for this forest, he knew.
And, his only price was to be remembered; remembered in a medium not even Time could erode.

