\chapter{Discrepancy}

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “Concentrated power is not rendered harmless by the good intentions of those who create it.”
        \begin{flushright}- Milton Friedman \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}


The winter came early and hard. The migratory birds had long fled south to the more pleasant European---and even African---continents; the winter air was thus calm and quiet, save for the irregular cooing of the pigeons. The forest bed was covered in a thick layer of snow, its distribution made uneven by the wind and the trees. The animals hid in their burrows and lairs for most of the days, huddled close to preserve body heat. Winter was but a game of waiting---a quarter of life on pause.

Kraerion wasn't immune to cold either, and he had prepared meticulously for winter: insulating the inner walls of his hollow with moss and lichen. He had Redrill carve him a round wooden disc, which could be rolled in front of his entrance to keep the shy warmth hostage.
In the mornings, though, he pushed the disc aside; he preferred the cold to the darkness, and a life in motion to a life on pause. He had watched as the days shrank, the morning dew slowly morph to morning frost---a phenomenon difficult to grasp for a creature raised underground. And today---this particular morning---the sun rays danced for Kraerion's eyes on the unadulterated hoar frost covering the surface, seemingly stretching forever in every direction. A dance of free admission, open to all, yet but a lone chipmunk hunched in a tree paid to attend---and, in that moment, he was truly the richest animal in the forest.\\

The sun shifted and its rays intercepted by a pine, the dance moved on to other glades. Kraerion's mind wandered to the events in the Glade: the attempted seizure of Αίσωπος, the death of the young stoat, and the Decree. The now outlawed badger had never officially been apprehended, and no one knew for sure where he was.
Nevertheless, many a rumour spread like wildfire that early winter. "He had been caught, killed, and buried by the stoats!", he had heard Spinestack boast to Greyhead.
"No, he is still in hiding in some old forgotten badgers' lair deep underground---biding his time!" Greyhead had conjectured back to Spinestack.
"No, he sought out supporters to his cause, roaming the marshes to the east of the forest and preparing for war!", a Robin had chimed to anyone who would listen as he flew by Kraerion's birch.

No one had definitive proof of their claims, yet the animals argued incessantly about it. Kraerion didn't know what to make of it himself. He didn't know the badger personally---no one truly did---but he had always appeared to him to be an animal of reason. He couldn't wrap his head around how quickly Eaglewing had reached a verdict. Could Αίσωπος really be that cut-throat?\\

His morning conundrum was abruptly disturbed by Cinnamon who suddenly, hastily entered the glade, in stark contrast to the leisurely pace of that late summer morning. This time she didn't stop at the base of the birch; instead---to Kraerion's surprise---she sprang up it without hesitation, her claws tearing at the bark in her urgency. When she reached the hollow, she was breathless, her small chest heaving as she fought to recover. She didn't have to speak for Kraerion to realize she came with news; and looking into her pearl black eyes, he saw that the news was grave.

"Veritas is dead", she finally mustered, still panting, "I think you better come."

They ran back together through the winter silence which no longer appeared nearly as beautiful as it had just a few minutes before, only heavy. They entered the run and Cinnamon led the way through the many twists and turns that were slowly fading from Kraerion's memory.
When they finally entered Veritas's spartan burrow, they were both out of breath. "There's too many chipmunks for this space...", Kraerion thought to himself as he pushed past the scurry with Cinnamon on his heels, "too many damn chipmunks."
He saw his father leaning over his sister's lifeless body---his forepaw gently resting on her chest. Pietus was also standing there; he looked up when they approached and gave them a silent nod. Aequitus didn't notice them or didn't care to show if he did.
Kraerion suddenly felt a cold thought creeping up his spine: "Even in death, she had defied Nature. animals seldom die in burrows; they seek a quiet, open space for their final rest. Veritas, however, chosen this confined space---sealing herself in with the very truth she preached."
Overwhelmed with emotions, Kraerion finally had enough. "Get out of here!", he screamed suddenly, the ferocity of his own voice surpised him, "Get out of here, all of you!"

When no one moved a limb, Aequitus finally looked up from Veritas's body. "You heard him", the Cheif bellowed, his voice ragged but commanding, "Get out!"

And so the chipmunks did---revealing that Kraerion's voice no longer carried the same weight as it once did. As the burrow emptied, Cinnamon turned to follow, but Kraerion quickly placed a paw on her shoulder. "Not you", he whispered, "stay with me."

When only Aequitus, Pietus, Cinnamon, and Kraerion remained in the burrow, they remained in silence. It was a heavy silence, as if by not speaking they could somehow deny the reality of the situation.

"What...", Kraerion asked at length, his voice trembling, "what happened?

"I..., she. I don't", Aequitus stammered, "I... I think she starved herself."

"What do you mean?", Kraerion asked confused, "She couldn't---why would she starve?"

Aequitus looked like he was about to speak, but the words died in his throat, a single tear rolling down his cheek before he turned away.

Pietus sighed heavily, "It's hard to say for certain what was going through her mind. She was... agitated. She was angry with the Crows, but mostly with me and your father. She had this notion that the Winter Fund was underfunded--- that we needed to sound the alarm immediately. The rest of us disagreed."
Pietus paused, glancing at Aequitus for input; when none came, he continued, "She threatened to disclose her concerns to the forest. We... we found it necessary to confine her to her burrow on the day of the assembly in the Glade. After that, she became withdrawn. She began rationing her feed---a silent protest to show what we all ought to be doing. We never imagined she would take it this far."

"Why did no one think to tell me?", Kraerion asked, now angry, "We could have saved her!"

"I \textit{did} tell you Kraerion", Cinnamon interjected gently, trying with all her might to keep compassion in her voice, "Do you think it was easy for me to seek you out after you left like you did? I told you she was struggling... but you chose not to hear."

"Feed is dialectic; hunger is constant. The delta must eventually reverse." Kraerion whispered, recalling that summer morning. The anger in him deflated instantly, replaced by a heavy pain of guilt in his chest. "But, I still don't get it", Kraerion begain again, "What would make her think the Winter fund was underfunded?"

``Well, it's a bit complicated", Pietus answered, rubbing his temples, "But, I'll try to do justice to Veritas's argument. When the swap from screw-nuts to leaves happend, there was a liquidity crisis of sort. For example, we paid the moles this year to widen the eastern tunnel, but since we had to convert our screw-nuts to leaves first, we had to postpone the project a week or so."

Pietus gestured vaguely with a paw. ``Similar projects got delayed all over the forest, causing economic activity to slow down. When demand falls, so does prices; and when prices fall, animals tend to hold back on spending in expectation that prices will drop even further. It's a vicious cycle Veritas explained."

``Sounds very reasonable to me,", Cinnamon said, "Why would you stop her from telling the Forest?"

``Because she was a fool!", Aequitus suddenly exploded, his voice echoing through the burrow.
``She might have been the brightest chipmunk, near erie grasp of our economic system, but when it came to Animals, she was a fool!"
He paced the small burrow, his shadow flickering on the earthen walls. ``She thought we could just \textit{tell} them‽ That Animals are just this all-loving cooperative bunch of beings, surely no one could be so impolite as to get upset when they learn their kin might starve to death? No... It would have caused pandemonium! Chaos! Fighting in the glades! It's unfortunate, but if you strip away this thin veil of civility, we are but nasty, brutish beasts in the state of nature!"

``I'm sorry...", Aequitus sighed, his anger spent, "It's unfair to her. She was right about the Winter Fund, just not the way to fix it. She's gone now... gone forever.".

``It's not that we didn't listen to her.", Pietus added, ``On the contrary, we heeded her warnings. We sought help from the crows, and they took the warnings seriously. They provided us with more leaves on the spot, and arranged for a line of credit to be set up in case we needed more funding. The problem has been to find more feed to buy, here again the crows have been helping us, brokering a deal with the beavers that had some extra feed stored this winter. Br'r Rabbit has also been helping us, his scouts have been going nest to nest looking for surplus feed to buy."

Pietus paused to take a deep breath, ``So you see Kraerion, we have done everything in our power to heed Veritas's warnings; it may be a winter of  dearth, but we've given the Winter Fund good odds of making it through."

Silence claimed the burrow once more. There was nothing left to discuss; economics could not reverse death, nor could self-pity fill a belly that had ceased to hunger.

``We must bury her...", Kraerion said at length. He felt a heavy ache in his chest; usually, the dying slipped away into the night to pass alone, not here among the living. ``Before her body starts to..." He didn't finish the sentence; he didn't have to.

They wrapped Veritas in her bedding, a humble shroud of woven grass and dried moss. It took all four of them to maneuver her lifeless body through the narrow twists of the runs. The walls felt suffocatingly tight as they dragged the bundle upwards. Reaching an intersection of runs, they met a couple of chipmunks coming the other way.
``Hazelpaw," Pietus greeted one of them, ``could you fetch one of the moles and a blackbird, and have them meet us at the grey willow?"
The chipmunk nodded and hurried away. When the group emerged into the white glare of winter, the sun was beginning to dip, casting long, mournful shadows across the snow.

The scurry made their way to the grey willow; Aequitus dug away the layer of snow only to find the turf beneath frozen solid.

``I'm glad we ran into Hazelpaw", Pietus muttered, ``We'll need the moles to dig the grave."

The wait for the mole was agonizing. The cold gnawed at their fur; Cinnamon huddled close to Kraerion, shivering against the biting wind. It wasn't long, however, before the snow shifted nearby. A mound of earth erupted from the white blanket---shattering the pristine surface. A black snout appeared, followed by massive spade-like paws.

``Hwæt?", the mole grumbled, ``Hwȳ wēccest þū mec of mīnum slǣpe?"

``We're sorry to wake you from your sleep, Burrowfoot", Aequitus began, ``But we need a grave, and our claws don't cut it in this frozen ground. Of course we'll compensate you well for the short notice."

``Nā", Burrowfoot grunted, ``þis is hūsgifu."

And the mole set to work immediately, his powerful paws throwing up clumps of frozen earth with ease. The blackbird arrived shortly after; perched silently on a nearby branch, he observed the proceedings with solemn eyes.

When the hole was deep enough, the chipmunks gently lowered Veritas's body into the grave. The blackbird needed no instructions; he began to sing a mournful melody that echoed through the cold winter air.\\

Cheeks are empty, cold and still, Sleep beneath the quiet hill. Digging done and running past, You are home and safe at last.\\

Leave the burden, leave the load, Travel down the final road. To the Harvest, rich and deep, While the living wake and weep.\\

Join the roots, become the seed, Free from hunger, free from need. Cheeks are empty, cold and still, Sleep beneath the quiet hill.\\























