\chapter{Diversion}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“The struggle of man against power is the struggle of memory against forgetting.”
		\begin{flushright}- Milan Kundera \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

It might be easy---in places of kind latitudes, or times of modern comforts---to forget the implications of seasons. The beautiful autumn fires had raged for weeks in the forest's canopy, and now the leaves were falling; a red and orange royal carpet to invite the forth and final season.

When Man first left the forest many a generation ago, the animals came together in the glade of representatives with a sole objective: to survive winter. It was an unprecedented time, never before in the history of animal had they been free and able to meet as equals. It was a frenzy of excitement, a glade drunk on future prospects, a crowd eager to hear the words a crow uttered: "No flake of snow shall fall, til every Animal seeth a path to spring". Words that once said could not be unspoken, irrevocably written into the cultural fabric of the forest---a phrase that became known as the Crow's Law. But, more importantly, it became \textit{legend}---the essential moral in the tales that every mother told their kitten, pup, squawk, or bunny.

No matter how beautiful the law appeared to the first animals, reality seldom bends to beauty; the law was rather burdensome to implement and straight insipid in practice. There were simply too many an animal to listen to them all; but even so, the small fraction of animals that did speak, had a tendency to refrain from the truth. It requires little difficulty to imagine why an animal would not want to stand up, in front of the whole forest---and all potential mates---and declare himself incompetent: to advertise his inability to survive winter without aid.

Nevertheless, it was \textit{law}. So the day after the first frost, the animals gathered---as the first animals had done---in the glade for their annual pre-winter meeting.\\

"Craax---Hares!", Eaglewing cried tiredly, without any of his usual passion for the spoken word, as the fifth hour in the glade began, "Thou art next, Snowball."

"Okay,", the hare---who looked nothing like a snowball---said. But over the coming weeks she would---as would the forest---reveal her dormant beauty and gain a gorgeous white coat. "Our burrows are filled to the brim, we've estimated that we have collected approximately 10\% more produce than yesteryear. And, like always, most of us have paid into the Winter Fund as well."

"And dost thou speak for all hares?", Eaglewing asked, as he had done---verbatim---many a time before, as that was the exact phrasing that was deemed to comply with the Crow's Law.

"Inasmuch as I'm aware.", Snowball answered, which equally was the custom hedging response every animal who spoke for more than herself used.

"If any hare doth not feel spoken fore---speaketh now!"\\

"...let the record show that the hare seeth a path to spring.", Eaglewing continued in the still heavily scripted language before moving on to the next speaker. And, so it went on for hours.\\

The species in the forest varied greatly in their independence; whilst the hares, the rabbits, and chipmunks only required one speaker each, there was just as many on the other side of the spectrum. For instance, all magpies and roebucks represented themselves, each outbragging the next. The roebucks were particular notorious for their bragging, since their natural horn jousting had been outlawed, their need to dominate each other had found its way to this moment and their tales bordered on the ridiculous. The moles---who spoke their own peculiar language and seldom partook in the forest's func- tions---also lined up individually. Although, they went quickly by, each proclaiming a variation of the same sentence: "Ic hæbbe fōda nôg."

The sun was setting by the time all had been accounted for, save for the crows themselves who never spoke. Now but an update from the Winter Fund remained before the animals could head back to their burrows and nests.

"Before I leave the word to Aequitus and the Winter Fund, let me leave this final remark.", Eaglewing began, as he regained his usual tact,

\input{eaglewing_speech_2.tex}

The crow with a brown wing looked around for a while, gauging the response from the animals. He seemed pleased, and he continued:

"Thou hast waited patiently, Aequitus. Let us conclude this gathering with thy Winter Fund---have we naught to fear these coming winter months?"

"Thank you, Eaglewing.", Aequitus said formally as he took a few steps forward. With those steps, it became apparent to certain animals, including Kraerion, what he wasn't---in the company of Veritas. "Uhm, yes, we have indeed a record level of produce in our stores. And our low year-over-year churn have dropped even further. The fear of churn with the once rumored---now proclaimed---forest program, have thus, albeit early, not materialized."

"So thou sayest---to be exlicit---we have naught to fear this winter?"

"Yes---that is indeed what I am saying."

"I thank thee! If no one else hath something to contribute, I regard winter as welcome and this meeti---"

"HOLD IT CROW!", Αίσωπος cried assertively from somewhere out of sight. The animals around him moved away hastily; again, less from his hideous stank, but rather to show no doubt of any association with him. "I do believe you're forgetting something."

"Oh, dost thou?", Eaglewing answered glibly, "What have I forgotten, please enlighten us!"

"Quit the theater Eagleshit; you've not become senile and you---and everyone else in this damned Glade---know to what I'm referring to."

"Oh, I do?", the crow chuckled amused, "Well then, couldst thou not be a lamb and remind the rest of us of what we already know?"
%should it be remindst 

"So it's theater then---I'll give you theater, but let the record show that this was never my intent.", the badger said, he crawled up on a rock next to the Old Oak as to be closer in height with Eaglewing, but instead of facing the crow, he turned to Br'er Rabbit. "I hold Br'er Rabbit to be an honest and trusted member of our Forest, do the Animals in this Glade agree?"

Some of the animals nodded, others muttered something akin to a 'yes', or 'aye', and someone chimed in with a 'hear hear'. There was no doubt: Br'er Rabbit was trustworthy.

"I thought as much.", Αίσωπος said, "Br'er Rabbit, can you answer me this: the leaves we exchanged for our hard earned screw nuts, wasn't it but a temporary means to stop theft?" 

"Yes, I suppose that's true.", Br'er Rabbit said puzzled, unaware of what Αίσωπος might have planned.

"And, haven't crime been absent for quite a while now---not even one recorded case of theft since spring?"

"Yes, that's indeed also true."

"Well, isn't it then in order for us to return to the screw nuts as it was decided---or Eaglewing, was this never intended to be temporary?"

"Seizeth him!", Eaglewing bellowed, and within seconds Αίσωπος was surrounded by stoats. The stoats were still merely more than kits, yet their fierce nature were without question: their weight but red in tooth and claw. "Dost thou take us for fools? The theft has stopped \textit{because} of the transition to leaves; if we return to screw nuts, thou couldst but begin steeling again. Here, fellow Animals, the evidence be self evident---the screw nut thief be standing before ye. Why else would he careth so deeply about the reinstatement of screw nuts?"

"BECAUSE---", Αίσωπος roared whilst slowly spinning around in a circle---claws unsheathed---as to not expose his back to the same stoat for more than a moment at a time, "I DO NOT TRUST CROWS!"

Then everything happened very quickly. The stoat behind Αίσωπος leaped forward, his claws reaching for the badger's back. Αίσωπος spun around, but not fast enough, and the blow caught him in his right cheek, the claws cutting deep. Blood appeared, but the badger did not flinch; instead, he leaned his body and face into the stoat and---before the stoat had a chance to flee---caught its neck in his teeth. A loud crack filled the glade as the neck gave way and the brave youth was no more. The now injured badger saw his chance: he bolted for the opening in the circle that the dead stoat had left behind. Before the dead body had touched the ground, the other stoats were on him from all angels. He ran for his life, away and out of the glade; the stoats in full pursuit like that of a tail chasing its kite.

The dead stoat just laid there in the center of the glade. The grass soaking itself red. Dead silence entered the glade, and it screamed like never before.

"Craax.", Eaglewing croaked, but instead of speaking he calmly put his beak under his discoloured brown wing and started cleaning it. He took his time and showed no hint of haste---he appeared completely detached or undisturbed by the event that just transpired. He told his threat with silence. "Let this be a lesson ye learn as it's nonce taught. Αίσωπος be guilty, as witnessed here today. He be beyond law---an Enemy of the Forest---free to be killed by whomsoever feeleth desire. Yet screw nuts are like oxygen to Αίσωπος and those similarly inclined; he might lurk in the outskirts of the Forest for months without trace or risk of capture. Therefore I must decree that henceforth:"

\input{executive_order.tex}

%Value is subjective; yet the function of value is not. It's the pragmatic process that converts hours to feed and shelter; it's objective and as true as the market rate for a commodity at the world's exchanges. What originated from a subjective quality, from beauty, or scarcity, or whatsoever attribute; becomes its arbitrary objective function. No matter what form it takes, it's value: its illusion proven, tangible and true. Nevertheless, illusion and delusion are kin. And, if its original quality dissipate, its function remains the same, delusion grows stronger---until the rug is pulled, and it all comes crashing down.
