----\\
Alternative 2 \\

The young crow waited patiently for the right opportunity. And, one day he heard a rumour of a lost vixen in a meadow close to the forest's edge.
The very next day, Ottarr flew to the meadow where the vixen had last been seen. There, he found a starving, desparate red vixen pacing near the tree line of the forest. Foxes are opportunistic omnivores and would hunt crows given the chance, but Ottarr did not flinch. He perched just out of leaping distance and made a proposition.

``I know where a human farmer left the chicken wire loose," Ottarr croaked calmly. ``How does a chicken feast sound to you?"

``Tell me!", the vixen said eagerly, her mouth watering.

``Sure, but first you must help me."

He instructed the vixen to wait in the tall grass nexr the lower branches of the Old Oak at dusk the next day---the exact time and place the older fledglings usually gather. The vixen was not to kill, only corner and terrify the bullies.

Ottar sat quietly on a lower branch of the Old oak, waiting for his plan to unfold. Suddenly, the tall grass violently parted. The vixen lunged, its jaws snapping shut mere inches from the lead bully's tail feathers. Panic erupted, all the fledglings scattered blindly in all directions. Except the lead bully, he was trapped by the vixen, his frontpaw pinning him to the ground.

The vixen showed her teeth, playing her part perfectly.

Above, perfectly aligned with the dying setting sun, Ottarr made his move. He leaped to an exposed branch in the oak and spread his wings wide. His black right wing blended into the coming night, but his patchy brown left wing caught the light exactly as planned.

Against the forest floor, Ottarr cast a massive terrifying silhouette---the unmistakable, broad-shouldered shadow of a hunting eagle. Ottarr let out a piercing, shriek that sounded nothing like a crow. The vixen, genuinely spooked by the sudden shadow, tucked its tail and bolted into the underbrush, just as she had promised.

The glade fell silent, save for the terrified panting of the lead bully in the dirt below. Ottarr drifted down from the canopy, landing gracefully in front of the trembling bird. He folded his brown wing, like a knight sheathing his sword.

``Mud does not scare away foxes," Ottarr whispered, his voice cold and commanding. ``Eagles do. Now... what is my name again?"

The bully starred in the direction of the vixen, then at the brown wing, his expression caught between awe and sheer terror. He swallowed hard. ``E... Eaglewing."

From that day on, the name Mudwing was never spoken again.