\chapter{Deputation}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“the only thing we have to fear is fear itself.”
		\begin{flushright}- Franklin D. Roosevelt \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

A murder of crows sat comfortly hutched along the wast network of branches in the ever reaching crown of the old Oak Tree. They watched as the animals poured into the glade — the Glade of Representatives. Since the time of Man, the Council had gathered here to discuss public matters, to air oppinions, and to converge on decisions. Although the glade was too smal to fit all animals, and bore a suggestive name, it wasn't a republic in the human sense of the word. It was not a selected office, no animal spoke for a predefined set of members; instead, non-present animals had someone whom they trusted present, that could speak on their behalf when necessary — to represent them.
In fact, the meetings of the Council was open to all, and anyone who wished to speak could. The pheasants did not attend these meetings, as their concerns were of worms; not of words.
%Indent
Kraerion entered the glade and opted, in the spirit of his now arboreal life, to join the song birds among the twigs. As he climed a limb, he spotted Aequtias and Veritas standing with the rabbits; his heart dropped — as if caught with his paw down a beehive. His head knew his paws were free of honey, yet his body felt otherwise.
%indent
When the last bucks straggled into the glade, a crow signaled for them to start. The crow took a few hops out on the oak branch — to be seen by them all. He bore the name Eaglewing, as his left wing was discoloured: a peculiar colour of brown, not unlike the brown wings of an eagle. Eagles were a rare sight in Wadborough, but once seen, seldom forgotten.
"Craax", Eaglewing remarked, and began.
%A murder of crows sat eerily hutched along the wast network of branches in the ever reaching crown of the old Oak Tree. The animals had gathered in the glade directly in front of the tree. Not all animals could fit in the glade but all had some one representing them there with a few exceptions. Some of the smaller rodents and moles who barely spoke the common language. The pheasants were not there either, as they barely could comprehend the ground in front of them any conclusion would pass over their heads anyway. The song birds had found comfortable twigs in some elms surrounding the glade. Kraerion clung among the birds and he had noticed Ripell standing with a hare near the rabbits. They were the only two chipmunks present. A few laggards arrived one after another and with the arrival of a large buck, known to speak on behalf of the deers, the meeting could start. \\

%One of the crows took a few deliberate steps far out on an oak branch, so as to become visible for all in the glade. The crow was named Eaglewing, since he had a discoloured right wing, flashing of light brown like that of a white-tailed eagle. Seldom had the forest seen eagles, but stories of the mighty creature had been past down through generations.\\ once seen, they're seldom forgotten
%"Craax", Eaglewing began to remark his intention to begin.

"I am not the fool to deny, nor delay, the pretext of which we've promptly gathered here today. It's ever so important, in times like these, to be blunt: attack the issue at hand, with naught but truth, frankly and boldly. Not to belittle these challenges facing us; to met them but in earnest and with prudence.
%Indent
But first, fellow Animals, I would like to say this: it's in difficult times we get to show what we've been made of — our true morals and colour. And I am certain our true colours will show — in all of its magnificent glory. Our Forest shall endure, as it always has endured, since the time of Man and the founding of this very Concil. I am convinced we will, once again, unite agains our common foe — and earn a second wind with this imminent victory.
%Space

It's my firm belief that the fear itself is more dangerous than what we fear — wicked, dark, unsettling terror that have paralized every function of our Forest. A few stolen screw-nuts in themselves — insignificant in the greater scheme of things; an empty forest, a lack of trade, a hoarding of goods, and an arming and a guarding of one's own — are anything but. Our forest has reached a complete standstill in fear of theft; when it ought to fear the lack of feed come winter — fear of trade not dealt. We've retreated back into our humble nests and spartan burrows; now we must advance into action. Our Forest asks for action, and action you must allow us to take.
%Space

%regress to athoritarian, repressive tyrannical culprit

We may act against the perpetrator — root him out. We may wage a war of suspicion, with accusation as ammunition. And we may not. Even a victorious battle aganist the enemy amongst us may lead us to defeat — the loss of time. To while whilst winter marcheth.

Does such a measure — if successful — prevent any future crisis of this kind? No — ? We'd become a fragile forest — unlearned from scars past. When we must be the opposite of fragile; not merely unbroken and resiliant, but something that gains with every blow. 
Our reforms must likewise gain from turmoil and crisis; adapt from our scar-tissue and evolve as a Forest.

%Lest our scar-tissue bes in vain

%Indent
We are prepared to exhaust our full arsenal in meeting the challenge of this crisis. We are prepared to do more than that — prepared go beyond whats been deemed reasonable in histories pasts. And for that we need your support.
The first step in our plan will soon be explained by Vlahir. It concerns the act of trade itself — a constitutional force seldom tampered — so I ask you to listen with consideration. It may seem extreme, we know, yet we believe it to be the right path forward. I ask the Council for this final instrument to face this crisis — broad Executive power to make war with the emergency, a power that would be entrusted in me if our forest was in fact invaded by Man once again. 

%We shan't stand idle by,
%We shan't wait to make reply,
%None shall dare the law defy,
%All shall know the reason why.

I believe this to be the only path forward lest our Forest be reduced to dust and generations of progress be but in vain.

I can take but no credit for this ingenious strategy however; it's time for Vlahir to speak."

The glade was in silence when Eaglewing receded to a higher branch of the Old Oak tree; the sound that broke it was Vlahir, scrambling to take his place. Whereas Eaglewing spoke with a confident, well-paced certainty; Vlahir spoke with a twitchy, unregular uncertainty — although that was only his appearance — he was in fact very certain.

% Nor does such a measure prevent any furher crisis of this kind. No, we must be the opposite of fragile, not mere resilience, but something that gains with every blow — like pulling one end of a knot. We've devisted a path that we believe to be antifragile; however it concerns the act of trade itself — a constitutional force seldom tampered. It may seem extreme, yet I believe it to be the most prudent and right choice forward: I ask you the Council for this final instrument — broad Executive power, to win the war with this crisis, and would be granted to me if we were in fact invaded by Man once again."

%If you choose to grant me this power, we shall implement the course of action Vlahir will now lay before you."


% "We're all aware of whats transpired, prompting this vital gathering. A few of us, good and decent animals, have gotten their hard earned screw-nuts stolen from otherwise secure dens and burrows. Theft at this level, if I may remark, is unprecedented in our history since the time of man, the founding of this council and the proclamation of our laws." He spoke with a deep solemn tone, pacing himself to give weight to his words.

%"Nonetheless, these recent events will require us to act, and to act swiftly we must to insure our continued safety which we have had to privilege off for so very long. We have a suggested recourse which we, if no one objects, are willing to implement. The geniality of this plan however, I cannot take any credit for, so its best to leave the branch to our dear Vlahir." He unfolded his wings, showing his strong and wide wingspan of black and brown. Thrusting his wings he flew off to a neighboring branch slightly high in the Oak. Vladhir, a smaller and young crow, made his way out on the branch where Eaglewing previously stood.\\

"There was once a man who claimed: incentives triumps ethics every time. We're not Men however; Men are creatures of sin, the only specie capable of doing harm without benefit — the purest form of evil. Animals are simpler: we're not driven by envy and hate; we are incentives embodied.
%Indent
If we'd remove the incentives of thievery, we'd remove thievery itself. The theif steals with the prospect of spending what he steals in the future; if what he steals would be rendered unspendable however, theft would be moot to him.
Our beloved screw-nuts, which undoubtably contains a diverse set of colours and shapes, are still too fungible to trace with any certainty. We can't tell them apart; there's no way to stop a theif from spending his spoils. Fungibility is, I'm certain, an admirable quality — what makes it worthy an intermidiate of produce. Fungiblity and tracability are not necessarily contradictory traits; on the contrary, a tracable mark would but serve as the valid baseline of the fungible unit.
% Indent
If a unique mark would be inscribed, remarked and noted when stolen, the spending of it would accomplish naught save the admission of guilt.
We can't mark the screw-nuts however; we can mark leaves. A replacement is in order"

"I'm not sure I understand", said Zefrafa, one of the rabbits, after a moment of silence, "You want us to replace our screw-nuts with leaves? But leaves are everywhere — you could just pick them up?"

"The leaves themselves will be but a certificate of ownership of the real screw-nut. The valid leaves will have a unique sequence directly corresponding screw-nut — stored elsewhere. The quantity will remain exactly the same: one screw-nut, one leaf." %Temporary

"I don't believe I'd have to remind you all that leaves rot", a new voice echoed from the far end of the glade. Aesop, the forest's last badger, emerged from the crowd to the center of the glade. He carried with him a foul smell; the animals he passed jerked from it, but they did so more of reflex than disgust. 

"No, you do not", Eaglewing responded before Vlahir had a chance to, "Your apprehension saddens me. The silk — otherwise produced by the silkworm to enclose them in a robust cocoon — may be used to add a thin transparent hue around the leaf: protecting it from wear, tear, and as you've so kindly contributed — rot.INSERT TEMP, COULD BE RETURNED"

"All but a gullable disposition would sadden you I'm sure. How could we be sure the amount of leaves will remain the same? Gathering the screw-nuts in one place may be what the theif wants us to do — a honey pot for him to steal. To whom shall the burden to guard this liability fall? I doubt your ability to implement such measures; I doubt even more your reasons of doing so. The screw-nuts appeared out of Nature, ever the guide towards efficency and ever the creator of wealth we've been so priviledged to be born into. Who are we to change that which has given us everything? Who are we to intervene with forces of Nature? And who are you to conspire against Nature, to conspire for our mutual demise?"

"Before I respond to these ridiculus acusations and poor judgement, I want to remind you all that Aesop may have some ulterior motive with these comments of his — maybe his interests align with letting this remain an unsolved issue.
Nevertheless, I shall address these Men of straw.
We shall arrange regular audits as frequent as to give no doubt of the discrepency of screw-nuts and issued leaves.
To your second question, we'd not intended to disclose the plan to guard the screw-nuts today. But, as a gesture of good faith, I will answer it now. A few days ago, a few crows found a litter of stoats — abandoned by their mother — as they flew over the neighbouring meadows. They are but blind kittens as of now; minds still unformed by their natural instincts. We thought they could be raised and trained with a singular purpose in mind: to protect the screw-nuts - with their life if necessary.
And we shall answer your final remark with a question: Whence came that peculiar odor of thine, if not from Nature herself?"

"S— Stoats!?", Zefrafa shrieked, trembling like shackles of a leaf on the wind, "I— I must have mistaken, did– did you say stoats?"

"You crows have gone mad!", Aesop said as he stormed off, "I will have no part in this folly."

"Yes..., Stoats.", Eaglewing said slowly, "But don't you worry Zefrafa; we're long beyond the days of predation — I will personally supervise their training, and make sure that their manners conform to our standard. Anyone else wish to object?"


%The glade became silent, yet the silence wrote the volumes spoken words could never write. The anxious air could be felt; no animal in that glade had been alive in a time of Man, nor experienced predation, 

%"See, the problem stems from the screw-nuts themselves", Vladhir said, he spoke hastily with a twitchy, irregular pitch very unlike that of Eaglewing. If one did not know of his incredible ingenuity, which had come to be expected in the forest, one could get the impression that he was nervous. "The screw-nuts is terribly fungible, there is no way to tell them apart..." He paused, as if he had said something significant.  


%"If we were to mark the and trace the ownership of each screw-nut" He continued, "and if anyone were to be stolen we simply tell everyone and if someone then tries to trade with stolen nut we know of his guilt" As Vladhir paused for the third time, Eaglewing had enough and flew down to the ground and standing in the middle of the glade and continued \\

%"There is no way to mark the screw-nuts themselves, we've tried. But we have experimented with leaves and we're certain we can mark them distinguishably. Its just a matter of replacing the screw-nuts with these new marked leaves."\\

%"And we all should just trust you crows to handle this nuisance for us then?", Aesop said amused. He had moved to the center of the glade. "The screw-nuts have a proven track record. They have certain unique irreplaceable qualities and are already fairly distributed. It's the medium that drives our economy%. I do believe we both can agree that the screw-nuts is the reason for our recent prosperity, no?"

%"Well, it's only temporary, when the crimes are over we'll return to the screw-nuts.", Eaglewing said, "Besides, the leaves will be redeemed one-to-one so distribution and function will remain exactly the same."

%"Where shall the screw-nuts be held? Gathering all the our wealth in one place is a sure road to disaster. To whom shall the burden of guard fall?"

%"It's actually good that you brought that up. A few of the crows and I flew over the neighboring meadows just yesterday. We were curious to discover a litter of stoats, abandon by their mother. They are only blind kittens now, so we'll be able to raise them properly."

%"Wait, you want to do what? Wouldn't the leaves just rot. Don't tell me..." The Stag was cut of mid-sentence by Eaglewind who continued
%"No, of course we aren't that stupid, in our experiments we have had help from some silk worms who adds a thin transparent hue around the leaf making it robust %against both wear and rot. In a few days we will have made enough leaves to replace the screw-nuts. We gather up the screw-nuts in this hollow in the Oak for safe %keeping and get some stoats to guard it. When the crime ends, we simply return the screw-nuts for the leaves."\\

%"Yes, you heard correct and like I said we'll raise them properly.", Eaglewing repeated, "I assure you, no rabbit or any other animal for that matter will be hurt by the stoats we raise"


%The glade was silent, most did not know what to believe and fewer what to do. The rabbits and other smaller prey, born with an innate dread of stoats similar to how human children are afraid of snakes, could not help but express fear in their faces. 

%The question silenced the glade. All animals in the forest had been born long after the time of Man and only knew of predation through tales passed down over generation. Yet many of them still \textit{felt} like prey — an innate fear that cuts deeper than cognition.
%Stoats had preyed on rabbits for so long as to be ingrained in the genetic beings themselves; Zefrafa and the rabbits present in the glade could feel it in their bones.
%  Zefrafa made an attempt to speak, but not a sound left his mouth; as he grapsed for any reasonable objection, the moment passed. And the glade remained silent.

The question silenced the glade, yet the anxious air told what words couldn't. Even though no animal in that glade had been alive in a time of predation, many of them still \textit{felt} like prey; the innate: that which no constitution, nor council, can amend.
No one spoke, not necessarily due to cowardice, but rather to a moment ill-prepared.
  Zefrafa opened his mouth, but spoke in Silence. The language of Nature's poetry; the language with a thousand ways to say things you regret.
The moment passed, Zefrafa had not said a word - yet all had heard. 

"Good." Eaglewing concluded, ignoring the silence, "It's decided."  %"Let's meet here a week from now and exchange the screw-nuts."

Again, a sheperd was of this world. This time not by belief, but by force; a hand was visible once more.

%A sheperd was once again of this world, 


