\chapter{Duty}

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “Until they become conscious they will never rebel, and until after they have rebelled they cannot become conscious.”
        \begin{flushright}- George Orwell \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}


The sun rose slowly above the tree line, the first rays piercing the entrance of Kraerion's hollow in the birch. As had now become habit, the chipmunk sat perched at the threshold, watching the world wake up.
But unlike the weeks prior, where a calm and beautiful winter lanscape had greeted him, only a grey slob of dead undergrowth and leafless trees met Kraerion's gaze. The thaw left the forest naked, in limbo, before the spring would arrive and dress it.

And unlike the previous weeks, he no longer felt the same gratitude for the sun's warmth. He did not longer feel like the richest animal in the forest.

``Is this it?", he thought somberly, ``Is this the life I've been chasing all my life?"

He had been so focused on the pursuit---on the thrill of achieving it---that he never considered, never anticipated, the feelings that had now caught up to him. Guilt. A heavy weight in his chest. It was the feelings of loss, and the gnawing knowledge of his inability to prevent it. He knew, rationally, that he wasn't responsible for Veritas's death. Yet, a whisper in his mind insisted that if he had made different choices---less unortodox choices, less selfish choices---Veritas would still be alive and well.

He shook his head, pushing the thoughts aside. That line of thinking would never lead to anything good.\\

Kraerion sighed, and stood up. He begad to climb down from the birch. Every day since Veritas's death, he had gone back to his family's burrows underground, and today was no exception.
He landed on the ground, his feet sinking into the mud as he walked towards the run. The path usually offered him solitude, but not today; the forest was bustling with animals, all of them in frantic hurry.

As he rounded a bend on path, he had to step off it entirely. A team of beavers were heading in the opposite direction, but instead of carrying logs for a dam, they were hauling large bulding pouches.

"Make way! Make way!", the first beaver shouted, his voice surprisingly cheerful for the early morning.

Kraerion had no choice but to step aside, he leaped onto a tree stump to let them pass.

``Oh sorry there, Kraerion!", the beaver said. Kraerion recognized him as Castor, a friendly but a \textit{simple} creature. ``I didn't see you there!"

``That looks like a heavy load---", Kraerion said, pointing a paw at the pouch. ``Building a new dam?"

``No, no, no! It's not for the dam", Castor replied, a wide grin appearing on his face. ``It's a thick bundle of leaves from the Crows. They're commissioning a massive windmill on the other side of the river. Bought the land from the hedgehogs!"

``A windmill?", Kraerion said, puzzled. ``What is a windmill?"

``I don't know exactly.", Castor answered honestly, ``but I think it's some kind of machine to make bread..."

``But what is bread?", Kraerion asked, even more confused, ``Is it some kind of food?"

``Yes! you know those city birds that live in the wadborough village", a younger beaver Kraerion didn't recognize chimed in, ``Um, the winged rats of the sky I think they're called. They eat it all the time!"

``Winged rats?", Kraerion snapped, ``They're called pigeons. You're aware that Chipmunks are also rodents, aren't you?"

``Ah, relax, Kraerion", Castor said quickly. ``He means no offense---beavers are rodents too, after all! Yes, pigeons eat it---they call it \textit{Breadcrumb Au Rue(Ruelle, Breadcrumb aux Poubelles)}, it's a delicacy, the best food of them all, apparently!"

``I see", Kraerion said after a while, still wrapping his head around the absurdity of it. ``And, they've already paid you?"

``Paid us upfront, yes!", Castor laughed slapping the pouch on his back, ``For the whole summer's labour! It's all part of a bigger incentive to increase demand, or something like that. RAIN they called it, I don't remember what it stands for, though."

``It means", the younger beaver added, ``Rebuild Abundance, Invest in Nature." The young beaver beamed proudly, looking at castor for approval, who nodded slightly in his direction.

``Thanks Flat-tail", Castor remarked as he opened his pouch, ``But never mind some silly name---LOOK AT THIS, Kraerion. I've never seen this much wealth in my life. The missus is already planning to expand our lodge in the dam, it's all very exciting!"

``That's great Castor...", Kraerion said at length, he could sense that there was something terribly wrong with the whole situation---but what exactly, he couldn't put his paw on it. Then it dawned on him. ``But what about the screw-nuts? What about the vote next week?"

The beaver's grin faltered, but only for a second. He leaned in, lowering his voice conspiratorially, ``Well, that's the thing. It's in the deal, Clause four to be exact. If the vote goes in favor of the screw-nuts, the contract is voided. They said their initiative wouldn't work without the leaves. Something about liquidity and public spending, but it all sounds like greek to me."

Kraerion went still, ``Voided? Don't you find that strange, Castor?"

``Well, between you and me", Castor gave Kraerion a not-so-subtle wink, ``we're not the only one who's been paid, and the hedgehogs land purchase has a similar clause too. It's pretty clear how the forest will vote next week."

When Kraerion just stood there dumbfounded, Castor adjusted his pouch, ``Well, time for us to get to work! We have lots of leaves to spend! See you around Kraerion!"\\

Kraerion watched them go, a cold dread settling in his stomach. He wondedered about the integrity of the vote, the future of the forest, but then firmly shook his head.
He reminded himself that this was not his fight---this wasn't in his cards. He had his own life to build.

He hurried the rest of the way underground, slipping into the main burrow known as the Aorta. The Aorta had always been---in Kraerion's fading memory---a place of controlled efficient chaos. But today, it was in a state of utter disarray. Messengers dashing back and forth, stacks of to-be-delivered cargo lined the earthen walls, and chipmunks stood around with a paralizing mix of urgency and confusion.
Kraerion pushed through the commotion, making his way to a side burrow that was Aequitius's personal office. Inside, he found Aequitius, who was sitting on a neat pile of straw, shaped into what best can be described as a makeshift chair. His eyes were bloodshot, his fur was unkempt---he looked like he hadn't slept in a week.

``It doesn't balance.", Aequitius muttered, scratching with a piece of dried root at the massive schematic carved into the dirt walls, clearly not noticing Kraerion's presence. ``What am I missing?"

``Father?", Kraerion said, stepping into the room, ``Is everything alright?"

The older chipmunk jumped, startled. ``Oh, it's just you Kraerion, I didn't see you there..." Aequitius said, his voice trailing off, sounding incredibly fragile. ``Sorry, I'm just... I'm trying to get my bearings again. Veritas took over the scheduling a long time ago. You see this? Is any of this making sense to you?"

``I would love to help, father", Kraerion began hesitantly, ``But, to be honest, do you really think that's a good idea? You know, that's not the path I've chosen for myself"

``Not this scat again, Kraerion", Aequitius roared, his voice rising into his former self, ``Don't you get it, Veritas is dead---Wake up!"

Kraerion stiffened, trying to keep his cool ``I am awake, father. But there are hundreds of capable chipmunks in the your service





(Make way to the Aorta, find Aequitius office)

(Find Aequitius struggle with the everything)

(Kraerion showing competence reluctantly)

(Storm off running out it frustration and finding Cinnamon outside)


