\chapter{Doubt}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“I have never made but one prayer to God, a very short one: Oh Lord, make my enemies ridiculous. And God granted it."
		\begin{flushright}- Voltaire \end{flushright}
	\end{quote}
\end{localsize}
\vspace{1cm}


"One day is today---", Kraerion whispered to himself as his tired eyes slowly widened to an open state. The chimpunk had woke---like all mornings---to a loud unpleasant banging sound, echoing around the run outside the comforts of his small burrow. The sound carried with it the news of a new day, and with it: the message that all who wanted a day's pay ought to drag themselves to the great hall, the Aorta, presently. The frowsty air this deep underground usually made him rise as soon as he woke---to seek a more pleasant ambiance---but today he lingered in thoughts.

"One day is today.", he repeated, to reassure himself and still his doubts, as if repeating the words would make them more true. The power of inertia is strong; Kraerion full well knew of its insidious nature: that tomorrow and never were but equal measurements of eternity. He had longed---even dreamed---for this day to come for as long as he could remember; so he wondered why---now when the day was finally here---he had so suddenly lost his strong convictions.

Chipmunks may be genetically poised for a life underground, but not the chipmunk Kraerion. Even as a little kitten, he had loathed their exists: the damp runs and burrows, the second-hand air, the ever present darkness, and about everything else underground just by association. He hated---as only an adolescent can hate---that which most of his peers called home.
Instead, he wished for a strong wind in his fur, sunlight that uncovered all the beauty that is Nature, but most of all the chaotic buzzing of life above, that so contrasts the routines down below. He yearned to run the branches of trees, not the ever branching network of runs dug in the forest soil. His father had many a time japed that his son was born more a squirrel than chipmunk---and he had not been wrong. When he was younger, he had stated that one day he was going to live amongst the trees, but received feedback which would otherwise only be appropriate after a well executed joke.

Kraerion eventually mustered the will to rise from his moss coated bed. He went over to a corner of his burrow and began scratching away at the dirt.

"Good, still here.", he confirmed anxiously, as the felt the steel of seven steel screw-nuts---which would surely appear beautiful in the sunlight---laying before him. He covered them up again and left his burrow into the run, and followed its twists and turns until it widened into a great hall: the Aorta. It was dug under a great willow; its massive network of roots---intertwined with the walls and ceiling---supported the weight of the dirt and kept it from caving in.\\

Since the time of Man, the forest had steadily increased its economic output. One of the  contributing factors was the increased specialization of its inhabitants. Whilst many a specie have some certain advantage in the gathering of some specific type of feed, none is as great a carrier than that of the chipmunk. In their elastic cheeks, they are able to carry loads of feed---and other goods for that matter---efficiently around the forest; their small size and great numbers gave the operation a granularity to it, which made it difficult for larger and stronger animals like the roebuck to compete. When other animals began to hire them for their service, they began to expand their network of tunnels and runs to cover whole forest---connecting all its major hubs. Therefor---every morning---the chipmunks gathered in the Aorta to share news and plan the day ahead.

Most chipmunks were already present when Kraerion entered. 

"One day is today.", he thought again, as he headed towards his usual spot in the front. But he hesitated suddenly and reconsidered; instead, he decided to begin his new life with breaking this habit and found a place in the back.\\

The murmur of conversation disappeared in an instance when an old chipmunk appeared in the Aorta. His name was Aequitus and was the chief chipmunk, gray spots of fur spoke of his age, yet his features were easy on the eye and he bore his age proudly. Everyone knew the chief and saw him as something akin to a revered hero. When he was but a kitten, he'd taken interest in the chipmunks' livelihood and noticed irregularities in their billings; after some further deliberation with his friend Br'er Rabbit, he realized that they could likely double their prices with little to no churn. He put forth the motion to the then chief chipmunk, who surprisingly listened to the youngster and approved it. When their income subsequently increased, he was very vocal about its occurrence, and made it impossible for the chief chipmunk not to pass it forward to the chipmunks' daily wage.

When Aequitus a few years later became unanimously chosen as the next chief, he took it a step further. He transformed the chipmunks' enterprise to a sort of cooperative, with bylaws dictating that a fixed percentage of the total revenue would be earmarked for workers' wages. As well as other rules limiting the influence of his own office---not only for himself but setting the precedence for his eventual replacements. 

Together with Br'er Rabbit---who had by then become the implicit leader of the rabbits---and with the help of the by  then Glade of Representatives Twig Ongenþeow, he started the Winter Fund. A collective fund that functions similar to that of human insurance: its members contributes feed during the spring, summer, and autumn as a premium; members that find themselves short during the winter may then make a claim and receive feed to sustain them until winter's end. % Dearth

A cynic human might proclaim the flaw in this scheme, that an animal might take advantage of it by wasting his wage and making a claim every winter---but he forgets two things: most animals can't count; and although possible, making a claim is very stigmatized, and that most animals would rather starve than to broadcast their destitution. Aequitus also---being a co-founder of the fund---made sure that all the work related to the logistics---moving and storing of the feed deep underground, where the soil is grainy, cold, and preserves the feed from pest and rot, and hidden from prying thieves---went to the chipmunks---further boosting the demand for their services.

The fund was a great success; winter deaths decreased drastically the first year, and then slowly year after year. The chipmunks got a more steady stream of sophisticated work from the fund and thus means for a better life. For all the contributions Aequitus made, none could match the feeling he instilled in every chipmunk: the intangible sense of worth; the standing the brought them to in the forest; and the care he fostered between chipmunks by treating them all as equals.\\

When Aequitus reached the front of the Aorta, he turned and faced the scurry.

"Before we go through today's agenda, I have news---both good and bad.", he began, "And, as you may not be able to appreciate the good in anticipation of bad, I'll begin with the bad.", he took a tactful pause, as anyone with his level of experience would in this situation.

"The eastbound run collapsed late last evening; we're completely cut off from the eastern part of the forest. Therefor, the deliveries to the rabbits' hill must be postponed."

"Why did it collapse?", Aequitus younger brother Pietus asked, who stood at his regular place just right of his brother.

"Well---", Aequitus dragged, "a pheasant went chasing a maggot again and crossed above the shallow no-zone."

"Again!?", Pietus cried, not hiding his contempt, "Did the pheasants not promise to be more careful---that last time would be the last? Will they honour our agreement and pay for the damages?"

"They did indeed. As you all know, the pheasants are not the most organized of animals and will only blame each other if we make a claim for damages. We may bring it to the Glade, but what---other than appearing petty---would we gain? Little and less, I'm afraid. Nevertheless, I want you, Pietus, to go to the moles and have them dig a deeper eastbound run this time---that is, at least, a factor we can affect."
"I'll do it.", Pietus responded, "But send someone else to the moles next time---they don't even speak our language..." %the common tongue.

"Nā, hēo seċġaþ þone ealda sprǣċe. It is we that don't speak theirs.", Aequitus paused, waiting to see if Pietus had a response. When his brother only mumbled something inaudible, he continued.

"I'll make sure Br'er and the rabbits get the news of this postponement personally. As for the good news, the rumors going around are true: the Glade have decided to institute a 2\% tax on all Forest shipments. It's only a temporary experiment with us as the pilot service."

"How is this good news?", Veritas squeaked, a tiny runt of a chipmunk who were also standing in the front close to Aequitus.

"Two reasons: firstly, the funds are marked as aid for destitute animals who can't afford the Winter Fund, and we'll surely get the contract for its operation; secondly, we don't pay for our own services---we're essentially exempt!"

"No! That's not how it works.", Veritas snapped angrily, "this will force an increase in our prices---hurt our margins; to only burden one industry, and ours at that---it's... it's incredibly unfair."

"Enough.", Aequitus grumbled, "That's enough, this is neither the place nor time, we may discuss this later in private."

Veritas did not answer, but she turned her head sideways---showing everyone her disdain.

The old chipmunk moved on to the day's normal agenda, dishing out more routinely orders before dismissing his workforce. However, his eyes were fixed on Kraerion---the dismissal did not apply to him. When the last chipmunk had left the Aorta, he began to speak.

"Kraerion---", he said.

"Father.", Kraerion responded, equally enthusiastic.

"It's true then, hiding in the back like that; you're actually leaving what we worked so hard to create?"

"What you created you mean? You cannot pretend this is news---I've been more than forthcoming with my intention to lead a different life. You of all chipmunks should know of my extra shifts to afford this move, and my refusal of the managerial responsibilities you so blatantly pushed on me."

"We all have dreams, Kraerion. I know you might \textit{feel} like a squirrel, but you're not one---I promise you that you'll end up miserable, dearth of resources, and completely alone in a world of wings if you try to live as one.
Dreams are a lesson in growing up: learning how to smother them in favour of what's truly important in this life. And, you'll get other dreams---realistic dreams---like forming a family, building a future for our specie, and contributing to the betterment of the Forest at large."

"I'm sorry---", Kraerion said at length, "but that's not me, and quite frankly, that'll never be me."

"Don't you feel any sense of responsibility? What about your sister Veritas? You expect Pietus and I to go on forever?"

"What about her? She's smarter than us three combined; she could take over tomorrow if you'd only let her."

"You know full well that intelligence isn't everything. You saw how she acted today: she lacks the social conduct to lead other chipmunks."

"Maybe you should have spoken with her before announcing your decision to the whole Aorta?"

"It's not only today and you know it. Never mind. If not for us, then what of you and Cinnamon?"

"Don't", Kraerion said flustered.

"What, you haven't told her!?", Aequitus said truly surprised; he was just about scold his son, but hesitated when he saw Kraerion's face and realized it would be superfluous. Before he had time to say anything more, Kraerion turned around and ran.

Kraerion ran, and he ran, and he kept on running until the pain in his lungs, and muscles, numbed the thoughts that so rudely had occupied his mind.
