\chapter{Discrepency}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		%“In man's struggle against the world, bet on the world.”
    %\begin{flushright}- Franz Kafka \end{flushright}
	“Concentrated power is not rendered harmless by the good intentions of those who create it.” 
		\begin{flushright}- Milton Friedman \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}



%The song birds had long gone south for the winter; the winter air calm and quiet, save for the irregular cooing of a pidgeon.

%The winter came early and hard. Most of the song birds had long migrated south, but the pidgeons made up for it with their incessant cooing. The forest bed was covered in about five inches of snow and most animals were in their burrows and nests trying to preserve their body heat. Kraerion had insulated his hollow, the inner walls meticulously covered with moss and lichen. Redrill had carved a rounded wooden piece, which could be rolled in front of the entrance to keep the warmth from escaping.

The winter came early and hard; the song birds had long fled south: the winter air calm and quiet, save for the irregular cooing of the pidgeons. The forest bed covered in a thick layer of snow, unevenly distributed by wind and tree. The animals hid in their burrows and nests for most of the days, keeping close and preserving body heat. Winter but a game of waiting—a quarter of life on pause.

Kraerion too, wasn't immune to cold and had prepared for winter: covering the inner walls of his hollow with moss and lichen. He'd Redrill carve a round wooden piece, which could be rolled in front of the entrance to keep the shy warmth hostage.

In the mornings though, he pushed the piece aside; he preffered cold to a life on pause. He had watched as the days grew shorter, the morning dew slowy turn to frost - a fenomena that is difficult to understand living underground. And today, this particular morning, on the surface of the unadultered fallen snow, haor frost stretched far and beyond Kraerion's sight. The chipmunk listened to the winter silence whilst his eyes followed the sun's rays' glimmering dance on the suface hoar.

As he sat there, his mind wandered to the events in the glade: the attempted seizure of Aesop, the death of the stoat, and the issued decree. The outlawed badger had never officially been attained, and no one knew where he was. Nevertheless, many a rumour spread like wildfire through the forest: 'He'd been caugth, killed, and buried by the stoats.', 'No, he hid in some old forgotten badger's lair deep underground - biding his time', 'No, he sought supporters to his cause, roaming the marshes to the east of the Forest.', and many more.

Kraerion did not know what to think of it himself. Aesop was a solitary animal who bore his smell like armor; yet when he'd spoken, his words had always seemed sensible and moral to Kraerion. It was difficult to imagine him a theif.

%Kraerion did not know what to think himself; he'd always liked Aesop, despite his smell, and thought him sensible on most 

%Kraerion did not pause; instead, he'd prepared to stay in his tree through winter. He'd  

%In the mornings though, he pushed the piece aside. He preferred the view of the glade over warmth. He had watched the morning dew slowly been turned to frost. The years before he had been underground and not fully realized that they were but two sides of the same metal, denominated by temperature. His mind wandered back to the events in the glade. The seizure of Aesop, the death of the brave stoat and the forbidding of screw-nuts. No one had seen Aesop since he fled, yet everyone seemed to carry their own rumor where he was or what he was doing. The hedgehog Spinestack had sworn he'd seen the stoats catch him, and that he most likely was already buried as to away trial. The pigeon Greyhead conjectured that Aesop had escaped the forest and sought rebels in the surrounding meadows and marshes. No one knew for certain, yet it didn't keep anyone from talking about it. Kraerion didn't know what to make of it. Aesop was peculiar, no one denied that, but a theif? No, he could not believe it.

%He's thoughs were abruptly disturbed by Cinnamon who suddenly appeared in the glade, as she had done that late summer morning. This time she didn't stop at the foot of the birch; instead, she raced up trunk with a haste not to her character. When she reached the hollow she was completely out of breath, grasping for air - Kraerion did not need to hear her speak, he saw in her pearl black eyes that she bore grave news. She knew there was no point in delaying the inevitable, so when she caught breath she uttered solemnly 

His morning thoughts were interrupted by a running Cinnamon who suddenly entered his field of view, as she'd done that late summer morning. This time shes didn't stop at the foot of the birch; instead, she ran up the trunk with a haste not to her character. Before she had a chance to speak, Kraerion saw the gravity in her black pearl eyes. Suspense grew, as she caught her breath.

"Veritas is dead", she said with a shiver, "You better come."
%"Veritas is dead", with a slight shiver in her voice. Her face carried grief, but turned empathic in an instance once she saw Kraerions reaction, "I think you better come."

%They ran side by side back to the tunnels and into Shrubs burrow. They ran in a, to them, new sort of silence. A heavy silence. A Silence which could not bear the weight of words. Nothing carry intent as silence does, the implicit understanding of words not uttered. 

They ran back togehter, side by side. The beautiful morning silence quickly turned to a silence of despair. They were out of breath by the time they entered Veritas spartan burrow. "Too many chipmunks", Kraerion thought as he saw the crowd around her lifeless body, "too little space and too many damned chipmunks". He pushed himself past the crowd and found his grieving father leaning over her - his forepaw gently resting on her chest. Pietas was also there, he looked up as they approached and gave them a silent nod; Aequitas didn't notice them.

"Get out!", Kraerion screamed suddenly, surpising himself most of all, "Get out, all of you!"

But no one moved a lim; "did I not say that out loud?", kraerion had time to wonder before Aequitas bellowed:

"Do as he says: get out! Now!"

And so they did — a revelation to none that Aequtias voice carried more clout than the son which was lost—they left one after the another til only Aequtias, Pietas, Kraerion, and Cinnamon remained in Veritas presence. The living chipmunks remained quiet, honoring—as was the norm amongst animals as with Man—the chipmunk which was not, with their silence. The silence death requires.

%They entered the Veritas's spartan burrow and joined the small crowd of chipmunks surrounding her body. Aequitas was leaning over her with his forepaw pushing lightly on his chest, not hiding his grief. Next to his father stood his uncle, Pietas, who bore a refrained expression over his face. Around them stood a mixture of kin and friends. Veritas had been a difficult fellow to enfriend, but no one denined his ability to keep accounts and his integral part in their shared vocation. When Kraerion saw his brothers, his mind ignited, filling him with memories. Their  quarrels, their laughter and the childhood they had shared. Memories that now had grown heavy with grief.

%Kraerion and Cinnamon pushed their way forward through the crowd to join Aequitas and Pietas next to the corpse. Aequitas, still with his paw on the chest, turned to face the two arrivals. His face was full of grief. 

%"What.., what happened?", Kraerion managed to say, breaking the long silence.
%"I.., He..", Aequitas began, but his voice gave way. He took a deep breath, "I.. I think he starved himself to death.. He had a strong conviction that we'd not collected enough food to survive the winter. That we ought to ration. I.. I know he was eating less.., but to so far as to..", He struggled to finish the sentence, as if stating the fact would remove all hope that this was just a bad dream. Instead he said, "He's not wrong you know.., the food supply is running short. Veritas is not the only one who'll starve to death before this winter is over."

"What... what happened!?", Kraerion asked, once the silence had been paid.

"I.., she. I don't", Aequitas managed, his once proud face now but a beacon of guilt. He stooped and continued with his face hidden, "I... I think she starved himself to death."

"What do you mean starved? How do you starve when there's no lack of feed?"

"Well, there's a lack of sorts. Of course we're not literally out of feed right know, the winter is still young after all, but we've already seen an abnormal amount of Winter Fund claims; at this rate we'll run dry long before winter's end. Veritas has, in her own prophetical way, been warning us since summer - saying we'd need to begin to ration. And a few weeks ago she began rationing herself to lead by example. When we didn't listen, I guess...", he paused, emitting an anxious sigh, "I guess she pushed it too far."

Kraerion was stupefied, staring at everything, and nothing in particular. When he didn't respond, Cinnamon did:

"But, what about the things you said in the Glade - was that all lies?"

"No, what was said was, and still is, true. The Winter Fund received more feed this year than ever before. And, it's not like we dismissed Veritas concerns either - it got the full and proper due diligence from not only me but Eaglewing and the crows too.%; and whilst what she said was true, we didn't believe it was significant enought to have a real impact on our economy and this winters survival rate."

%Eaglewing asked that Vertias shouldn't be present

"What did she say?", Cinnamon continued, "What was here concerns?"

"I think you know them, 'Feed is dialectic; hunger is constant', 'a delta must reverse', and so on. She's never been one to articulate her thoughts, but I give it a go. As you know, there are many _ Unions in the forest that works in part as protection of wealth, and in part as a source of liquidity for projects which benefits all. We chipmunks have one where we store screw-nuts safely deep underground, and use part of it to fund large operations, such as new tunnels, where the benefits will only outweigh the cost on a large time scale. So, when screw-nuts were changed for leaves, all our members withdrew their funds temporarily, and for a few weeks we lost our ability to invest. For example, the eastbound tunnels, which been in the talks for years, was scheduled to begin digging this summer, but got postponed to next year due to this lack of funds.
   But this is only the initial cause, less projects means less salaries, and in turn leaves less animals with the means to buy feed. And, well, so it goes on and on.

"That's why the prices fell...", Cinnamon said, suddenly understanding.

"That's correct, feed prices fell not because an increase in supply, but because the reduction in demand. And eventually the supply will course correct, leaving us with a winter dearth of feed."

%"But why did you dismiss it?", Cinnamon asked, "It sounds very plausible to me..."

"But this sounds more than plausible, how could you dismiss them?"

"As I said: we didn't. On the contrary, we took great pains to understand and counter them. And no one denied the truthness of her claims, but it's difficult to gage how large the actual impact on our economy. Similar demand shocks happens all the time, but usually something else just fills its place - and its effects, in the grand scheme of things, are seldom noticed. Alas, not this time around..."

"Well, if that was the case", she said without refrain to show her irritation, "how come you didn't care to mention the possibility in the Glade?"

"Mention it?", Aequitas scoffed, "What do you think we Animals really are? We beautiful all-loving cooperative beings of Animalkind! Surely none could be so impolite to get upset when they learn their kin might starve to death! I'm afraid our newfound civility is but a veil; we're nasty and brutish beasts of violence in the true state of Nature.
  And that said, there's a less gruesome reason as to why we chose to stay silent: fear. If we were to warn of what we know, we'd only 
spread fear - and when we fear we look invard, we save and scimp and care only for the bare essentials. Thus dropping demand further, making matter worse. We must avoid fear at all cost. Eaglewing even suggested that Veritas ought to be absent that pre-winter meeting, and I agreed with him, there was no telling of what she might have said."

%as with many things that stagnates demand
%we didnt, difficult to gage the impact - we believed to little to even notice

"At least we have a right to know. And late is better than never, we must tell the Forest of what we know!"

"It's no use!", Aeqiutas cried, "It's no use! Do you fancy bloody hands, fine, go ahead tell them. Tell them all. I may have Veritas death on my hands, but I will not be here to see our Forest regress to a state of Violence."


"That's enough!", Pietas finally snarled, "This is not the place, nor time.", And the painful silence, which death requires, filled the burrow again.


%our newfound civility is but a veil; we're still nasty and brutish in a state of Nature.

%our newfound civility is a veil; we're nasty and brutish beasts of violence in a state of Nature.

A nobel laureate once said: "a society that puts equality before freedom will get neither", but a chipmunk that puts his people before truth, one might wonder, what will he get?

%"What!?", Kraerion said, "What do you mean? Didn't you tell the whole forest that our cellars are filled to the brim?"

%"Gnath", Aequitas scoffed, "Eaglewing came to us the day before and told us not to tell about the deficit. 'Panic would ensue', he claimed and I.. I believed him. But Veritas didn't, he simply would not have it. Eaglewind and myself agreed that it was for the best to leave Vertias out of the meeting. I.. I was naive, I thought we ougth to have had enough time to quietly fix the problem before chaos ever surfaced. But it doesn't seem like it anymore..."

%Kraerion was stupefied and when he didn't respond, Cinnamon took the tone. "But how? How could this be kept a secret?", she asked, "Don't we all keep track of how much food we've stored?"

%"You would think that was the case", Aequitas snarled, "But most animals doesn't run in our tunnels, nor visit the our cellars. They simply put away bits and pieces throughout the year and hope it will be enough. And this year it's simply not enough."

%Cinnamon paused for a moment before responing. "If what you're saying is true", she said, "We must inform everyone."

%"It's no use", Aequitas cried verily with a deep and troubled voice, "The forest is cover in a thick layer of snow. It's no use."

%The cry ended the conversation. The four chipmunks and their fallen friend remaind silent for a very long while, each grapsing the dire consequences and fighting their imidiate grief. The days passed but Aequitas never left Veritas bedside. Any will to work or deal with the chipmunks daily business were gone with Veritas. Next to him remained, broken by grief, until eventually he fell dead himself. 

%A great man once claimed that a society that put equality before freedom will get neither. If truth is a prerequisite to freedom, what would that imply for equality? What happens to agency when the Great Truths aren't allowed to propagate? Equality is ever so important, yet it's not a factor - it's a product. It's not the reason, it's the result. The end result of a well governed 

%Like a great eastern power has tauth ous with their devotion to Orwell. Take away the thruth and you take away options, without option we behave predictable to a tee, droning on the only way we know how. Truth is a pre-requesit to freedom and freedom is a pre-requesit to equality, 

%A 'free' choice is not free when choices are censored and can't explored. A limited agency, where all the given options are controlled and managed. Although no explicit law or rule forbids your freedom of choice, the implicit imprisonment of truths denied. 