\chapter{Delight}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“If a man does not keep pace with his companions, perhaps it is because he hears a different drummer. Let him step to the music he hears, however measured or far away.”
		\begin{flushright}- Henry David Thoreau \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

%His life as a savage, what he lost in produce, he gained in quality of life

%Food is dialectic; hunger is constant.

%working this way took him more of the day, but there was a certain disutility, which is seldom accounted for, that made it whole.

%Supply and demand at odds — hidden in aggregatef A delta must reverse

The sun slowly rose in the eastern sky; innocent rays of morning light trickled through the dense forest canopy. The sparse beams reaching for the undergrowth, fighting off the morning mist like a potent antidote. The daily struggle between dew and vapor had began anew. Kraerion sat awake in his hollow, hunched on his forepaws, gazing contently out through the morning air. He had woke, like most mornings, to the varied orchestra of nightingales and blackbirds tirelessly competing for the vibration of the humid air. The beautiful song was now and again disrupted by the distinct cooing of the neighboring wood pigeons. 
  
He'd managed well — gathering his own feed, suplimented by the odd job when such oppertunities arose — but, of course, he was less efficient then with this former vocation. Yet, the savage life called to him; the absence of the natural irregularities of life — which, a steady piece of produce, from an even steadier wage, had smoothen numb — was to him in itself: disutitlity. And, waking before the sun instead of with it — there's disutility there too.

  Before he left his damp burrow, he'd saved enough to procure feed, to last the transition to independence and cover the many uncertainties this new life surely would entail. But, that summer, something of magic happened: prices began to fall. They fell little by little at first, then all at once. By the end of July, the prices where but half of what they had been at the end of spring, making Kraerions savings not only ample for an uncertain transition, but ample for the first winter as well.

No cause could be attributed to the sudden drop in price, but thought or concern did not burdened the Wadborough animals' minds. Instead, they feasted — as if that summer of abundance would never end. 

The exchange to leaves had happended as Eaglewing dictated one week later; the animals poured into the glade from all sides. They'd attempted to form a line before the crows. Although the animals had increased in affluence, lines are still as innate to them as a sheep stalking a pack of wolves, or a chicken snagging a fox for dinner, so it was short of a miracle that no major incident occured. Kraerion — ever so prudent — had waited until the end to avoid most of the expected tumult before exchanging his last screw-nuts for a thick stack of leaves. 

%The swap over to leaves had happened as planned one week after the meeting. The whole forest had gathered in a long line, and all things considered, it had gone well with only a couple scraps. Pray animals are usually very risk averse and tend to be quite unpredictable in numbers. Supram had waited in a nearby tree to avoid the tumult and only entered the line when most animals had left. He kept his stack of fresh leaves in the back of his hollow. The theft had stopped immediately after the switch had taken place and the crows had received nothing but praise for their ingenuity.\\

A sound of scratched bark broke his thoughts; he leaned his head out as to see down the trunk and saw a familiar shape standing at the foot of the birch. 

"I am not climbing this \textit{thing}", Cinnamon cried mockingly. He moved — in response — down the trunk and stopped a rough meter from the ground in the manner of a nuthatch.\\

"You never said goodbye.", she said when Kraerion failed to speak.

%"I didn't know what to say", he replied. She was not entirely pleased with his answer, but stayed silent.\\
"What could I have said?", he answered, knowing it was a poor excuse, "Besides, I couldn't, it was hard enought as it was."

"Well, if it was too hard — may it be the wrong decision?"

"No", he said harsly as by instinct, seeing her reaction he realized his mistake he quickly said, "should we walk somewhere?"

"Somewhere?"

"Anywhere."

"I though you were the one to distinct between walk and wander. But sure, east?"
She'd turn and begun walking before he had a chance to reply. 

%The months appart dissappeared in an instance and he remembered how well she knew him. He knew she'd always listened, but he was afraid she could never hear

Kraerion had long made an effort to distinguish between walking and wandering. "Walking is active and with purpose — you \textit{walk} with the purpose to get somewhere.", he'd preach, "But wandering \textit{is} the purpose, done for its own sake — an end in itself." To Kraerion they were more than just definitions, they symbolised the two outlooks of life: the former the ambitious numbness of habit; the latter, the very beauty of life itself. He also reasoned that it wasn't just a difference in disposition, but that the former would eventually meet the Thoreauvian fear: to wake up one day and discover that they had not lived. The chipmunks — and thus also Cinnamon — had built their existence around efficient transportation, so whilst she'd always listen, he feared she could never hear.

After walking a short while, Cinnamon broke the silence.

"I'm worried about your sister", she began tentatively, "she's changed." 

"Veritas?", Kraerion said surprised, "how do you mean, changed?"

"I... — I don't know. Well, maybe not changed per se. She's herself, only more so."

%"Zealous, Intense, Rightous?", Kraerion paused, "Like she must right every wrong in this forest"

%"Zealous and rightous?, there's always something the Forest \textit{ought} to do. But she's honest, clever and have never been wrong — she quite deserves to sit the high horse. Sure, she gets stuck in the prison of her mind sometimes, but don't we all?"

"Honest, can you get too much of that?", Kraerion chuckled, "I see what you mean, she gets caught in her mind, not letting thougths go — letting them take loop around in her head. Yet her mind is the sharpest in the forest—even sharper than the crows'. You needn't worry."

"She gets caught in her mind.", she repeated, "That's it. Sure, her mind is sharp — it's sharp but undusted. Whilst a dull mind can do no harm, a sharp one cuts; the dull is cleaned, the sharp begets dust. Her mind is in a fog of dust, and you're the broom Kraerion! You were always the pragmatic balance to her ingenuity, but you aren't there anymore... And her undusted mind grows dustier still."

%"But, that's usually the story of sharp minds, they are undusted as dusting them makes cuts. A dull mind can do no harm, "

"Nonsense, you talk as if she's crazy!"

"Maybe she is, or she's beginning to be percieved as if she is. But, there is more, she's talking of our economy as if there's some great danger to it. She's not terribly coherent in the best of times, she's reduced to repeating... — repeating these phrases."
%"Yea, she gets these ideas and then she broods and nags; too diligent for this world. What is it this time?"

"What do you mean phrases? Which phrases?"

"There's a lof of them, but there's a couple in particular that she keeps coming back to which I remember: 'Feed is dialectic; hunger is constant' and this other one, 'A delta must reverse'", she paused, "Do they tell you anything?"

"Well...", he though for a while, "The first one is clearly about winter, feed is cyclical: from the first rare morels that nigh beat thaw, to the late autumn tubers — accessed til the ground freezes hard. And, hunger is..., well — hunger: constant, and independent of season. 
But why'd she care? The winter fund was invented to fill this discrepency in seasons, and she \textit{practically} runs the fund. She runs it in all but name.", he took another pause, "'A delta must reverse' — I don't know this one, which delta is it? and why must it reverse?"

Their conversation did not end, but transposed to one in Silence. With words omitted, silence leaves room for other ways to communicate; and the tension that grew between them, larger for every second, was one of them. Cinnamon hadn't shown up out of a sense of duty — to tell of Veritas well-being; both new it, yet they pressed on, pushing the issue ever further into the future.

"You are never coming back, are you?", she said and she stopped abruptly; her chipmunk eyes – glimmering like black pearls caught in sunshine — glaring through him. \\

"No.", he said staunchly after some thought, "I don't think I ever will."\\

"But why? Why would you leave? I'm not asking for Veritas, nor Aequitas, I'm asking for me, Kraerion. For me. What about us? What about the life we were creating?"

"You know why.", Kraerion answered sadly, "You know how miserable I was, living in darkness with that damnable soil all around. No matter how much I'd want to, I can never be in consonance with a life underground."

Once again, they regressed to Silence. Tension might have eased, yet the silence layed but as heavy. Exhausted by it, they wandered along.

They wandered past the rabbits' great hill, thence past the clearings which constitute the central part of the forest. Many an animal laid leasurly basking in the morning sun and they watched curiously as the two chipmunks quietly wandered past. "That's queer." Kraerion thought, "aren't they suppose to be working at this hour?", but he soon dismissed the though when he remembered that price drops and the lower cost of living it surely must have brougth. % Last sentence doesnt fit with narrative.

When they reached the Glade of Representatives, the silence had grown them weary. Kraerion could scarcely recognize the glade without it being filled by the forest's animals. The glade however, wasn't empty; on the contrary, woodpeckers were swarming the Old Oak - pecking away at its trunk, sturdy roebucks were hauling loads of dirt away from the glade, and crows were all around them talking - amongst themselves and with other animals - making plans. 

They'd nigh entered the glade before a voice called out for them.

"Good morning!", the voice, which belonged to the crow Vlahir, said as he waved to them to come over. He was standing next to a straight stick running perpendicular to the ground; stones had been laid around the stick to form a semi-circle. 

"Morning", Cinnamon responded as the approached, "What is this?", she continued pointing to the stick and stones.

Vlahir only smirked for a while, then he spoke.

	A sun's eternally bound,
	Companionless, but she must around;
	Her solitude that of natural law,%Her loneliness that of natural law —
	Yet she smiles; and thy heart thaw.

	And trees the east salute,
	To whom that bears them fruit.
	Although raised in different glades,
	They cast but similar shades.

	What an angle may disclose,
	To thee, and he who knows; % SPELLING ERR To thee, and he who knows, and those who knows
	With stick and stones to be precise,
	Of where a shadow bound to slice.

	A sun's eternally bound,
	To us distant yet profound —
	To tell the pace of the Sublime,
	And thus thou know about the Time.



When he stopped, as by a bespoke requset to God, the sun appeared behind the lone cloud in the sky. Its rays of sunlight gave birth to shadows; the tip of the stick's newborn shadow laid right on top of the second westernmost stone.\\

"Wait, do you mean that this thing — this... \textit{contraption} — tell us the time? ", Cinnamon said astonished.\\

"Yes!", the clever crow hooted with delight, "And here I thought \textit{Rodents} were void of wit! Whilst the sun travels from east to west, the shadow traverses the stones from west to east. The stones enumerate the Time of day"

"And, this shadow, is it precise? Is it the same stone at the same time every morning?", She asked, ignoring the slight. %Too excited to care about the slight.

"Not only is it precise, it's also independent of location. No matter where in the Forest, the angles are always the same. Now it is but a mattter to raise them in all parts of the Forest, which I presume you chipmunks — with your vocation — see the value in."

"This is truly transformative, naught will be the same!" 

"No, it will not.", he said, yet with no hint of humility, his smirk appeared again as he considered if he ought to say what he wanted to say.

"But I will tell you what is: sentiment. There're so many of these silly belives that by themselves become the agents of its own truth. For us, as individuals, spending less than you earn is the only viable strategy for financial success; hence it's thus assumed that prudence and frugality must surely transpose into viable strategies for the Forest's finances as a collective. Whilst nought could be further from the truth, what is true in the singular might be in complete opposite in the aggregate! Consider for example, if each animal saved but 5\% more, then on average each business would also receive 5\% less. Low margin businesses would immedietly be trouble, but even if we assumed all businesses would survive, they'd all earn less, and have less to pay out to employees and owners, which in turn would decrease spend even furthur. Good individual decisions, could thus cause a vicious negative spiral of ever less spending: a maelstrom to demise our economy. 
  
Savings bear no meaning in the aggregate, if you really think about it. If someone reduces his savings by way of consumption, it will become  but the savings of someone else. Thus aggregate savings must always be equal the total supply of money. And frugality but the means to reduce economic velocity - making everyone poorer in the process.

What if I told you that spending could be controlled? We could create an economic boom that would never end; the bull could embark on its last and final run - the run that would last an eternity."

When Cinnamon responded, Kraerion had long since stopped listening. "The need to know the Time \texit{is} the problem.", he muttered, "No one plans to smell the hillside flowers, nor watch the glimmer of the morning dew; when the day's activities are shackled to Time, the wonders of the world does not cease, but become imperceptible - and a world without wonder is not of life worthy. The solution - the true solution indeed - would be no solution at all."

Instead, he admired the woodpeckers hard at work. And then he saw, there were too many woodpeckers for only one tree; and they were hauling out dirt, but there was no sign of digging — Whence did the dirt come? 

%"So we could have duplicate structures all over the forest! It would be easier to coordinate, it would even be possible among strangers.", Cinnamon said to show she understood. 

%"Coordination is important, as I'm sure you chipmunks understand", Vlahir said, hinting at their vocation, 

%"But time heeds another purpose. When you and I go earn and spend our screw-nuts, we do so in a limited scope, it is to us no truble to balance the two. But all our actions viewed in aggregate becomes impalpable, and with time we may quantify actions in its aggregate. Velocity. With this device we may finally grasp the true velocity of our forest, and what you find is truly remarkable 
%The rules by which the collective is governed is not the same as for us as individuals. 

 %Velocity. Labor is only a function of time, and velocity its quantifier. "

%"But not what we crows are interested in. The fruits of labor are really a function of time, if we cannot measure time - we cannot know where to spend it. Sure, you may counter, for each and every one of us, there is no difficulty in allocating or spending, we know what we can and cannot afford. But there lies the mistake, our forest does not consist of mere individuals, and if you consider the economy in it's aggregate you'll surely see the misconseption. Since the recipient is also an animal in the forest, he thus have more to spend and you more to earn. So if we account precisely, letting everyone spend mre, all would also recieve more. The money supply remains the same, but the velocity increase. To conclude, only by raising the aggregate willingness to spend, one would also raise the aggregate standard of living. Now when we've found how to measure velocity, we only need to find how to increase spending. " \\ 

%Vlahir pointed his wing at the rocks, "The time for the shadow to travel between the first and second takes as long time to travel from the second to the third. We may say that harvesting a stones worth of blueberries takes two rocks and three pebbles worth of time, but during two rocks and three pebbles you could harvest as much as two stones of cranberries. When you see labor as a cost function of time, only then will you know what to prefer." % Note, there is a difference of spending in aggregate


When great ideas are discovered, those seemingly obvious in hindsight, they appear imperishable. Propagating from mind to mind, like a virus, only by the percieved virute of the idea itself until it's safely kept in the collective mind. Yet they're anything but imperishable, they slowly twist and turn; they transform until none of its original beauty remains. --- morph

  We humans have learned to think of time in base 60, because long ago when the Babylonians discovered how to measure time they had inherited a sexagesimal numberic system from ancient Sumer. Much of the meaning — the substance — of their system of mathematics have long been forgotten, or fallen out of relvancy, yet here today the arbitrary number 60, written in decimal form, remains inert. Now is but the cumulative residue of legacy; the fabric of time woven with fragments of lost meaning.

Or is it arbitrary, maybe the Babylonians discovered to measure time \textit{because} of their numberic system— that the trajectory of the past had gather enough information to enable the next progressive step of human understanding? Would Newtonian physics been discovered if 18th century England were cursed by Roman numerals?

%The ideas of the past has a momentum of its own, with a high degree of inertia; it's not we who alter the course of history, but the past that alters us to fit its agenda.

The survival of ideas might be akin to Darwin's Natural Selection: knowledge, that is useful to its carrier, is remembered and passed on; information, that is easily shared, like the infectious joke or the compelling fireside story, survives the erosion of time; and (the base sixty here remnant with function lost is) like our  useless appendix still here inerth, some informational relics of the past has no usage but for the telling of time. Like any stochastic process, it appears, insofar as we are capable to discern, as noise; yet over large enough time frames, the signal becomes undeniable.

Wherever the truth may lie, when Vlahir saw a shadow and realized what it meant — did he consider the futute crows whom would grow up burdened by his conjecture, that the arbitrary number of stones he had chosen for his sundial would be the last piece to remain of his legacy? 
Did he realize the implications of the economic system he'd set loose, what society it would create, and that it was unstoppable once in motion?



By the time the two chipmunks begun their journey home, the sun had gone down; the forest without shadow and time imprecise once again. They took another way back, going in an arch, so as to see more of the forest; they did so in silence. But this was a differerent silence: the silence they'd shared for so many years, a rare and intimate silence that many an animal could go a whole life without ever knwowing. This was a silence one could grow old in and call it a good life - both knew it, but likewise they knew that their paths would soon diverge. 
Kraerion thought of a sun that was to earth bound, and of eternal returns; he entertained the idea, and smiled a solemn smile at his folly.

%Yet they're anything but imperishable; they're changed, transformed, amended, and forgotten only to be rediscovered again.


%A great discovery may seem inperishable once discovered, spreading and kept in the collective mind, yet they are not. The English count time in base 60, as that was how the Babylonians had their numeric systems. When realized that fingers made a better tool for the task of numbers, time remained in base 60. Intentions and reason long forgotten, yet here it remains inert. Now is but the cumulative residue of legacy %- forever parading the power of inertia. A fabric of time woven by fragments of lost meaning.
%Vlahir had placed five stones and three peddles between each. Not due to any particular reason or conviction, it had to be denoted in something. Generations past would be burden by his conjectures, to learn the meaning of shadows and stones. When the intended impact of Vlahir's ideas and monetary paradigm ultimatly subsides and perish, what will remain are five stones. A random thread of indeliberate noise woven together with other equally random threads which forms the beutiful and ever complex carpet of an ever changing society.

%Now is but the cumulative residue of legacy — a world tiled with fragments of lost meaning

%Now is the cumulative residue of legacy; the fabric of Time woven together with fragments of lost meaning.

%Kraerion had stopped listening, he did neither understand nor share their excitement. He instead watched the Oak intently, grasping the massive ongoing construction. In that moment he truly admired the crows, "what a disciplined bunch" he thought, "able to save for so long as to afford such a vast project." \\

Cinnamon and Vlahir had finally exhausted their conversation and Cinnamon urged Kraerion to continue their wander. They began heading back, but not the way they came. Instead they went in a circle; catching different glades on their retinas. They did not talk, but there was comfort in the silence. Both of them knew that the feeling was mutual. \\


They reached the birch Kraerion had made his home, they said farewell. As Cinnamon disappeared among the trees so too did the sun. He thought with a smile, "The sun is bound for eternal returns, so too will Cinnamon - whatever glade or burrow , she would return.". He looked forward to their next meeting and wondered if 'eternal' existed in their world.      


* Insofar as a number could be called arbitrary, number theorists please forgive me

I cant forget my roots, and roots have a proclivity for soil

%"Kraerion, I'm worried", she said suddenly, "It seem to me like we've worked more this year than we ever have before, but Shrub is very worried. He says again and again that food is short. I think he's having a nervous breakdown."

%"You know how shrub is, or you ought to by now. He's always concerned, even with his own shadow."

%"It's not only him though. Even I have less food saved for this winter, and you know how I am, or you ought to. I've always been frugal, always been more scared of winter than drawn to immediate pleasure. I don't know. I've earned more this season than any other, yet somehow it buys me less food. We haven't had any drought or any good reason for diminishing supply. Am I making any sense?"

%"To be honest, I've never thought about much since I moved out. What does Ripell say?"

%"He just parrots the crows, Eaglewing told him personally not to worry and that everything is fine. He seems to believe them, but I'm not so sure."

%"The crows have been right before?", Kraerion said a bit reluctant, "haven't they?"

"%I know", Cinnamon said quietly, "But I can't shake the feeling that something is terribly wrong. I just don't know what."



%There is a great difference between walking and wandering. To walk, is to have a purpose in mind. A destination to reach, a route to be taken. To wander however, is the purpose itself. For the simple pure joy of just wandering about. It may be said that there are two kinds of animals in this world; those who walk and those who wander. Kraerion belongs to the latter group, which separated him fundamentally from his chipmunk origins. A commune raised on logistics - to move goods under the forest, to do it on schedule and with efficiency. \\

%Kraerion expected to be reproached, as Cinnamon was clever and would take notice of his choice of words. Instead, to his surprise, she answered him with a short "Okey, sure!". He jumped the last meter down to the ground and they set off at a leisurely pace. \\

%"You smell different", Cinnamon said after a short while.\\

%"I do?", Kraerion said, "Must be those damn pigeons, passing droppings like its art.". He said it jokingly, as if they hadn't been apart. \\

%"You are never coming back, are you?", she said as she stopped, with her chipmunk eyes —black as pearls—  glaring through him. \\

%"No", he said staunchly after some thought, "I don't think I ever will."\\



%They continued in silence, seemingly exhausted by their situation. They were wandering past the old oak. Kraerion did not recognize it at first as he had only seen the glade when it was full with animals. The oak was under heavy construction, it swarmed with woodpeckers, rabbits and seemingly every carpenter up for hire. Even a roebuck was there dragging in materials. A few crows was spread out, directing the whole spectacle. A few paces from behind the oak stood Vlahir. The crow were standing in the middle of a semi-circle, consumed in deep thought. Next to him, in the exact middle, stood a straight stick perpendicular to the ground. The stick casted a long shadow in the morning sun. He looked up as the chipmunks approached him. 



%"Good morning", Vlahir said lightly. He was clearly in a good mood. \\

%"Morning", Kraerion responded, "What are the stones for?"\\

%"The sun runs in it's eternal circuit the Lord has given her. She does so alone, never able to befriend the moon half a day away. Her pace is beyond our world, too distant for us to comprehend; yet she passes the trees with a precision no mortal can ever rival. She is the measure of our days."\\

%"
%	The sun runs; circuit eternally bound
%	A desolate pace cursed by natural law
%	Shackeled to earth, ever to go around, % never to go aground
%	Yet her smile shines; and thy frozen bones thaw.
	
%	and trees of different glades

%"But the trees she lapses are firmly caught in place, animals raised in different glades, may not share their names. Just as she is, she treats them true - so the shadows they cast are thusly the same."\\


%"Yes, the sun rise in the east and the shadow will fall over the westernmost stone here", Vlahir said as he pointed at the first stone. "The shadow will then walk across the stones. If we align the semi-circle after the stars, we may be able to build multiple constructions at the same angel. It's not bounded to a singular position."\\

