\chapter{Dilution}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“The long run is a misleading guide to current affairs. In the long run we are all dead.” 
		\begin{flushright}- John Maynard Keynes \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}


"This has been the worst Winter of our generation." Zefrafa cried with an unusual high tone, "We've all sacrificed, we've all rationed, an most of us all - by some miracle - have survived to see spring again."  

Like salt to injury, the spring came late to the forest that year. The warm sunrays - when it finally came - was met as a saviour. They bathed in its warmth, and they kneeled to the it. They had survived.
It was a battered, bony, and thin group of animals that gathered in the glade beneth the Old Oak to, as they always do in early spring, assess the winter's damage. The oak itself seemed a bit battered too, and it did not stand with its usual might.  

"That said", Zefrafa continued with his more usual tone. He had spent many a night thinking and rethinking the time he had spoke in the glade, where he'd froze with the introduction of the stoats and he'd failed to make his point. He was not about to make the same mistake. "This must never be allow this to happen again! And we must look closly at the actions that put us here. Eaglewing, I'm looking at you. We took all the actions you asked, we followed through on every policy you suggested. Yet, we're standing here as survivors with the most dire of outlooks. There's no food, prices have stumbled, and there's no jobs - even for the most hardworking an animal - in sight. What do you have to say for yourself Eaglewing!?"

"This be non sense...", Eaglewing began, but he was interrupted before he got any longer.

"No, my dear Eaglwing", Snowball said, "I've only heard sense from Zefrafa. He speaks what we all think."

"Ic efencyme mid Zefrafa." said one of the moles.

"Nā, we efencymaþ mid Zefrafa.", another mole corrected.

A low murmur of ayes started going around the glade, and it could be not mistaken: Zefrafa had a clear majority.

When Zefrafa was about to speak again, a black shadow swept down from out of nowhere. 

The shadow gently landed on a branch of the Old Oak. And when he became still, the animals realized that it was none else than Hroðulf. The black crow looked around the glade with disgust, and began to speak.

"The snow have not yet melted, and you all are already pointing fingers and seeking a scape goat. When I - in my folly - was beginning to see us as civilised Animals, you all just have to disappoint and regress to the brutish beasts your ancestors were."

"I'm not seeking to be punitive", Zefrafa said hurt, "yet we must hold Eaglewing accountable for his actions. And it's through this - albeit harsh - discorse, we must ventilate our dissaproval in order to set a new course for our Forest."

"But Eaglewing's cute little play at policy did not cause this.", Hroðulf said waving his wing, "And although I'm sympathetic to Eaglewing's attempts at social reform, and I by no means impugn on such reform, they were too miniscule in scale and too late in implementation to have swayed our Forest one way or another. But - unlike you Zefrafa, or any other Animal for that matter - Eaglewing made an attempt to spur stimulation; and to simply attack his person is not the crticisim of democratic discorse you believe it to be. If you however could offer constructive insights of how Eaglewing's actions caused this winter's supply shortfall, I highly urge you to do so."

"Well", Zefrafa said with hesitation, "I can't explicilty describe in detail the cause and effect of this winter's shortfall; however, no Animal can. And Eaglewing's changes are the only difference from the generations of plentiful winters preciding this one."

"There you are wrong. I can explain; and I will explain.", Hroðulf said, and took a little break, retucked his black wings, and let the glade linger before he began again.

"My dear Zefrafa, answer me this: Is water water?"

"What are you playing at Crow!?", Zefrafa hissed frustrad, "is this what you call an explaination!?"

"Well yes!", Hroðulf exclaimed, "Riddles are these precious little things, tender and digestible with reality abstracted, to afford even the dullest of minds - like yours - some amount of comprehension. I ask you again: Is water water?"

"Yes.", Snowbal said after at length, when it was apperent that Zefrafa wouldn't respond. "Water is water."

"Ask the salmon, who dares his life on his heroic journey uspream, only to get from water to water?

Ask the beaver, who spends his days creating dams, only to form a pond in the brook - to live in water instead of water?

And ask the doe, whose fawn drank from a stale puddle born with disease instead of the running brook as she was taught - whose fawn drank water instead of water?

No, water is not water if life is not death. Water is a canvas, a medium that can be altered, shaped, or most importantly: controlled."

"Craaax", Eaglewing interrupted, "as facinating this tale of thine might be, how does it surve us? If it supposeth to be a parable, or allegory, or whatsoever of meaing, it's rather incomprehensable."

%"This must never be allowed to happen again!", Zefrafa cried, his voice void of the tremors of meetings past. "
%We've all sacrificed this Winter, 
%we've rationed and we've scrambbled to find .
%And, it wouldn't have been enough without the early warning from the Chipmunks, and their extrodinary effort to see us to spring.", the rabbit paused for empasis, "This must never be allowed to happen again, we require change!"

%"The hares are in agree.", said Snowball, and many more animals — if not all of them — nodded or made a sound of agreement.





