\chapter{Deputation}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“the only thing we have to fear is fear itself.”
		\begin{flushright}- Franklin D. Roosevelt \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

The crows watched as the animals poured in the glade---the Glade of Representatives. The murder sat comfortably tucked all along the branches of the ever reaching crown of the Old Oak. From afar it looked as if the Oak bore large, black acorns. Since the time of Man, the animals had gathered here to discuss public matters, to air opinions, and to converge on decisions. Although the glade bore a suggestive name, it wasn't a republic in the most human sense of the word. It wasn't a selected office: no animal spoke for a predefined set of members; instead, non present members usually had someone whom they trusted present, who could speak on their behalf if needed. In fact, the meetings in the Glade was open to everyone; and anyone who wished to speak could. The animal species differed though, in their eagerness to follow the discourse. Many of the crows and the rabbits were actively engaged in the discussions, and the presiding officer---responsible for the agenda and order---had been a crow for generations, and became referred to as the Twig. The rats and the blackbirds on the other hand, took little to no interest in the proceedings. The pheasants did not even attend; their concerns were more of worms, than with words.

Kraerion entered the Glade when it was almost full and opted---in the spirits of his now arboreal life---to join the birds amongst the trees. He was taken aback by the might of the Old Oak---its powerful branches and colourful leaves seemed as powerful and green as ever. As he found a comfy twig in a beech, he saw Aequitus and Pietus standing next to the rabbits; and his heart dropped. He felt at once uneasy. He knew he'd done nothing wrong by leaving, yet his body felt otherwise.

When the last roebuck straggled into the glade, a crow signaled for them to start. The crow took a few awkward skips out on the oak branch, so as to be seen by all. He bore the name Eaglewing. His right wing was unevenly discoloured: half the wing's feathers were of a peculiar colour of brown, not unlike the wings of an eagle. He had been an unlikely candidate to the office of Twig; although, he was the son of the previous one, Ongenþeow, but been born very much the runt of the litter. His discoloured wing was also rumored to be broken, and only a few crows could claim to have seen him fly. The crow began to speak:

\input{eaglewing_speech.tex}

The glade was in silence when Eaglewing receded backwards on the Oak branch---leaving room for Hroðulf---who quickly took his place. Whereas Eaglewing spoke with a confident, well-paced certainty, never missing an emphasis; Hroðulf spoke with a twitchy, irregular pitch, as if he never given the spoken word a forethought. The crow with his two perfectly black pair of wings was renowned for his wit, yet somehow very unpopular with the animals.

"There was once a man who proclaimed: incentives trump ethics every time.", Hroðulf began, "And we're not even Men; Men are creatures of sin, the only specie known capable of doing harm without direct benefit to his person---truly the purest form of evil. Us Animals are simpler: we're not driven by hate nor envy. Remove the incentives and you remove the act itself."

Hroðulf took a pause. He didn't lack confidence nor certainty in his message, but he lacked confidence however---especially in aggregate---in the animals' intellectual abilities. He knew he had to go slow, never leaving out a simple deduction of reason.

"If we remove the incentives for thievery, we remove thievery itself.", he repeated thus, "The thief steals only with the prospect of spending his spoils in the future; but what if what he has stolen could be rendered unspendable? Theft would be moot to him. Our screw nuts---which undoubtedly contains a diverse set of colour and shapes---are still too fungible to trace with any certainty. We can't efficiently tell them apart, we can't ban a particular stolen screw nut from ever being spent. Fungibility is certainly an admirable quality, but it and traceability are not necessarily contradictory traits; on the contrary, a traceable mark issued by the Glade could only serve as a valid baseline for the fungible unit. If an unique mark was inscribed on our screw nuts, and remarked before stolen; spending it would accomplish naught save the admission of guilt."

The crow took another pause, he knew his finale could create controversy and he made sure to get every word correct.

"There is however, no way to mark the screw nuts themselves; but, we can mark leaves. We suggest that the Glade temporarily issues leaves in place of our screw nuts, until this wave of crime calms down."

"I'm not sure I understand", Br'r Rabbit said after a moment of silence, "You want us to replace our screw nuts with leaves? But leaves are everywhere---you could just pick them up?"

"The leaves will be but a certificate of ownership to the real screw nut. The leaves will have an unique sequence directly corresponding to a screw nut safely stored elsewhere. The quantity will thus remain the same: one screw nut, one leaf."

"But, could you not simply copy the sequence, and spend it twice?"

"Yes, if not for our new secret process, effectively making the leaves impossible to counterfeit."

"Do I need to remind you all that leaves have a tendency to rot!?", a new voice bellowed from the far end of the glade. It belonged to Αίσωπος, the forest's last remaining badger. He emerged from the crowed and headed towards the center of the glade, and with him followed a strong, foul smell. The animals he passed jerked away from him; they did so however, more out of reflex than actual disgust.

"No, thou dost not." Eaglewing responded before Hroðulf had a chance to, "Thy apprehension saddeneth me. In the same process where we make the leaves counterfeit proof, a silkworm addeth a thin, almost transparent hue around the leaf: protecting it from wear, tear, and as thou hast so kindly contributed: rot."

"All but a gullible disposition would sadden you, I'm sure.", Αίσωπος roared, "This plan has so many flaws, where do I even begin...Let's begin with this: how can we be sure that the amount of leaves remain at a one-to-one ratio with the screw nuts?" 

"Before I respond to these ridiculous questions of poor judgment, let me remind ye that Αίσωπος is not your friend: he might have some ulterior motive with these questions---maybe his interests align with letting this issue remain unresolved.
Nevertheless, I shall address every rabbit of straw thou shalt call forth.", Eaglewing took a deep pause, showing off a sly grin, as if he had waited for exactly this moment, "We shall arrange regular audits of the amount of screw nuts in custody; as frequent as to give no doubt of any discrepancy."

"How shall the screw nuts be protected? To whom shall this significant burden fall upon? Perhaps this might be what the thief---who you ascribe so much influence---wants? Now they'll be gathered together in one place---one massive honey pot."

"We did not intend to disclose our plan to guard the screw nuts today. But, as a gesture...", Eaglewing didn't get further before being cut of by Αίσωπος.

"See Animals, as always these crows only reveal what suits them! I categorically doubt their competence to implement this scheme, but I doubt even more their reasons to go through all this trouble! The screw nut have served our Forest well; a guide towards efficiency, a creator of wealth. The screw nuts became the means of exchange not by decree, but by an organic force of Nature. And, who are we to intervene with forces we do not understand? And, Who are you to conspire against Nature?"

"But, as a gesture...!", Eaglewing repeated louder than before, "of good faith, I will tell thee. A few days ago, a few crows found a litter of stoat kittens---clearly abandoned by their mother---as they flew over a neighbouring meadow. They be but blind and furless; their animal still plastic, unformed by their natural instincts. We will raise them with a singular purpose: to guard and protect the screw nuts---with their life if necessary.\\
And, let me answer thy incomprehensible drivel about Nature with a question: Whence came that peculiar odor of thine, if not from Nature herself?"

"Ssss---Stoats!?", Br'er Rabbit shrieked, trembling like a shackled leaf on the wind, "I---I must have mistaken, did---did you say stoats?"

"You crows have gone \textit{completely} mad!", Αίσωπος thundered as he stormed off, "I will have no further part in this folly."

"Yes..., stoats", Eaglewing almost whispered in contrast, "But dost not worry Br'er Rabbit, we're long past the days of predation. I promise thee: they shall conform to our ways of life and abide our laws---I shall make that my personal mission. If anyone doth not object to the idea, of course?"

The question silenced the glade, yet the air told of unrest. Even though no animal in the glade had been alive in a time of predation, many of them still \textit{felt} like pray; the innate: that which no constitution, nor glade, can amend. No one spoke, not necessarily due to cowardice, but rather due to the limited time to come up with a reasonable objection.

Br'er Rabbit opened his mouth, but spoke in Silence. The beautiful language of Nature, but also the language with a thousand ways to say what you later come to regret.

The moment passed, Br'er Rabbit had not said a word---yet everyone had heard what he said.

"Good.", Eaglewing concluded, ignoring the silence, "It's decided. We are done here."\\

The forest had not---since inception---been without a guide. First, of course, it was aided by the laws of physics; thence, by the rules so elegantly described by Darwin; and eventually, by a certain hand which could not be seen. That hand was now feathered and coloured black, and it would remain visible---irreversibly---forevermore.