\chapter{Discrepancy}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
	“Concentrated power is not rendered harmless by the good intentions of those who create it.” 
		\begin{flushright}- Milton Friedman \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

The winter came early and hard. The migratory birds had long fled south to the more pleasant European-, and even African continent; the winter air were thus calm and quiet, save for the irregular cooing of the pigeons. The forest bed was covered in a thick layer of snow, its distribution made uneven by the wind and the trees. The animals hid in their burrows and lairs for most of the days, keeping close to preserve body heat. Winter but a game of waiting---a quarter of life on pause.

Kraerion wasn't immune to cold either, and he had prepared meticulously for winter: insulating the inner walls of his hollow with moss and lichen. He had Redrill carve him a round wooden piece, which could be rolled in front of his entrance to keep the shy warmth hostage. In the mornings though, he pushed the piece aside; he preferred the cold to the darkness, and a life in motion to a life on pause. He had watched as the days shrank shorter, the morning dew slowly morph to morning frost---a phenomenon difficult to grasp for a creature raised underground. And today---this particular morning---the sun rays danced for Kraerion's eyes on the unadulterated hoar frost covering the surface, seemingly stretching forever  in every direction. A dance of free admission, open to all, yet but a lone chipmunk hunched in a tree paid to enter---and in that moment, he was truly the richest animal in the forest.

%Kraerion wasn't immune to cold either, and he had prepared meticulously for winter: insulating the inner walls of his hollow with moss and lichen. He had Redrill carve him a round wooden piece, which could be rolled in front of his entrance to keep the shy warmth hostage. In the mornings though, he pushed the piece aside; he preferred the cold to the darkness of a life on pause. He had watched as the days shrank shorter, the morning dew slowly morph into morning frost---a phenomenon difficult to dissect living underground. 


The sun shifted and its rays partially blocked by a tree; the dance moved on to other avenues. Kraerion's mind wandered to the events in the glade: the attempted seizure of Αίσωπος, the death of the stoat, and the issued decree. The outlawed badger had never officially been attained, and no one knew for sure where he was. Nevertheless, many a rumour spread like wildfire that late fall and early winter. "He had been caught, killed, and buried by the stoats!", "No, he is still hiding in some old forgotten badgers' lair deep underground---biding his time!", "No, he sought out supporters to his cause, roaming the marshes to the east of the forest and preparing for war!" % Spinestack boasted, Greyhead conjectured

No one had definitive proof of their claims, yet the animals argued incessantly about it. Kraerion didn't know what to make of it himself. He didn't know the badger personally---no-one did!---but he had always appeared to him to be an animal of reason, and he couldn't wrap his head around how quickly Eaglewing had jumped to conclusions. Could Αίσωπος really be that cut-throat?\\

His morning conundrum were abruptly disturbed by Cinnamon who suddenly, and somewhat hastily entered the glade, in very much opposite manner she had done that late summer morning. This time she didn't stop at the base of the birch; instead, to Kraerion's surprise, she sprung up it. When she reached the hollow, she was out of breath and had to recover for a moment. She didn't have to speak for Kraerion to realize she came with news---and he could see in her pearl black that the news were grave.

"Veritas is dead", she finally mustered, still panting, "I think you better come."

They ran back together, in the quite winter silence that didn't appear as beautiful as it had just a few minutes before, only heavy. They entered the run and Cinnamon lead the way through the many turns that was slowly fading from Kraerion's memory. When they entered Veritas's spartan burrow, they were long out of breath. "Too many chipmunks---", Kraerion thought to himself as he pushed himself past the scurry, Cinnamon in his heels, "too many damn chipmunks." He saw his father leaning over his sister's lifeless body---his forepaw gently resting on her chest. Pietus was also standing there, he looked up when they approached and gave them a silent nod; Aequitus didn't notice them.

(Animals seldom die in burrows, but seek a quite place to die)

Kraerion's overwhelmed with emotions, finally had enough. 
"Get out!", hi screamed suddenly, surprising himself most of all, "get out, all of you!" 

When no one moved a limb, Pietus came to the rescue and bellowed "You heard him, get out!"



