\begingroup
	\fontsize{10pt}{12pt}\selectfont
		\begin{quote}

			"It looketh like we have successfully prepared for another winter. And it warmeth my heart that nigh every year we gather here, we are better along than the year before. Incrementally our quality of life improveth. Each year's improvement might appear invisible to the naked eye; nonetheless, over generations---in aggregate, since our humble beginnings---these changes be breathtaking.
			
			Ought we not be content with our progress? Oughtest thou not stand back in awe and admire our accomplishments?
			No, our pace be lousy at best! We have by no means inherited a perfect system. We are at the whims of markets---it ebbs, it flows---but it be never stable; and we suffer for it: wasting value in good times; erasing value in bad times---capricious jobs created; honest jobs lost, and progress resets. And, even worse: unfairness be an innate quality of markets, its abundance be distributed---by the sick wiles of Nature---according to a power law. To wit, as the book of Man saith: whoever hath, more shall be given; whoever hath not, even that shall be taken away.
			
			No, we ought not be content. Thou oughtest not stand in awe. And the first steps have already been taken: to ease the ebbs and flows of our markets; to reserve parts of our forest solely for recreation; to aid the Animals of our poorest percentiles---to eradicate destitution. Last namely: as ye already know, we imposed a small tax on transportation this previous spring which will aid a new institution; a program which will help animals who caneth afford to participate in the Winter Fund. Never again shall an Animal find herself in destitution---the only lack: a dearth of hunger."
		\end{quote}
\endgroup