\begingroup
%\begin{localsize}{10}
\fontsize{10pt}{12pt}\selectfont
	\begin{quote}
		"I am not the fool to deny, nor delay, the pretext by which we have so promptly gathered here today. It is ever so important---in times like these---to be blunt: attack the issue unto us---with naught but truth---frankly and boldly. 
		
		% mention screw nuts once(?)
		
		But first, fellow Animals, I would like to say this: it is in difficult times we get to show what we have been made of---our true colours and morals. And I am certain, our colours shall burn true and its brightness prevail! Our Forest shall endure, as it always hath endured: since the time of Man and the founding of this very Glade. I promise ye, we shall---once again---unite against our common foe, and earn a second wind with this imminent victory!
		
		If thou hast lost thy screw nuts, dost not worry; dost not attempt revenge---or any other folly---by thyself. Thou shalt be revenged---in Time---by a collective effort!
		I hold the firm belief that the fear itself is more dangerous than what we fear---wicked, dark, unsettling terror that have paralyzed every important function of our Forest. A few stolen screw nuts in themselves: are insignificant in the greater scheme of things; an empty forest, a lack of trade, a hoarding of goods, a canceling of service, and an arming and guarding of thine own: are significant. Our beloved Forest hath reached a complete standstill in the fear of theft; it ought to fear the lack of feed come winter. Fear of trade undealt. We have retreated back into our humble nests and spartan burrows; now we must advance with full force! Our Forest asketh for action, and action thou must allow us to take.
		
		We may wage war against this unknown perpetrator: a war of suspicion with accusation as ammunition. And we may not. Even a victorious battle against this enemy amongst us may lead us unto defeat---the loss of Time; to while whilst winter marcheth.
		
		In policy---as in life---it is difficult to seeth but the short term. To value tactic over strategy. Doth catching our foe red-handed---spending all our time and resources in the process---prevent any future crisis of this kind? Our reforms must gain strength from our history and turmoil; they must adapt from our scar-tissue, and our Forest evolveth by it.
		
		It saddens me to acknowledge: this Glade is not prepared for this challenge. It's in a sad state. It's currently but a mere group of volunteers!\\
		It hath no funds to relieve its victims.\\
		It hath no office to investigate this matter.\\
		And, ---\\
		it hath no mandate to prevent this---nor anything of equal disaster---to happen in the future.

		Our Forest hath grown, but our Glade hath not grown with it, and that must be set right. We are prepared to exhaust our full arsenal to meet this crisis. To go beyond what hath seen constitutional---and deemed reasonable---in the past. Our first step, thou wilt shortly learn from Hroðulf, yet that is but a beginning. So, I ask this Glade---and its Animals within it---for this final instrument to face this challenge---broad executive power, to wage a war with this crisis, the power that would be given unto me if our Forest was invaded by Man once again."
	\end{quote} 
%\end{localsize}
\endgroup