\chapter*{Preface}

This is the first out of two external revisions. So---although, I'd appreciate comments regarding grammatical errors, sentence structures and formulations---the focus is intended to be on the consistency of the story, the flow of the writing, the entertainment to the reader, and, most notably, the quality and feasibility of the book.

There will be, if this first one goes well, a second revision, where the focus will solely be on the language.

I've made an effort use British spelling and British words where there are multiple possibilities. E.g. brook over creek, autumn over fall, rubbish over trash.

Notably I've chosen to use whilst and amongst as the conjunction, preposition, adverb, and while solely for the verb. Similarly, I've chosen to use the somewhat increasingly archaic verb form of but. \\

This story is a satire; therefore, it touches on many ideas and references that is not entirely self contained within this book. It is my wish that the story is in itself self contained(in the same way Animal farm is self contained, albeit very boring if no association to the real world is allowed). However, much of the fun(or value) in reading it comes with the understanding of symbolism and the mockery within it. 
As part of this first revision, I've noted every outside reference(those that are intentional at least) made in this work. I do not want to rely on obscure knowledge of trivia however, and those references should not harm the experience of reading---if so, they should be removed. Please note every reference you are able to find---even the ones that are almost too obvious.
I've divided every outside reference in to three categories.\\[1cm]

\textbf{Category tier one, must be noted.}
Contains very few but obvious references that I think should be known by 80\% of the populace aged 18 or over. They are also imperative for the tale itself. Failing to understand these would make a really dull read.\\[1cm]

\textbf{Category tier two, may be noted.}
Missing to draw these connections should not interfere with the cohesiveness of the tale; they should be passed over without the reader feeling a sense of missing out. Understanding none of them would probably diminish the reading experience.
Most references are in this category.\\[1cm]
 
\textbf{Category tier three, unlikely noted.} 
This category contains all obscure references. They must be completely passed over with no hiccup, i.e. you'd never guess it's an reference if not told so. Some of these require some deduction, and I hope that even if they're found, It's not obvious that I put it there intentionally.

Perhaps unnecessary remark 1: the chapter quotes are carefully picked and are all relevant to the chapter's text.

Perhaps unnecessary remark 2: the character names are carefully picked and are all relevant to the story(albeit some more than others).\\[1cm]