Chapter 1\\[1cm]
c3: Darwin quote, hints to a tertiary theme of the book: [REDACTED].\\
c3: published in 1859, it fits perfect being ruffly 10 years before la belle epoque.\\
cX: I'm a fan of Darwin's work\\
c2: 'Natural checks and balances': a very darwinian sentence.\\
c3: Locks of gold --- Goldilock: both: https://en.wikipedia.org/wiki/Goldilocks\_economy, and https://en.wikipedia.org/wiki/Circumstellar\_habitable\_zone\\
c3: The beautiful era: La Belle Époque: https://en.wikipedia.org/wiki/Belle\_Epoque\\[1cm]
chapter 2 \\
c2: inertia: tertiary theme [REDACTED]\\
c1: Increase in specialization, very well known phenomena. Although I'd like to attribute to Adam Smith.\\ https://www.investopedia.com/ask/answers/040615/what-are-economic-impacts-specialization.asp\\
c1: Aorta, (arteriole), allegory(or metaphor, but I don't think so(?)) Circulatory system -> Logistics.\\
c2: Aequitus: Equality(Roman, but masculine form.) Also [REDACTED]\\
c3: Chief Chipmunk -> Adams's Chief Rabbit\\
c2: Br'er Rabbit, read Brother Rabbit.\\ https://en.wikipedia.org/wiki/Br\%27er\_Rabbit , also c3 reference to Adams's El-ahrairah(the multiple references to Adams should make this clear). Also Anansi and folklore. I've included it also due to the widespread censorship of him. It's absolutely ridiculous.\\
c2: Chipmunks' enterprise -> cooperative, it's a thing by itself:\\
https://en.wikipedia.org/wiki/Cooperative\\
But also relates to unionization.\\
c2: Winter Fund -> private health insurance\\
c2: Ongentheow: King of Svea. Egil Vendelcrow, makes sense since he is a [REDACTED], also literally means 'Against Slavery' which is also very fitting with the introduction of Br'er Rabbit in the exact same sentence.\\
c1: Glade of Representatives -> House of Representatives or any form of Parliamentary structure.\\
c2: Pietus: [REDACTED](Roman, but masculine form.) Also [REDACTED]\\
c2: Veritas: Truth(Roman, true feminine form.) Also [REDACTED]\\
c1: Moles speaking Old English, also spins on tertiary theme [REDACTED]\\
Chapter 3\\[0.1cm]
c1: Aritole, continuation.\\
c1: screw nuts -> gold.\\
c2: Death is the mother of beauty. Wallace Stevens Sunday Morning.\\
c2: Death is the mother, reciprocal altruism, screw nuts 'of other beauty', transcend death. All of same theme.\\
c2: Markets with everything available, woodpecker 'commercial interest', describing a Laissez-faire free market system. Or 'Capitalism'.\\
c2: Chapter quote, said 'emergencies' happens in the chapter.\\
c2: Having Hayek quoted tells quite a lot by itself.\\
c2: Heap and Stack, CS related.\\
c1: State of emergency.\\
Chapter 4\\[0.1cm]
c1: Glade of Representatives, a republic 'democratic' institution\\
c1: Twig -> speaker, or chairman\\
c2: Eaglewing -> Franklin D. Roosevelt\\
c2: Eaglewing disabled wing can't fly, Roosevelt couldn't walk.\\
c2: Eaglewing's speech, Franklin's inaugural speech. Two paraphrased quotes, many uses of war like analogies to fighting the economy.\\
c2: Hroðulf -> [REDACTED]\\
c2: "Incentives trump ethics", said by Steven Eisman at a debate at Oxford about the '08 crash. Named Mark Baum in the Big Short, played by Steve Carell.\\
c1: Leaves -> fiat currency.\\
c2: Aesop -> It's a fable, Aesop being the father of fables.\\
c1: Stoats -> police or military, enforcing by force.\\
c2: invisible hand, very well known reference to a free economy, Adam Smith. Some Smith as previously referenced.\\
c3: laws of physics, rules described by Darwin, invisible hand, irreversible: [REDACTED]
