\chapter{Deputation}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		``the only thing we have to fear is fear itself."
		\begin{flushright}- Franklin D. Roosevelt \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

%\renewcommand*{\thepage}{\footnotesize\babylonian{page}}
\setcounter{page}{23}

The crows watched as the animals poured into the glade---
the Glade of Representatives.
The murder sat comfortably tucked all along the branches of the ever-reaching crown of the Old Oak.
From afar, it looked as if the Oak bore large, black acorns.
Since the time of Man, the animals had gathered here to discuss public matters, to air opinions, and to converge on decisions.
Although the glade bore a suggestive name, it wasn't a republic in the strict human sense of the word.
It wasn't an elected office: no animal spoke for a predefined set of members; instead, absent members usually had someone present whom they trusted to speak on their behalf if needed.
In fact, the meetings in the glade were open to everyone, and anyone who wished to speak could.
The animal species differed widely in their eagerness to follow and participate in the discourse.
Many of the crows and the rabbits were actively engaged in the discussions, and the presiding officer---responsible for the agenda and order---had been a crow for generations, and had come to be known as the Twig.
The rats and the blackbirds, on the other hand, took little to no interest in the proceedings.
The pheasants did not even attend; their concerns lay more with worms than with words.\\

Kraerion entered the glade when it was almost full and opted---in the spirit of his now arboreal life---to join the birds amongst the trees.
He was taken aback by the might of the Old Oak---its powerful branches and colourful leaves seemed as sturdy and green as ever.
As he found a comfortable twig in a beech, he saw Aequitius and Pietus standing next to the rabbits, and his heart dropped.
He felt at once uneasy.
He knew he had done nothing wrong by leaving, yet his body felt otherwise.

When the last roebuck straggled into the glade, a crow signaled for them to start.
The crow took a few awkward skips out onto the oak branch, so as to be seen by all.
He bore the name Eaglewing.
His left wing was unevenly discoloured: most of the wing's feathers were of a peculiar shade of brown, not unlike the wings of an eagle.
He had been an unlikely candidate for the office of Twig; although he was the son of the previous one, Ongenþeow, he had been born very much the runt of the litter.
His discoloured wing was also rumoured to be broken, and only a few crows could claim to have seen him fly.
The crow began to speak:

\input{second_version/eaglewing_speech}

The glade was in silence when Eaglewing retreated along the oak branch---leaving room for Hroðulf---who quickly took his place.
Whereas Eaglewing spoke with a confident, well-paced certainty, never missing an emphasis, Hroðulf spoke with a twitchy, irregular pitch, as if he had never given the spoken word a forethought.
The crow with his perfectly black pair of wings, was renowned for his wit, yet was somehow very unpopular with the rest of the animals.

``There was once a man who proclaimed: incentives trump ethics every time," Hroðulf began.
``And we're not even Men; for Men are creatures of sin, the only species capable of doing harm without direct benefit to themselves---truly the purest form of evil.
We Animals are simpler: we're not driven by hate nor envy.
Remove the incentives, and you remove the act itself."

Hroðulf paused.
He lacked neither confidence nor certainty in his message, but he did lack confidence---especially in the aggregate---in the animals' intellectual abilities.
He knew he had to proceed slowly, never omitting a simple deduction of reason.

``If we remove the incentives for thievery, we remove thievery itself," Hroðulf summarized.
``The thief steals only with the prospect of spending his spoils in the future; but what if what he has stolen could be rendered unspendable?
Theft would be moot to him.
Our screw nuts---which undoubtedly contain a diverse set of colours and shapes---are ultimately interchangeable.
We cannot efficiently tell them apart, and thus we cannot track them with any certainty.
We cannot ban a particular stolen screw nut from ever being spent.
It is certainly an admirable trait that one screw-nut is equal to another, but being interchangeable and identifiable are not necessarily contradictory traits; on the contrary, a mark of origin issued by the Glade would only prove that the unit is valid.
If a unique mark were inscribed on every screw-nut, making it identifiable before being stolen---spending it would accomplish naught save the admission of guilt."

The crow paused once more.
He knew his finale would create controversy, and he made sure to get every word proper weight.

``There is however, no way to mark the screw nuts themselves.
However, we can mark leaves.
We suggest that the Glade temporarily issues leaves in place of our screw nuts until this wave of crime calms down."

``I'm not sure I understand," Br'r Rabbit said after a moment of silence.
``You want us to replace our screw-nuts with leaves?
But leaves are everywhere---you could just pick them up?"

``Each leaf will only be a certificate of ownership of the real screw-nut," Hroðulf explained with precision.
``Each leaf will bear a unique sequence directly corresponding to a screw-nut which is safely stored elsewhere.
The quantity will thus remain the same: one screw nut, one leaf."

``But, could you not simply copy the sequence, and spend it twice?" Br'r Rabbit huffed.

``Indeed you could, were it not for our new secret process to fortify them, effectively making the leaves impossible to counterfeit."

``Do I need to remind you all that leaves have a tendency to rot!" a new voice bellowed from the far end of the glade.
It belonged to Αίσωπος, the forest's last remaining badger.
He emerged from the crowd and headed towards the center of the glade, and with him came a strong, foul smell.
The animals he passed jerked away from him; they did so, however, more out of reflex than actual disgust.

``No, thou dost not," Eaglewing responded before Hroðulf had a chance to.
``Thy apprehension saddeneth me.
In the same process where we make the leaves counterfeit proof, a silkworm addeth a thin, almost transparent glaze around the leaf: protecting it from wear, tear, and---as thou hast so kindly contributed---rot."

``All but a gullible disposition would sadden you, I'm sure," Αίσωπος roared.
``This plan has so many flaws, where do I even begin... Let's begin with this: how can we be sure that the number of leaves remains at a one-to-one ratio with the screw-nuts?"

``Before I respond to these ridiculous questions of poor judgment, let
me remind ye that Αίσωπος is not your friend: he might have some ulterior motive with these questions---maybe his interests align with letting this issue remain unresolved.
Nevertheless, I shall address every rabbit of straw thou callest forth." Eaglewing took a deep pause, showing off a sly grin, as if he had waited for exactly this moment.
``We shall arrange regular audits of the number of screw-nuts in custody, as frequent as to give no doubt of any discrepancy."

``How shall the screw nuts be protected?" Αίσωπος continued.
``To whom shall this significant burden fall?
Perhaps this might be what the thief---to whom you ascribe so much influence---wants?
Now they'll be gathered together in one place---one massive pot of honey."

``We did not intend to disclose our plan to guard the screw-nuts today.
But, as a gesture---" Eaglewing didn't get further before being cut of by Αίσωπος.

``See, Animals, as always these crows only reveal what suits them for the moment!
I categorically doubt their competence to implement this scheme, but I doubt even more their reasons to go through all this trouble!
The screw-nuts have served our Forest well---a guide towards efficiency, a creator of wealth.
The screw-nuts became the means of exchange not by decree, but by an organic force of Nature.
And who are we to intervene with forces we do not understand?
And who are you, Eaglewing, to conspire against us and Nature herself?"

``But, as a gesture---!" Eaglewing repeated louder than before.
``Of good faith, I will tell thee now.
Some days past, a few crows found a litter of stoat kittens---clearly abandoned by their mother---as they flew over a neighbouring meadow.
They be but blind and furless; their mind still pure, unformed by their natural instincts.
We shall raise them with a singular purpose: to guard and protect the screw-nuts---with
their lives if necessary.
And let me answer thy vain babblings about Nature with a question of my own: Whence came that peculiar odor of thine, if not from Nature herself?"

``Ssss---Stoats!?" Br'er Rabbit shrieked, trembling like a shackled leaf on the wind.
``I---I must have mistaken, did---did you say stoats?"

``You crows have gone completely mad!" Αίσωπος thundered as he stormed off. ``I will have no further part in this folly."

``Yes..., stoats," Eaglewing almost whispered in contrast.
``But fret not, Br'er Rabbit, we are long past the days of predation.
I promise thee: they shall conform to our ways of life and abide by our laws---I shall make that my personal mission.
Unless anyone doth object to the idea, of course?"

The question silenced the glade, yet the air told of unrest.
Even though no animal in the glade had been alive in a time of predation, many of them still felt like prey---the innate: that which no constitution, nor glade, can amend.
No one spoke, not necessarily due to cowardice, but rather due to the limited time to come up with a reasonable objection.
Br'er Rabbit opened his mouth, but spoke in Silence---the beautiful language of Nature, but also the language with a thousand ways to say what you later come to regret.
The moment passed.
Br'er Rabbit had not said a word---yet everyone had heard what he said.

``Good," Eaglewing concluded, ignoring the silence.
``It is decided.
We are done here."\\

The forest had not---since inception---been without a guide.
First, of course, it was aided by the laws of physics; thence, by the rules so elegantly described by Darwin; and eventually, by a certain hand which could not be seen.
That hand was now feathered and coloured black, and it would remain visible---irreversibly---forevermore.