\chapter{Departure} % 12

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “Hell is truth seen too late.”
        \begin{flushright}- Thomas Adam \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}

The winter was mild, the snowfall light, and the usual biting cold had not blessed them with its presence.
Yet, despite the winter's mercy, the animals died like fly larvae in drying puddles.

To a human, it could appear as though the forest were locked in a brutal civil war, heavy casualties mounting on both sides. But there were no armies, no heroic battles, and no weapons to be seen. The war was one of attrition against nutrition and cold, the enemy that of Nature. And, contrary to war, it's the meek that fall---the kits and the pups, and the old whose motor is not what it used to be.

Deep underground, below the warm snow-covered blanket, Kraerion crept through the silent runs. It was late evening, and most animals were already tucked in to keep their warmth. He moved with caution---his frame turned meager from the dearth of feed---in search of anything edible to steal. The chipmunk was a ghost of his former self; the once proud and moral being had reverted to a simple thief. But, in a way, he was still the same chipmunk---what really is morality, when your kits are starving?

To Kraerion's surprise, he had been allowed to stay on as the logistics manager. But Pietus had taken every precaution to limit his access. His uncle had moved the Winter Fund's resources, and had him watched for most of the days. There was little solace in that, however; his wage was but a small defense against the Grim Reaper.

A noise down the run startled Kraerion. ``Scat," he whispered to himself, pressing himself hard against the run's wall, holding his breath. The noise was coming closer, he had nowhere to go, nowhere to hide. He moved to the middle of the run, to appear less suspicious.

``Who's there?" someone called out, ``I can hear you, show yourself!"

Kraerion sighed heavily. ``It's just me, Kraerion", he called out.

A rat trotted up to him. ``Oh, thank heaven," Pip sighed, ``It's only you. Anyway, what are you doing here at this hour?"

``Erm", Kraerion mumbled to give himself some more time to think. ``I'm... I'm just patrolling, making the rounds. We've had some thefts."

``You too!", Pip said, his face washing in relief. Kraerion's body relaxed; Pip did not suspect him. ``We had someone steal nuts in the night, multiple times."

``Yes, I heard that," Kraerion lied, guilt rushing over him---he was, in fact, the thief. He needed to keep his cool. ``Have you taken any measure against it?"

``We've instituted a neighbourhood watch program. Volunteers have signed up to keep guard," the rat explained. ``It's my night tonight. Have the chipmunks done the same?"

``Yes, in a way...", Kraerion lied again. \textit{``What was he going to do now?"}, his mind screamed. Although it pained him to steal from the rats that were no better off than himself, he \textit{needed} that feed. ``Anyway, have you seen anything suspicious tonight?"

``No, it's been quiet so far.", Pip said slowly, ``Except you, of course."

The rat's expression changed slightly, his eyes narrowing. \textit{``Had he been made?"}, Kraerion question himself with horror. Something in the chipmunk's conduct must have given him away; the rat looked very uncomfortable now.

``I, I think I should head back now," Pip said stumbling over his words, ``I wish you a calm evening."\\

The rat left Kraerion alone with his thoughts. Panic seized him; his chest felt like it was going to explode. Pip knew. He pulled his knees to his chest, his meager body trembling. He had lost his dignity, and was yet to lose much more than that.

An image of his burrow flashed before him: Cinnamon, wrapping herself tightly around the kits, to share what little body heat she had left. He had failed them. Pip must already be on his way to tell the rest of the forest, to tell the Crows. There was nothing left for him to do. He forced himself back to his feet, a tear trickling down his snout.

The crushed chipmunk began to take the first steps back home. His mind spiraled, a haze of his long-lost dreams flashed before his eyes. His dear hollow, the beautiful sun. Everything he had sacrificed---sacrificed just to lose it all. Cinnamon and himself might still survive, their remaining body fat keeping them alive---but not the kits. They had not had time to accumulate any fat. And, even if he did survive, what would happen to him next? A life in exile?\\

Suddenly, voices appeared in the dark, followed by a vague light. Kraerion looked up, not recognizing where he was. He had, for the first time in his life, become lost in the runs. This must be a recently built run, a very narrow one at that. Regardless, he followed it towards the voices.

The run widened, and eventually he exited into a massive hall. The ceiling and walls were covered with bright lights, \textit{``it must be some kind of glow-worms, trapped somehow,"} Kraerion thought. The walls of the hall was covered in gorgeous wooden paneling, that must have been carved by a skilled woodpecker. Around the glow-worms, set with equal spacing, sat decorative screw-nuts fastened, in a mezmerizing recursive pattern.

His eyes slowly adjusted to the lights, and he saw Crows, Magpies, and a few other animals. They were all eating and laughing around a big oaken table. He wittnesed a feast of excess, and his mouth watered. This must be directly below the Old Oak, he realized. This was what he had witnessed that wonderful summer day with Cinnamon, back when life was still beautiful.

A crow must have noticed him standing there. ``Hello there, Kraerion!", he cawed. ``Don't be shy!"

The bird was moving towards him now. Kraerion saw, to his surprise, that it was Hroðulf.

``Why the long face?" Hroðulf exclaimed.

``What is this place...?" Kraerion said astounded, ignoring the question entirely.

``Oh, this?", Hroðulf began, gesturing with his wing. ``It's the Twig's round table, where all the major decisions are made. A bit much, isn't it?"

``I've never seen anything like it," Kraerion answered, ``A bit much doesn't begin to cover it."

``Yes, my point exactly!", the crow hooted cheerfully. ``But, we saved the Forest! And if the comfort of this room makes our decisions get only one percent better, it's all worth it."

``Excuse me," Kraerion said in absolute disbelief. ``Saved the Forest? Do I look \textit{saved} to you?"

``Ah, you're confusing anecdotes with empirical evidence," Hroðulf smirked. ``It's a common mistake; don't feel too bad. We've measured the Gross Forest Yield, and the average animal has spent more leaves this year than ever before. Even if you adjust for the loss in purchasing power, the velocity of trade more than makes up for it. The forest is richer now than it ever has been."

``But, what about us... all our hard work?" Kraerion couldn't stop the tears from falling now. ``How come you wouldn't fund the Winter fund more?"

``Good question!" Hroðulf praised, speaking as if he were lecturing a child. ``I would argue that public must have great negotiators since they're representing the interests of the whole forest. They must be as ferocious with the public's leaves, as if they were their own."

The bird took a pause, tapping his beak thoughtfully, ``And in your personal case... I'm quite surprised you chipmunks chose Pietus to represent your interests. He's a slave to virtue, that one. A very naive and poor economic steward, truth be told."

``But, what about the windmill." Kraerion looked around, seeing the luxurious hall through his tears, ``and this place, you did not spare the public here, did you?"

``Ah, that is very different," Hroðulf said warmly. ``The Forest was in a tough place. Many an animal was unemployed. We needed more jobs so that the animals got leaves to spend again, which in turn would stimulate the economy. You chipmunks were already fully employed. And, while I'm not fond of vanity projects---especially dumb ones like the windmill; where would we even get the wheat from?---they \textit{do} create jobs. I would even go so far as to support a project where we dig a massive hole, just to fill it back up again, so long as it adds jobs to the Forest."

The Crow took another pause, a proud smile spreading across his beak. ``And with the result in hand, unemployment is almost non-existent. We must conclude that the windmill was a resounding success!"\\

Something finally clicked in Kraerion. He understood that he didn't understand---that he would never understand. That was his fatal flaw.

The chipmunk left Hroðulf and the feast without saying another word. He walked blindly back through the narrow run, eventually finding a path out to the biting cold and free, unadulterated air. The night was quiet, the stars told of a world still beautiful. After all that hard work, and all that pain, he deserved some rest. \textit{``At least the cold is real."} he thought; a thought that would be his last.
He curled up in the snow beneath the roots of a grand spruce, closed his eyes, and finally found peace. \\

Death is not the opposite of life, just as ignorance is not the opposite of knowledge---it's merely a lack thereof.

If you had asked Kraerion at the beginning of this tale what the opposite of life was, he would have answered without hesitation, with his back straight, and his head held high: \textit{to not have lived}. To be but a passenger while life passes by; to leave the proverbial marrow left unsucked. And if \textit{to live} is the answer to life, then spelling it backwards reveals another answer.

Whatever the opposite of life might be, we know this to be true: Kraerion did die, but he never lost his life; he had but no life left to lose.

%Death is not the opposite of life, as ignorance is not the opposite of knowledge---only a lack thereof. If you had asked Kraerion in the beginning of this tale, what the opposite of life is, he would have answered without hesitation, and with his back straight: that the opposite of life, is not to have lived. To not live your life to the fullest, to be but a passanger while life passes by---to leave the proverbial marrow left unsucked. And, if to live, is the answer to life, its ananym, its spelling backwards might reveal a final answer. Whatever the opposite of life might be, we know this to be true: Kraerion did die, but he never lost his life; he had but no life left to lose.