\begingroup
%\begin{localsize}{10}
\fontsize{10pt}{12pt}\selectfont
	\begin{quote}
		"I am not the fool to deny, nor delay, the pretext by which we have so promptly gathered here today.
		It is ever so important---in times of such tribulation---to be blunt: attack the issue before us with naught but truth, frankly and boldly.
		
		% mention screw nuts once(?)
		
		But first, fellow Animals, I would say unto you this: it is in difficult times we are called to reveal what we are truly made of---our true colours and morals.
		And I am certain, our true colours shall burn bright, and their brightness shall prevail!
		Our Forest shall endure, as it hath always endured, since the time of Man and the founding of this very Glade.
		I promise you, we shall---once again---unite against our common foe, and find a second wind with this imminent victory!
		
		If any amongst you hath lost her screw-nuts, let her not despair; let her not seek foolish vengeance by her own claw or beak.
		Ye shall be avenged---in due time---by our collective, united strength.
		For I hold the firm conviction that fear itself is a far graver danger than the very thing we fear---a wicked, dark, unsettling phantom that hath paralyzed every vital function of our Forest.
		A few stolen screw-nuts are, in themselves, insignificant in the grander measure of things; yet an empty Forest, the cessation of trade, the hoarding of feed, the forsaking of service, and the fearful arming and guarding of your own nests and burrows---these are calamities of the highest order.
		Our beloved Forest hath been brought to a complete standstill by the fear of theft; when, in truth, it ought rather fear the famine of winter and the ruin of trade left undone.
		We have retreated back into our humble nests and spartan burrows; now we must advance with unwavering resolve!
		Our Forest crieth out for action, and action ye must empower us to take.

		We might wage a war of suspicion against this unknown perpetrator, with accusation as ammunition.
		Or we may not.
		Yet, even a victorious skirmish against this enemy within may lead us unto ultimate defeat---the squandering of time, to while whilst winter marcheth ever closer.
		
		In governance---as in life---it is a folly to see but upon the morrow, to exalt tactic over strategy.
		Doth the mere snaring of our thief red-handed---spending all our strength and resources in the chase---prevent the return of such a crisis?
		Nay.
		Our reforms must gain strength from our history and turmoil; they must be built upon our scar-tissue, and our Forest evolveth thereby.
		
		It grieveth me to confess: this Glade is ill-equipped for this trial at hand.
		It is in a woeful state indeed.
		It is presently but a mere fellowship of volunteers!\\
		It hath no treasury to relieve its victims.\\
		It hath no constabulary to investigate this wickedness.\\
		And, ---\\
		it hath no mandate to prevent this---nor anything of equal weight---from rising again in the future.

		Our Forest hath grown, but our Glade hath not grown with it.
		This must be set right, and set right this very hour.
		We stand prepared to exhaust our full arsenal to meet this crisis.
		To go beyond that which hath been deemed constitutional---and held reasonable---in the peaceful days of yore.
		The first of these measures ye shall shortly learn from Hroðulf; yet that is but a beginning.
		Therefore, I ask this Glade---and the Animals within it---for this final instrument to vanquish this peril: broad executive power. % Absolute dominion, absolute stewardship.
		I ask for the mandate to wage a war against this crisis, a power as great as the power that would be given unto me if our Forest were indeed invaded by Man once again."
	\end{quote} 
%\end{localsize}
\endgroup