\chapter{Duty}

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “Until they become conscious they will never rebel, and until after they have rebelled they cannot become conscious.”
        \begin{flushright}- George Orwell \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}


The sun rose slowly above the tree line, the first rays piercing the entrance of Kraerion's hollow in the birch. As had now become habit, the chipmunk sat perched at the threshold, watching the world wake up.
But unlike the weeks prior, where a calm and beautiful winter lanscape had greeted him, only a grey slop of dead undergrowth and leafless trees met Kraerion's gaze. The thaw left the forest naked, in limbo, before the spring would arrive and dress it.

And unlike the previous weeks, he no longer felt the same gratitude for the sun's warmth. He no longer feel like the richest animal in the forest.

``Is this it?", he thought somberly, ``Is this the life I've been chasing all my life?"

He had been so focused on the pursuit---on the thrill of achieving it---that he never considered, never anticipated, the feelings that had now caught up to him. Guilt. A heavy weight in his chest. It was the feelings of loss, and the gnawing knowledge of his inability to prevent it. He knew, rationally, that he wasn't responsible for Veritas's death. Yet, a whisper in his mind insisted that if he had made different choices---less unorthodox choices, less selfish choices---Veritas would still be alive and well.

He shook his head, pushing the thoughts aside. That line of thinking would never lead to anything good.\\

Kraerion sighed, and stood up. He began to climb down from the birch. Every day since Veritas's death, he had gone back to his family's burrows underground, and today was no exception.
He landed on the ground, his feet sinking into the mud as he walked towards the run. The path usually offered him solitude, but not today; the forest was bustling with animals, all of them in frantic hurry.

As he rounded a bend on path, he had to step off it entirely. A team of beavers were heading in the opposite direction, but instead of carrying logs for a dam, they were hauling large bulging pouches.

"Make way! Make way!", the first beaver shouted, his voice surprisingly cheerful for the early morning.

Kraerion had no choice but to step aside, he leaped onto a tree stump to let them pass.

``Oh sorry there, Kraerion!", the beaver said. Kraerion recognized him as Castor, a friendly but a \textit{simple} creature. ``I didn't see you there!"

``That looks like a heavy load---", Kraerion said, pointing a paw at the pouch. ``Building a new dam?"

``No, no, no! It's not for the dam", Castor replied, a wide grin appearing on his face. ``It's a thick bundle of leaves from the Crows. They're commissioning a massive windmill on the other side of the river. Bought the land from the hedgehogs!"

``A windmill?", Kraerion said, puzzled. ``What is a windmill?"

``I don't know exactly.", Castor answered honestly, ``but I think it's some kind of machine to make bread..."

``But what is bread?", Kraerion asked, even more confused, ``Is it some kind of food?"

``Yes! you know those city birds that live in the wadborough village", a younger beaver Kraerion didn't recognize chimed in, ``Um, the winged rats of the sky I think they're called. They eat it all the time!"

``Winged rats?", Kraerion snapped, ``They're called pigeons. You're aware that Chipmunks are also rodents, aren't you?"

``Ah, relax, Kraerion", Castor said quickly. ``He means no offense---beavers are rodents too, after all! Yes, pigeons eat it---they call it \textit{Breadcrumb aux Poubelles}, it's a delicacy, the best food of them all, apparently!"

``I see", Kraerion said after a while, still wrapping his head around the absurdity of it. ``And, they've already paid you?"

``Paid us upfront, yes!", Castor laughed slapping the pouch on his back, ``For the whole summer's labour! It's all part of a bigger incentive to increase demand, or something like that. RAIN they called it, I don't remember what it stands for, though."

``It means", the younger beaver added, ``Rebuild Abundance, Invest in Nature." The young beaver beamed proudly, looking at castor for approval, who nodded slightly in his direction.

``Thanks Flat-tail", Castor remarked as he opened his pouch, ``But never mind some silly name---LOOK AT THIS, Kraerion. I've never seen this much wealth in my life. The missus is already planning to expand our lodge in the dam, it's all very exciting!"

``That's great Castor...", Kraerion said at length, he could sense that there was something terribly wrong with the whole situation---but what exactly, he couldn't put his paw on it. Then it dawned on him. ``But what about the screw-nuts? What about the vote next week?"

The beaver's grin faltered, but only for a second. He leaned in, lowering his voice conspiratorially, ``Well, that's the thing. It's in the deal, Clause four to be exact. If the vote goes in favor of the screw-nuts, the contract is voided. They said their initiative wouldn't work without the leaves. Something about liquidity and public spending, but it all sounds like greek to me."

Kraerion went still, ``Voided? Don't you find that strange, Castor?"

``Well, between you and me", Castor gave Kraerion a not-so-subtle wink, ``we're not the only one who's been paid, and the hedgehogs land purchase has a similar clause too. It's pretty clear how the forest will vote next week."

When Kraerion just stood there dumbfounded, Castor adjusted his pouch, ``Well, time for us to get to work! We have lots of leaves to spend! See you around Kraerion!"\\

Kraerion watched them go, a cold dread settling in his stomach. He wondedered about the integrity of the vote, the future of the forest, but then firmly shook his head.
He reminded himself that this was not his fight---this wasn't in his cards. He had his own life to build.

He hurried the rest of the way underground, slipping into the main burrow known as the Aorta. The Aorta had always been---in Kraerion's fading memory---a place of controlled efficient chaos. But today, it was in a state of utter disarray. Messengers dashing back and forth, stacks of to-be-delivered cargo lined the earthen walls, and chipmunks stood around with a paralyzing mix of urgency and confusion.
Kraerion pushed through the commotion, making his way to a side burrow that was Aequitius's personal office. Inside, he found Aequitius, who was sitting on a neat pile of straw, shaped into what best can be described as a makeshift chair. His eyes were bloodshot, his fur was unkempt---he looked like he hadn't slept in a week.

``It doesn't balance.", Aequitius muttered, scratching with a piece of dried root at the massive schematic carved into the dirt walls, clearly not noticing Kraerion's presence. ``What am I missing?"

``Father?", Kraerion said, stepping into the room, ``Is everything alright?"

The older chipmunk jumped, startled. ``Oh, it's just you Kraerion, I didn't see you there..." Aequitius said, his voice trailing off, sounding incredibly fragile. ``Sorry, I'm just... I'm trying to get my bearings again. Veritas took over the scheduling a long time ago. You see this? Is any of this making sense to you?"

``I would love to help, father", Kraerion began hesitantly, ``But, to be honest, do you really think that's a good idea? You know, that's not the path I've chosen for myself"

``Not this scat again, Kraerion", Aequitius roared, his voice rising into his former self, ``Don't you get it, Veritas is dead---Wake up!"

Kraerion stiffened, trying to keep his cool ``I am awake, father. There are hundreds of capable chipmunks in your service. Pick someone else, train them."

``How can you \textit{still} not understand? I can't just pick one!" Aequitius snapped, hurling the root at the wall, ``Our entire operation functions on fairness, Kraerion! Every worker earns equal pay by the amount they carry, by digging and sweating in the runs. If I arbitrarily pull a random chipmunk off the line and crown him my successor just to spare your feelings, I destroy the very meritocracy we've built!

Aequitius slumped back into his straw chair, losing his short burst of energy, suddenly looking his age again.``You want to live out there like a commoner, free of the family's obligation. You were raised with privilege---with the education and the experience required to lead. Would it be fair to drop the entire weight of our enterprise onto some random chipmunk---someone without the knowledge, without the privilege to justify the burden---just because my own son is too proud to do his duty?"

He looked up at Kraerion, pleading but firm.

``Leadership isn't a prize, Kraerion; it's a burden. You didn't choose your privilege, so you can't choose your burden---that is the paradox of equality."

Kraerion stood frozen for a moment. The silence was thick and deafening, broken only by Aequitius's ragged breathing. There was a voice in Kraerion's mind screaming at him to turn around, arguing that this was not his burden to bear, that he had his own life to live. Yet, he stood there, staring at his old frail exhausted father.

Without anything better to occupy his mind, his gaze slowly drifted to the schematic on the dirt wall. At first, it just appeared as a complex, chaotic mess of lines and numbers, but as he stared at it longer, patterns began to emerge. He saw that a scurry of chipmunks were to pick up a bundle of old hay at Rabbit's Hill at one small stone past the third big stone this very afternoon. But, just a small stone later, they were supposed to deliver twigs to a crew of woodpeckers.

\textit{There's no way they would have time to do both}, he thought. He glanced back at the schematic tracing a different line. \textit{There}---another scurry had a pickup at the robins next door at exactly four stone; they could simply handle the delivery instead.

Kraerion slowly walked towards the piece of dried root lying on the floor. He picked it up and pointed it at the wall.

``Wouldn't it be better", he began softly, ``if scurry F, instead of scurry B, delivered the twigs to the woodpeckers, since they already have a pickup at the robins next door at four stones?"

Aequitius stared at the carving, then at Kraerion. Pausing for a moment, before a tired smile appeared on his weathered face. He let out long breath. ``Yes", Aequitius whispered hoarsely.``I don't know why I didn't see that myself."

They spent the next hour going through the schematic together, finding small inefficiencies here and there. To Kraerion's surprise, he found himself enjoying the process; it was like solving a puzzle with all the chaotic pieces snapping neatly into place.\\

``Have you heard about the windmill the Crows are commissioning?", Kraerion asked, suddenly remembering his unsettling conversation with Castor earlier on the trail. ``What do you make of it?"

``Oh yes, the RAIN initiative, right?", Aequitius chuckled softly, ``The crows never rests, do they? I don't know anything about a windmill---but we've been in talks to receive funding from them for the Winter Fund instead of the usual premiums. It will alleviate the animals' budgets somewhat, and induce demand elsewhere."

Kraerion stopped carving, the satisfaction of problem solving vanished as quickly as it had come.

``You cooperate with them?", he asked, his voice cracking, ``Even after what they did to Veritas?"

A very pained expression crossed on Aequitius's face; he looked down at the dirt floor, ``There's much that went wrong this winter, and ultimately, the blame should fall on me. And, I will regret my actions for the rest of my life. But, it wasn't the damn Crows' fault---you know that, right?"

Kraerion didn't have a reply, but he knew in his bones that there was something fundamentally wrong with the whole situation. The leaves, the vote, the windmill, the subsidized Winter Fund---everything was happening too quickly. His brain physically ached just trying to keep up with his thoughts.

As he stared at his father, a horrifying realization settled over him. If he took Aequitius's place, he would be alone in this. He would have to deal with the crows.He would have to navigate the \textit{politics}.
Maybe he could handle the logistics, but \textit{this}?. No, this was not a life. This was too much. He whispered a breathless ``sorry", turned, and ran out of the office.\\

Kraerion pushed blindly past a group of startled chipmunks in the Aorta, his breathing shallow and erratic. He had no idea where he was going, it didn't matter; he just needed to get away. He turned a sharp corner in a run and collided hard with a soft, warm body, nearly sending them both sprawling to the ground.

``Watch your ste---", Kraerion gasped, but the words caught in his throat.

Cinnamon steadied herself with a paw against the earthen wall.
``I was actually looking for you. I have some news.", Cinnamon said offering a warm smile. But as her eyes met his, the smile vanished instantly. ``Are you alright?"

``I don't know...", Kraerion managed to get out, leaning back against the wall. ``I truly don't know."

Cinnamon's eyes softened, and she gave him a small, reassuring smile, ``It's going to be alright, Kraerion. Let's get out of here."

They walked together in familiar, comforting silence until they reached the exit of the runs. The sun was high in the sky now, the air crisp, the day beautiful. They wandered along the trail, letting the fresh air clense their lungs.

``I don't get it", Kraerion said at length after his heart slowed and the panic subsided. ``Look how beautiful the world out here is. Even now, in the grey early spring before the trees find their clothing, it's still so beautiful. How can anyone be content staying underground?"

``Don't you feel exposed out here?", Cinnamon asked curiously, her ears swiveling at the distant rustle of the wind. ``I can't relax out here, I feel like I'm being watched. I feel vulnerable. Underground, I feel safe---down there, I can breathe. I'm not going to echo your father, nor lecture you about duty, but that's how I feel."

``Thanks... I see what you mean though,", Kraerion sighed, ``I guess it's only natural---we used to be hunted out here."

As they wandered along, they came up to one of Hroðulf's newly built stone sun dial.

``Look at this \textit{thing}", Kraerion said, pointing a paw to the sundial, ``It's not just about spending life underground. It's about having your life pre-determined by these stones; about having to play games with crows so as to not being taken advantage of."

He stopped himself for a moment, realizing that Cinnamon had heard him talk all about this at length, probably one time too many. His self-consciousness kicked in and he added, ``I'm sorry, you've heard this before. Never mind. You said you had news, what is it?"

``Oh, right", Cinnamon answered, suddenly looking very nervous. She looked down at her paws, then finding his eyes. ``This might not be the best time, but... ah shoot. I'm with kittens, Kraerion. You're going to be a father."
