\chapter{Denial} % 11

\vspace{-1.3cm}
\begin{localsize}{10}
    \begin{quote}
        “Virtue is more to be feared than vice, because its excesses are not subject to the regulation of conscience.”
        \begin{flushright}- Adam Smith \end{flushright}
    \end{quote}
\end{localsize}
\vspace{1cm}


A banging, unpleasant sound rang throughout the runs and burrows underground, signaling a new work day for the chipmunks. Kraerion woke up in his bed, rolling over to look at Cinnamon, who was still asleep. He studied his three kits, wrapped in a furry heap at the foot of the bed, feeling a contentment rivaling anything he ever known before. ``How they can sleep through this noice is beyond me,", he muttered, rising up and getting himself ready for the day. ``This is not so bad, though", he reminded himself---not for the first time---as he gave Cinnamon a gentle peck on the forehead before leaving their burrow.\\

Kraerion wasn't obligated to attend to the morning meetings in the Aorta, having already planned the day's schedule the previous evening. Shortly after he had returned to live underground, he had made a deal with Aequitius. Kraerion would only manage the internal logistics of the daily operations, whilst Pietus would be the external face---dealing with chipmunk workforce and handling the negotiations and politics with the rest of the forest. It was a compromise he could live with.

Today, however, he had a different agenda. The economic reality of the year dictated that a simple chipmunk wage would not guarantee a comfortable winter. So, he and Cinnamon had agreed that he had to sell his old hollow in the silver birch. Having found a buyer, he now only needed to close the deal.

Taking the path up to the surface jogged his memory of a different time. He exited the runs, stepping out into a a forest that felt vastly different from teh one he had left behind in the spring.

The beautiful long days of summer had passed without Kraerion having a single moment to reflect on them. Now, the trees surprised him with the flaming, bright colours of autumn. The dead, red and orange leaves covered the ground, like a red carpet, welcomed him back to the surface world.

``Where did the summer go?", he wondered solemnly, pushing forth onto the trail that would take him to his hollow. Another thought crept up on him: it was already autumn. winter was not far away, and there was still so much work that needed to happen. He pushed the thoughts aside; \textit{one thing at the time}, he reminded himself.\\

The silver birch stood proud and tall, its yellow-orange leaves barely moving in the cool autumn breeze. Looking up at his former home, Kraerion felt a pang of sorrow for the life he was leaving behind. His former sanctuary, the proof of his independence and hard work---now, but an asset to be liquidated.

Waiting at the base, sat a squirrel; next to him was a stack of bundled leaves.

``Morning, Cash'ew,", Kraerion greeted, bracing himself for the pending negotiation.

``Good morning, Kraerion!", Cash'ew replied frantically, his tail twitching with manic energy. ``Here are the 60 leaves we've agreed on; feel free to count them!"

``That might not be necessary,", Kraerion said carefully, ``It's a nice hollow, keep it dry and don't leave the wooden piece out of the door too often---that will erode the hollow faster."

``Oh, you don't have to \textit{sell} it to me", Cash'ew laughed, ``I'm not living in it, I'm leasing it out to a family of finches. Passive income, you know? You have to put your capital to work!"

``You're not living in it?", Kraerion said shocked, ``How can that be, how can you afford that?"

``Wheeling and dealing in public procurement contracts has been---let's say---a quite lucrative endeavour recently.", the squirrel said, giving another chuckle, ``It's business, I'll be wherever the opportunity arises. Anyhow, do we have a deal?"

Cash'ew raised his right paw for a shake.
At first, a feeling of relief washed over Kraerion. No negotiation. But then, a creeping unease took its place. The squirrel was used to making deals; wouldn't he haggle?
He had only spent a few screw-nuts buying and building the hollow, and now---just like that---it was worth sixty leaves. Prices had gone up, sure, but this much? Wasn't this a bit too easy?

``Okay.", he finally mustered, reaching up his own paw, and they shook.\\

Kraerion hurried away from his former silver birch. He didn't return to the Aorta, though. Instead, he made straight for the autumn market. With prices slowly rising, he reasoned, it felt prudent to spend it fast.

He didn't think much of what the market would look like, assuming it would be orderly and normal as usual. But, when he arrived there, it was absolute pandemonium. A pair of rabbits was frantically trying to out-bid each other over a measly basket of seemingly quite bruised apples. Everyone was desperate to quickly convert their leaves into something edible; the noise of haggling was deafening. He stood there in awe. ``This is insane", he whispered to himself.
His eyes wandered over the small signs; his jaw dropped when he grasped the prices.

``Hello, boss!", a young chipmunk Kraerion didn't recognize, greeted him. ``Out buying groceries like a commoner?"

``Hi---, I'm sorry, I don't remember your name.", he said apologetically, ``Sorry for asking, but how do you afford \textit{anything} here? We don't pay this."

``No worries,", the chipmunk answered cheerfully, ``We don't, me and a few in my scurry double-shift at the windmill construction."

``I see...", Kraerion said, although, he didn't really understand, ``Hey listen, I'm glad I ran into you; I need to make a purchase and could use some help carrying it back to my office. could you run back to the Aorta and fetch a scurry for me?"

``Sure thing boss,", he squeaked, ``you can count on me!"

As the young chipmunk scurried off, Kraerion turned his attention back at the stalls. He made a plan, he couldn't buy as much as he originally anticipated, but still enough for a comfortable winter. He scanned the prices again, ``nothing fancy then, only staple feed.", he thought, looking for the stall with the cheapest nuts. He pushed through the furred and feathered bodies, making his way to the back of the queue.

The line moved agonizingly slow. Directly in front of him stood a vole who was seemingly going through some sort of panic attack, muttering: ``Please don't increase the prices... please don't increase the prices", over and over again.

Finally, he reached the front, finding a familiar face standing in the stall.

``Hi, Pip", Kraerion greeted. ``I didn't know you worked the market."

``Oh, hi there Kraerion", the rat answered, ``What can I say, it's a sign of the times. What can I help you with."

``Let's see", Kraerion began, ``How much varied nuts can I get for sixty leaves?"

``We usually charge five leaves per bag", Pip said slowly, ``Never mind, the chipmunk freight service have been a life saver. You really ought to increase your prices, but don't tell anyone I said that. For you, I can go down to four per bag. So for sixty---let's see---that would be fifteen bags."

``Great, thanks!", Kraerion replied, doing the mental calculation in his head. Fifteen bags would be more than enough for the winter, ``There'll be a scurry here to pick it up shortly."\\

Kraerion left the market, the cacophony of angry voices and desperate haggling slowly fading away. The walk back to the Aorta wasn't far, so he tried to enjoy the little time he had above ground. Yet, his mind was a storm of conflicting thoughts.

Fifteen bags of real, tangible nuts. Cinnamon and the kits would be safe for the winter. He should be pleased; he should feel a sense of triumph. Instead, he felt only an anxious knot tighten in his chest.
\textit{``You really ought to increase the prices."} Pip's words echoed in his ears. What about all the other chipmunks without assets to sell off? How many of the chipmunks in his workforce had other jobs just to get by? They were moving more cargo now then ever, yet somhow, the common chipmunk seemed worse off. He decided; he knew what he had to do.

His thoughts drifted to his father. Aequitius had passed away quietly in his sleep during the summer. Kraerion wished he was here now, so someone could tell him what to do. He hadn't appreciated his father in life as he did now in death, nor had he understood the enormous burden he carried. He smiled at the memory of him, grateful that he---at least---given the old chipmunk some solace before the end. ``I lost a daughter...", he had said, ``but, I got my son back."

Taking a deep breath, Kraerion entered the runs and headed down into the Aorta.

``Can someone fetch Pietus?" he called out to everyone, and to no one in particular, ``Tell him to see me in my office."

He didn't wait for a response; he knew it would be done. Instead, he marched straight into his office---his father's old office---and shut the door.\\

Kraerion did not have to wait long before Pietus barged in to his office.

``What's the emergency?", Pietus asked, a hint of annoyance in his voice, ``Why did you summon me? I've got work to do. The hedgehogs want to increase their shipments."

``At what price?", Kraerion demanded, glaring at his uncle. ``Let me guess---the exact same rate we agreed to in the spring?"

``Of course,", Pietus said curtly. ``You know we don't discriminate. We've been over this---we can't just raise our prices."

``These agreements are ruining us. It's not discrimination, it's survival.", Kraerion argued, ``Do you know how bad it is? Look at the market prices for feed! Our runners must take on extra shifts outside our employment, just to make ends meet. And, the public funding for the Winter Fund is ridiculous with today's prices, it's not nearly enough, are we supposed to just cover it ourselves? That---if anything---is discrimination."

``You know our bylaws, Kraerion", Pietus sighed, speaking as if he were arguing with a child. ``We set our list prices in the spring, and then we're accountable for them. It's our duty to see it through."

``We are literally the only ones honoring any long-term price agreements. Our way of conducting business was set in a time before rapid price changes.", Kraerion cried, now desperate,  ``We have to renegotiate, that's our only option."

``No.", Pietus said with a finality in his voice, ``We chipmunks have never broken an agreement, I refuse to be the first. Regardless if whether it's our list prices or our obligation to run the Winter Fund."

Before Kraerion had time to reply, the door to the office swung open. The young chipmunk he had met in at the market, and three other chipmunks, lugged the fifteen bags of nuts into the room.

``Where do you want them, boss?", the young chipmunk asked cheerfully.

Kraerion simply nodded to the corner of the office.``Just put them over there...', he muttered. Then, realizing his tone was quite unfair to the workers, he forced a smile, ``Thanks for your swift service!"

The chipmunks did as they were bid, Pietus watching them hawkishly with a gaze full of suspicion. The four chipmunks left, pulling the door shut behind them.

``We're keeping feed in the office now?", Pietus accused, his eyes snapping back to his nephew. ``You're out of line!"

``Oh, \textit{I'm out of line?}", Kraerion countered mockingly, ``It's feed I bought with my own leaves after selling my hollow, since no one---not even me---can support a family on the wages we pay."

``So, you're using our workers as your personal valet?", Pietus pressed, stepping closer.

``No, of course not.", Kraerion almost yelled, reddening from anger, ``I'll pay, like anyone else. Not like it's much---we barely charge!"

``Have you forgotten,", Pietus asked, now suddenly appearing calm, ``that in our agreement of funding for the Winter Fund, the leadership is held personally liable in case of a shortfall."

Kraerion froze. ``You can't be serious---", Kraerion snapped. ``What's that supposed to mean?"

``It means," Pietus said, ``that a captain goes down with his ship, like any real leader would."

``You're really going to steal our feed? Starve your nephew's family?", Kraerion was fully yelling now; he could not believe what he was hearing, ``You're going to kill us all!"

``If I must. We must lead by example; we must be the ones to starve first.", Pietus said somberly, ``There's nothing you can do. You know you're in the wrong. Surrender the bags, Kraerion. Don't force me to involve the Crows."

The mention of the Crows---the implicit threat of their Stoats---snapped something deep inside Kraerion. This was not his uncle, this was a monster. His veil of civility fell, and left was only pure instinct. Kraerion took a couple of steps backwards, snatching up two heavy bags of nuts in his arms. Before his uncle could react, Kraerion rushed forward, dropping his shoulder, and tackled Pietus hard to the ground.

Panic seized him. ``What have I done...?", he whispered, his voice wavering. He clutched the two bags closer to his chest and fled out of the office, sprinting blindly into the maze of runs.