\chapter{Device}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		"'Emergencies' have always been the pretext on which the safeguards of individual liberty have eroded."
		\begin{flushright}- Friedrich A. von Hayek\end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

Redrill, the woodpecker he'd hired to build his home, was already waiting when Kraerion peeked his head out from the southern exit. The three screw-nuts, wrapped around his arm, caught by the sun and glimmered.

After the meeting, Kraerion had returned to his burrow one last time to fetch his screw-nuts and say goodbye. He had stood there for a very long time. 
"It's already done, the decision is taken.", he had said to himself, yet his legs had refused to move. Life underground was all he had known; and whilst moving his legs wasn't exactly novel, everything else was going to be. "This is no time to for nostalgia. it's already done, the decision is taken."

"You really sure about this?", a voice said. Redrill had snuck up on him, interrupting his thoughts.

"Yes —", Kraerion answered quickly, too quickly. He nodded his head in a silly attempt of a greeting, "I —— I've never been more sure."

Redrill chuckled amused, "Don't worry, I won't argue with the hands that feed me", he said, "I see you brought payment."

"Yes, only the one is for you though. Better get going."

The woodpecker smiled, nodded, and set off south — wings unfolded.

The Wadborough villagers, in a time before environmental concerns, dumped their undesirables in the forest. Everyone denied it, yet batteries, plastics, electronics, and everything inbetween found themselves in every nook and cranny of the forest floor — even a car or two occasionally joined the detritus and duff. Most animals, after a good sniff, would not bother with these alien contraptions. But in a magpie a curiosity grew; and soon, he conjectured: these objects of Men might teach a thing or two. The crow began to take them apart; to study their innate structures and learn of the screw-nut and its uses. Death may be the mother of beauty, yet these imperishable hexagons of cast steel were of different kind. The rays bouncing of the plain silver surface caught the crow in awe; the beauty consumed him and he took to hoarding. The desire for these litte things spread like wildfire amongst crow and animal; a treasured commodity was born. But it wasn't like any other commodity: it endured where blueberries rot, it was portable where trees stood firm, but most significant was its limtied supply — a thing of Man; it couldn't be produced like the spines of a hedgehogs back, nor grown like the acorns of an oak. Naturally the young economy yearned to keep score — an informational instrument to keep track of favors; a fair system of time allocation. And, for the first time in the kingdom of animal, go beyond reciprocal altruism and let a money be born.

%The Wadborough villagers, in a time before environmental concerns, used the forest as a dump. Everything from electronics to cars were shattered with regular interval. At first no animal would bother with the alien contraptions, but eventually the crows grew curious and conjectured that these objects of men could teach a thing or two. When taking apart them, they lay notice to the many screw-nuts holding them together; they quickly became consumed by their beauty. Their hexagonal shape and the glimmering of steel in the sun. The screw-nuts became desired and it didn't take long until trade was exclusively in screw-nuts. Their alien form made them difficult to counterfeit and they remained scarce through generations. Many a youth, seeking fortune, scavenged the forest and surrounding meadows in search for freshly dumped junk, but most came up shorthanded. 

%Chipmunks can quickly bolt if in danger, unthreatened however, they move slowly through the tall grass, weeds and thistle making up the forest floor. As they walk on their forepaws, their field of vision is limited and they usually need to stop every few step to stand up hind legs to see their surroundings.


To Kraerion the screw-nuts were just a means to an end: to persue life anew. The day was a beautiful one; ths sun shone bright on the blue canvas sky with only a few dots of white. He followed the flying woodpecker as best he could from the ground below. The anxious feeling he'd felt in his burrow was eased by the fine weather.
  "I could live a whole life underground without experience such a day like this.", he thought, "It's done, it's already done."
The sun's rays told of high noon, yet the forest was unusually quiet. Noon was a time of activity, when the animals left their burrows, nests, lairs, or vocational duties to gather for trade. To buy and sell food; and, offer and acquire services. Everything were available: a nightingale could be hired to sing, a joyride could be had on the back of a magpie, blueberries from meadows beyond the eastern horizon could be bought, amongst other things.
  So on any other day a distant voice would not have sparked an interest as they reached a clearing in the trees. Kraerion leaned back on his hindlegs and saw, past the overgrowth, a hedgehog and a robin arguing. He knew the hedgehog, as a friend of his father's, and closed the distance.

"Are you mad?", the robin asked, "Have you completely lost your mind? I need more than the two."

"Spines are not weeds; we only drop the few each week.", the hedgehog answered, "And, these recent events have created a certain demand, as you surely understand."

"But — But that's more than twice as expensive than one week ago. I'm down to my last screw-nut — you must understand."

"I mustn't anthing. I could ask any of your neighbours, whom I'm sure they would find the price to be fair and just."

"Why would you need spines anyway", Kraerion interruped as he reached them; between them, on the ground, lay a stack of spines sharp and keen.

"Haven't you heard? It's horrible — horrible: a lot has gotten their screw-nuts stolen. Just this morning, my nightingale neighbour got his stolen. I refuse to sit idle — we've got to take up arms and defend ourselves. Like — like in the time of Man."

"Hfm", Redrill uttered from a beech twig above the group, "I heard Zrefrafal and a few other rabbits complain earlier this morning, their burrows had apparently been raided. And they are {\it rabbits} after all, who would dare mess with them?"

"Yes, it's all very bad. All agree.", the hedgehog said, "But we got business to conduct, move along then, go waste someone else's time. Preferable someone whose time is less valuable than mine."

The woodpecker, without saying a word, pulled the seeds from one of weeds sticking up, chewed it, and spit it out at the feet of the hedgehog. He took of with a few broad wingstrokes and Kraerion was once again forced to hurry along after, earthbound.

They soon reached the birch, which was to become Kraerion's home, standing tall and shone of silver. Redrill began to drill out an entrance in the southern side of the thick trunk, just above the first branches, a 20 feet or so above the forest floor. Kraerion was about to go look for Greyhead, the pidgeon, he'd bought the tree from, to finalize the payment, when the two were interruped by a loud screech from a neighbouring birch.

"Wait here", Redrill urged, and, without hesitation, dashed of towards the sound. Kraerion didn't wait; instead, he lunged to the tree and rushed up its trunk. The sound had emerged from where the trunk divided into three limbs to form the crown, and, between those limbs, a pidgeon had built her nest. Kraerion leapt onto one of the limbs as to look down and see the nest. Redrill was perching on an opposite branch and pidgeons were joining all around them. They all looked down and saw a terrified mother and her three newborn squabs, naked but for their half-grown down.

"They're gone", she said despondently, "They're all gone."

"Won't insurance cover it?", a pigeon asked after a moment of silence.

"No," another answered, "theft has not been an issue since the time of Man; why would it be covered?"

"Insurance may yet be rectified, as far as I'm aware it has always been implied to cover these kinds of situations.", the pigeon, Greyhead, broke in, "Otherwise we'll come together and cover it ourselfs; solidarity is not lost on us. Anyway — the best we can do now is to give her some room to breath, especially those not yet part of our community." The pigeon had his eyes rested part on Kraerion and part of Redrill, as he said the last sentence. The two outsiders took the hint and retrited back to Kraerion's birch.

Redrill worked late into the night, his red crest blured as his head jerked back and forth in what appeared as one incessant motion. Kraeriom felt a fool as the woodpecker's name dawned on him.
Woodpeckers were not made to carve homes in trunks; evolution, over eons of time, formed their strong chisel-like bill and shock-resistance skull, to prey on termites, beetles, and various larvae dwelling under bark and wood. In Wadborough forest however, their unusual ability was better served carving homes, and they prospered from the commercial interests. They were only a few woodpeckers in the forest, their service were limited, and thus regarded as luxurious. Only the very well-of could afford one — the beloved singer nightingale or the industrious clever crow — and now Kraerion was amongst them.

Redrill was almost done, when Greyhead emerged from the canopy. 

"Excuse my rude welcome earlier", Greyhead began, "These are strange times, I hope you understand"\\

"Strange times indeed, there's no need", Kraerion said. "I assume you're here to collect what's yours."\\

"Yes, but not solely.", Greyhead said, "The crows have called to an emergency meeting, tomorrow at noon. Thought you and Redrill ought to know."

After receiving the payment, Greyhead dissappeared as quickly as he came, and it was Redrill's turn to collect.

"It's done!", he proclaimed, "are you sure it's deep enought? It's barely more than an entrance."

"Well, I can't afford any more of your time, you know that.", Kraerion answered, "Besides, my teeth should be strong enought to carve out the rest. Take the screw-nuts before I regret this."

"It's getting late, are you sleeping here?"

"Not that I have much of a choice, the new occupants have most likely moved into my old burrow by now."

% One day was today

"Well then", the woodpecker said as he untucked his wings and took off into the blissful summer night, leaving Kraerion alone with his hollow and new life. Still unsure if he'd made the right decision, he climbed up the tree deep in thoughts, "Now it's definitely done", he whispered. The hollow floor was still rought and unyielding, but it wasn't the soil of a burrow, and that was all that mattered. With time, he would widen the hollow, grind the walls and floor sleek, carry up moss and lichen to make a bed, and make a home. That night he slept uneasy on the stiff wood; his head unbridled and awake, yet his limbs heavy and yearning for rest. He'd never before felt the jolt of satisfaction this sort of exhaustive sleep produced — it scared him to know, he'd almost gone a whole life without it.


%"God I hope I never see this damp soil ever again" he muttered to himself in silence and left quickly, as to not get caught by the strong inearthing force of nostalgia . The sun had made its routinely voyage across the sky and was soon to pass over the great spruce. Supram took one last glance back at the burrow before he leaped into the run heading towards his new home. 

%"Sure enough", Redrill said as he flew up to the spot slightly above the first branches and began to peck. At once Kraerion realized how Redrill had gotten his name. His red crest was incessantly moving back and forth in what appeared only as a red blur to the naked eye. Woodpeckers have not gained their ability to build shelters, but to force larvae and other arboreal out from their comfy homes. The woodpecker of Wadborough forest had quickly learned how to apply their unusual ability for commercial interests. Many of the well-of song bird had gotten peckers nests carved for them. They may be best compared to the wooden bird-houses that have become popular for people to build and hang in their gardens, but instead of hanging on the trunk; they're built directly into the trunk itself.

