\chapter{Dilution}

\vspace{-1.3cm}
\begin{localsize}{10}
	\begin{quote}
		“The long run is a misleading guide to current affairs. In the long run we are all dead.” 
		\begin{flushright}- John Maynard Keynes \end{flushright}
	\end{quote} 
\end{localsize}
\vspace{1cm}

%"Is water water?", Vlahir crowed, peering out over the crowed that once again had gathered beneth the Old Oak.
%He waited a long while before he continuted - eating the silence.
% "Ask the doe, whose fawn drank from a puddle grown stale and infectious, and not from the healty brook as was taught. Ask the salmon, who dared his life swimming upstream only to get from one body of water to another. Water is not water - if life is not death. It's naught but a plain canvas; a medium to be altered, shaped, and most importantly: controlled." 

%"Our forest is water — and currently, it's that still infectious puddle.  "

%"Our forest is but a puddle; still and unproductive", Vlahir began, "It's known that puddles and otherwise still water carries disease. We shan't drink it.
%We shall however drink from the brooks, where the current has brought life and fortune. Our forest is but a puddle; if it remains a puddle - we all be dead come winter."\\


"Is water water?", Vlahir crowed, peering out over the crowd, which had once again gathered beneth the Old Oak in the Glade of Representatives. He let the question linger - eating the silence - before he continued. 

"Ask the salmon, who dares his life on his journey upstream, only to get from water to water?
 Ask the beaver, who spends his life perfecting his dam, only to form a pond in the creek?
 Ask the doe, whose fawn drank from a puddle grown stale with disease, instead of from the brook as she was taugh - whose fawn drank water instead of water?

 No, water is not water, if life is not death. Water is only a plain canvas, a medium to be altered, shaped, and for us to control - if we are to take control of our fate."

// Explain glade , winter survivale

The spring had emerged like sunshine through mist. Although the forest had survived the winter, they'd suffered greatly. The thin rationes had turned them meager and weak. And so, as the animals listen to the crow talk, they all had a silent understanding: this shall never happen again - whatever it will take.

// Our forest is water like the puddle stale and still.

"Imagine if the water in our Forest", Vlahir explained, "was stale like the puddle which the fawn drank from, so very stale and still. In fact, there is no movement in the water at all; the brooks have turned to narrow ponds, and the ponds lay still and blank. There's not a bend where the water flow, there's not a drop which isn't stale, and there's naugth for us to drink! And, without a solution, our Forest would slowly die. What must happen for our Forest to survive?

// Riddles

%"Each of us are the droplets that makes the puddle. Our actions, its current. There is natural ebbs and flows of course, but sometimes it gets stuck still in ebb. Low demand for goods leads to fewer trades and subsequently fewer jobs. Fewer jobs in turn leads to fewer leaves to spend, further damaging demand. A maelstrom of disease if you will."\\

Now imagine that this water is our economy, and that the same solution would apply to our now dire state of destitution.
Riddles are these precious little things, tender and digestible with reality abstracted, to afford even the dullest of minds some amount of comprehension. Solve this riddle and our economy is saved."

"I suppose", Zefrafa said at length, "water moves mainly because height differential in the terrain, so we'd should pray for rain?"

% this nees something more
"Yes, rain! Let the rain fall - like Enki whispered through the reeds; and to Noah told in the Book of Man - for forty days and forty nights. Let the rain fall and drown our Forest with movement and drinkable water - let our Forest drown in prosperity!

// Explain your parable 

"Craax", Eaglewing interrupted, "this story of thine is all well and good, but if it suppose to be parable, or allegory, or whatsoever of meaning - it's rather incomprehensible."

"Okey", Vlahir said, clearly dissapointed, "Where's the fun in that?"

When no one answered his question, the crow continued.

"The water represent our economy, and our economy do behave similar to a liquid. When water moves, it leaves a vaccum and water rushes in from all sides to fill it. Movement begets movement. When a leaf is spent, it leaves the producer with more captial, which he could either spend to increase his output, or spend on himself. Spending begets spending.

Whilst the velocity of water tells us the health of our ecosystem, the velocity of money tells us how much we produce. How much we produce, in turn, predicts the survival of winter.

When the screw-nuts began dissappearing late last spring, it caused three things to occur: 1) Decreased spending on leisure, as one aren't keen to disport oneself when one's livelihood is in danger, 2) Increased risk aversion, which manifests in many forms, but also leads to decreased spending as families choose the cheaper food alternatives in their saving for winter, and 3) increased disutility of labor, as laber often requires leaving screw-nuts and kittens unwatched, which of course is more significant a factor in a crisis.

All three of these, which I'm sure you've deduced by now, retards velocity - velocity which we know have an amplified effect on itself. We can also determine that 1), and 2) are more significant than 3), since the demand took a greater beating than supply, which may be observed in the decreasing prices. Decreased prices also decreases spending since salaries - ...", Eaglewing waved sofly with his normal black wing, Vlahir noticed and continued,".. you get the point. This negative sprial—this maelstrom— of ever decreased spending must be broken. Spending must be increased. At all cost.


Kraerion sat at his now usual place in the twigs amongst the song birds. Vlahir's words made sense to him, but they clearly formed another explaination than the one Veritas had given. And Veritas explaination had made sense too. He searched with his gaze for Pietas and Cinnamon in the glade; they both looked to him content with staying quiet. Kraerion supposed he ought to say something - explain what Vertias had - but what would he even say? This whole discussion was one abstraction beyond his comprehension.


"There are three ways for us to increase spending again", Vlahir continued, 

"The first is to somehow induce us the Animals to spend a higher percentage of our existing income. However, this likely goes against the best interest of the individual; it's a prisoners dilemma: spending is the losing move, until everyone else also are spending. For this reason, we can't expect this to break the cycle, but it will strengthen the Recovery once the tide turns."

%"The first" it's a prisoners dilemma, spending is the losing move, until everyone else are spending. We can't expect it to break the cycle but this will strenghten the Recovery once the 

"The secound way conserns the spending of business investments: building out infrastructure, and increasing supply capacity. But how can such a measure be feasable to take when demand is decreasing? No, we cannot rely on this form of spending to be the main driver of the Recovery! Nevertheless, this too will aid the recovery once we're back on a brighter course."


"That leaves us with the third and final form of spending: public spending. And, in contrast to the two first ways to increase output: it does not depend on the behaviour of individuals! It can be increased over night, by a simple decision by us, right here, right now."

"This third method, is the only way for us out of this crisis. There are still some technical caveats to consider. This public spending cannot come at the cost of some other form of spending. The funds for this spending cannot, for example, come from increased taxation - as that would reduce the individuals ability to spend."

"There are other technicalites in the implementation that are similarly key in the Recovery. Consumer prices have been all over the place - although mostly down. This creates an uncertainty; if — in your vocation - you've the need for a certain commodity, but the end product you sell are displaced in time. If prices fall during that time, you might end up with a loss - for an otherwise healthy business!
 Thus we ought to stablize prices, which we cannot do when our leaves are tied to screw-nuts. It is fixed, and like the ebb and flow, our currency must adjust with the market instead of being a product of it.

 



stable prices detatched from screw-nuts

decresed cost of money

"

Vlahir stood at length when he'd finished, and the he sort of just receded into the darkness. % What is this sentence even.

"Vlahir is right, this is the only way for Recovery. But, this is also an oppertunity for Reform. Public spending that does good. 

We shall spend on the Winter Fund, transform it to cover all - without any need to pay into it! And thus, we'll increase demand of feed - be the buyer of last resort.

We shall spend on the preservation of the beauty of the Forest - we shan't overdevelop but rather leave parts of innocent and natural Forest available for all.

"



%Vlahir looked around the glade, his curious eyes wandering. Vlahir truly loved an audience in dispense.\\


The glade was in complete silence now, only a few could grasp the true meaning of his words. Even fewer had any wits to contest it. \\

"It's the current that is the answer. A great stimulus. A greate spending to ignite, to create demand and need jobs. We will give you that." said Vlahir as he ended his speech. He left the branch and made room for Eaglewing.\\

Eaglewing stepped forward again. "Craax", he cried, "Through diligent consideration, we've decided to implement a set of policies to stimulate our economy. To increase demand and subsequently create jobs."


%"We need a current in our forest. If no-one demand anything, no-one works. If no-one works, we have no food. As puddles carries disease - a market gets stuck. It needs spending, jobs and stimulus. Otherwise it will carry disease  "  
